---
title: "SP_1.2_SIM"
author: "Colin Bailey"
date: "2025-04-24"
output: html_document
---

This code chunk loads the required packages and the data. Note that a specific version of samSim is required (see commented-out code to install the correct version), and that if a different version of samSim is installed on your computer, you may need to manually delete it from your library to get the new version to install correctly.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(viridis)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
#install.packages("remotes")    #run this line and the next once to get access to the sgen solver that DFO has developed
#remotes::install_github("Pacific-salmon-assess/samSim", ref="sbccnk-hatch", force=TRUE)
library(samSim) #package that DFO created to simulate salmon abundances

pkgbuild::has_build_tools(debug = TRUE)
rstan_options(auto_write=T)
options(mc.cores = parallel::detectCores())

#escapement data
esc_dat <- read.csv("SP_1.2\\Data_in\\sp1.2_smu_no_escape.csv")
head(esc_dat)

#posterior data
pos_dat <- readRDS("data\\post.rds")
head(pos_dat)

#age data
age_dat <- read.csv("SP_1.2\\Data_in\\rec_age_comp.csv")
head(age_dat)

#Nicola S-R data
nic_dat <- read.csv("SP_1.2//Data_in//nic_dat.csv")

#Nicola S-R data broken out by brood year and recruit age
dat_sr <- read.csv("SP_1.2//Data_in//srDat.csv")
```


This code chunk prepares data for use in 'samSim' (the forward simulation tool). The key data inputs in this chunk include:
1) a correlation matrix of the sub-populations being simulated
2) watershed area-based estimates of SREP for sub-populations without S-R models (all except Nicola) that are converted into beta values (*see "02_Benchmarks.Rmd" for details on conversion of SREP to beta*)
3) a posterior for each sub-population with Ricker model parameters "alpha", "beta", and "sigma" (**detailed explanation of the calculation of these parameters below this list**)
4) mean proportions and variance in age at return
5) an estimated S-R timeseries (based on Nicola Indicator Stock information) to prime the simulation

**Description of the posteriors for the sub-populations**
The 'samSim' package can produce forward simulations of salmon abundance using fixed Ricker parameter values or posteriors from Ricker stock-recruit models. Here, we wanted to simulate abundances in the sub-populations of the Fraser Spring 1.2 Chinook SMU across a realistic fixed range of alpha values (productivity) while still incorporating uncertainty from models' posteriors. The parameters provided in the population-specific posteriors included:
1) alpha - range from 0.2 to 1.305 in even steps representing a wide range of alpha values observed in the Nicola S-R model posterior. The same fixed values of alpha were assumed to be representative of all Fraser Spring 1.2 populations
2) beta - posterior generated from the Nicola S-R analysis for Nicola, and from the Parken Habitat Model for all other populations
3) sigma - posterior generated from the Nicola S-R analysis and assumed to be representative of all populations

The range of alpha values tested (n = 14) roughly matches the 80% CI of alpha values in the posterior from the Nicola S-R model. Because marine survival/productivity is a component of alpha (productivity), we can provide a rough translation between productivity and survival values. When the range of alpha values we tested are translated to equivalent smolt-to-age_3 survival index values, this equated to a range from 0.5% survival to 6.6%, which matches the lower 80% CI for logit-transformed and z-scored smolt-to-age_3 survival (0.5%) and roughly matches the upper 95% CI (6.3%). Thus, the range of alpha values used in the simulation cover a realistic range of productivity/survival values. 

Beta values were estimated from posterior predictions of SREP for each population except Nicola (for which beta is estimated in the S-R model) as described in "02_Benchmarks.Rmd". Because alpha and beta are correlated statistically, and pairings of low values of one parameter with high values of the other parameter can lead to simulation malfunction (samSim errors out and fails to complete the simulation), we paired lower values of alpha with lower quantile slices of beta, and vice versa. Thus, for each population, the vector of 30000 possible values of beta were sliced into 14 quantiles, and the 1st quantile of beta was matched with the lowest value of alpha tested, etc. 

Sigma values were not matched in any particular fashion to values of alpha or beta as they are not correlated with those parameters. Thus, sigma was drawn at random from the Nicola S-R model posterior.

For each population and level of alpha tested, a posterior of 1000 rows with alpha, beta and sigma were fed into the simulation.


```{r sim data prep}

###Escapement correlation### - filter out pops with high hatchery influence & no NO estimates, and filter out years with NAs
`%!in%` <- Negate(`%in%`)
dat <- esc_dat %>% filter(Pop_Name %!in% c("NICOLA RIVER-UPPER", "SPIUS CREEK", "COLDWATER RIVER"))

bess <- dat %>% filter(CU_ID == "CK-16") %>% group_by(Year) %>% summarize(TotalInfilled = sum(TotalInfilled, na.rm = F))

dat_simp <- dat %>% filter(Pop_Name %!in% c("BESSETTE CREEK", "HARRIS CREEK", "CREIGHTON CREEK", "DUTEAU CREEK"))

dat_bess <- dat %>% filter(Pop_Name == "BESSETTE CREEK") %>% dplyr::select(-TotalInfilled) %>%
  bind_cols(., TotalInfilled = bess$TotalInfilled)

dat <- bind_rows(dat_simp, dat_bess)

source("R\\pop_cor.R")

pcor <- pop_cor(dat) #population correlation matrix

###Estimate srep from watershed areas for populations without beta estimates###
wa = c(4521, 3498.64, 889.64, 519.39, 276.21)
pop = c("Nicola River", "Bonaparte River", "Deadman River", "Louis Creek", "Bessette Creek")

nu_wa = data.frame(pop, wa)

#baseline data (paired watershed areas and SREPs) are specific to stream-type chinook for maximum relevance to Fraser Spring 1.2 Chinook (which are stream-type Chinook) -> these data are for running the Parken Habitat Model (2006)
old_wa <- read.csv("data\\srep_habitat_model_data_stream-type_ May 2025.csv") %>% mutate_at(c(2:4), as.numeric)

source("R\\srep_wa_analysis_predict.R")

nu_srep <- srep_est(nu_wa, old_wa)
names(nu_srep) <- c(unique(nu_wa$pop))
nu_srep <- nu_srep[sample(nrow(nu_srep), 30000),] #srep posterior, 30000 samples each per population

###Estimate beta posterior from nu_srep posterior###
post <- readRDS("data\\post.rds") #posterior from the Nicola S-R model

srep_post <- nu_srep %>% dplyr::select(-`Nicola River`) %>% pivot_longer(names_to = "pop", cols = c(1:4)) %>% arrange(pop) #posterior of srep values for all populations except Nicola

#creating alpha-sigma-gamma-alpha_prime posterior for Bonaparte, Deadman, Louis and Bessette
bt <- post[sample(nrow(post), 30000),]
dm <- post[sample(nrow(post), 30000),]
ls <- post[sample(nrow(post), 30000),]
bs <- post[sample(nrow(post), 30000),]

h1 <- rbind(bt,dm)
h2 <- rbind(ls,bs)
w <- rbind(h1,h2) %>% dplyr::select(-beta) #binding the posteriors into a single dataframe

srep_post$alpha_prime <- w$alpha_prime
srep_post$alpha <- ifelse(w$alpha > 0, w$alpha, 0) 
srep_post$sigma <- w$sigma
srep_post$gamma <- w$gamma

nu_beta <- srep_post %>% mutate(srep = value, #produces equivalent-to-Nicola-posteriors for the non-Nicola populations
                     beta = alpha_prime/srep) %>%
  dplyr::select(alpha, beta, sigma, gamma, pop)

nu_post <- post %>% #produces Nicola River posterior in same format as nu_beta
  mutate(pop = "Nicola River",
         alpha = ifelse(alpha > 0, alpha, 0)) %>% 
  dplyr::select(alpha, beta, sigma, gamma, pop)

sim_post <- rbind(nu_beta, nu_post) %>% #creates one large posterior with all populations represented
  mutate(stk = ifelse(pop == "Nicola River", 1,
                      ifelse(pop == "Bonaparte River", 2,
                             ifelse(pop == "Deadman River", 3,
                                    ifelse(pop == "Louis Creek", 4, 5))))) %>% 
  dplyr::select(stk, alpha, beta, sigma)#full posterior to feed to the simulation

sim_post=sim_post[order(sim_post$stk),] #orders the posterior by stk #

#manipulate the posterior into 14 posteriors, each with a fixed value for alpha and varying values of beta based on srep - this preserves the posterior variance while allowing fixed values of alpha to test across the plausible range for the icecream plots (see "04_samsim_processing.Rmd")
#note that alpha values are based on the 2 SD range in SAS 
alpha_nu <- seq(from = 0.2, to = 1.35, by = 0.085) #alpha values to test
stk_beta <- list() #empty list to populate with beta values sampled from 14 quantiles
beta_nu <- list() #empty list of lists to combine the outputs of stk_beta
b_ks <- c(7.142857,        #quantile break points (100 / 14 = 7.142857)
             (7.142857*2),
             (7.142857*3),
             (7.142857*4),
             (7.142857*5),
             (7.142857*6),
             (7.142857*7),
             (7.142857*8),
             (7.142857*9),
             (7.142857*10),
             (7.142857*11),
             (7.142857*12),
             (7.142857*13)) * 0.01

###Creating a list of dataframes with beta and sigma pairs arranged by beta quantile slice##

for(s in 1:5){
  stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta < quantile(beta, probs = c(b_ks[1]))), 1000)[,3:4] #sample beta and sigma pairs from the posterior for each stock and the first beta quantile
}
beta_nu[[1]] <- bind_rows(stk_beta, .id = "column_label") #bind together for loop outputs

for(i in 2:(length(alpha_nu) - 1)){ #sample beta and sigma pairs from the posterior for each stock and the middle 11 beta quantiles
  for(s in 1:5){
    stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta >= quantile(beta, probs = c(b_ks[i-1])) &
                                                                      beta < quantile(beta, probs = c(b_ks[i]))), 1000)[,3:4]
  }
  
  
  sim_post[sim_post$beta >= quantile(sim_post$beta, probs = c(b_ks[i-1])) & 
                            sim_post$beta < quantile(sim_post$beta, probs = c(b_ks[i])), 3:4]
  
  beta_nu[[i]] = bind_rows(stk_beta, .id = "column_label")
}

for(s in 1:5){ #sample beta and sigma pairs from the posterior for each stock and the last beta quantile
  stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta >= quantile(beta, probs = c(b_ks[13]))), 1000)[,3:4]
}
beta_nu[[14]] <- bind_rows(stk_beta, .id = "column_label") #bind together for loop outputs


###Creating a list of dataframes with rows of alpha, beta, and sigma arranged by alpha value and beta quantile slice##

sim_post_vars <- list() #create empty list for final posteriors to feed to the simulation

for(i in 1:length(alpha_nu)){
  sim_post_vars[[i]] <- assign(paste("sim_post_a", alpha_nu[i], sep =""), rep(99, 5000))
}

for(i in 1:length(alpha_nu)){ #populating dataframes with stk and alpha, leaving dummy values for beta and sigma
  sim_post_vars[[i]] <- sample_n(sim_post, 5000) %>% mutate(alpha = alpha_nu[i], 
                                                            beta = 99,
                                                            sigma = 99)
  sim_post_vars[[i]]$stk <- c(rep(1,1000), rep(2,1000), rep(3,1000), rep(4,1000), rep(5,1000))
}


for(i in 1:length(sim_post_vars)){ #replacing dummy values of beta and sigma with pairs from beta_nu
  sim_post_vars[[i]][,3:4] = beta_nu[[i]][2:3]
}

###Tau for age variance and mean proportions at age (3,4,5)###
ppnMat <- age_dat %>% mutate(p3 = a3/(a3 + a4 + a5),
                   p4 = a4/(a3 + a4 + a5),
                   p5 = a5/(a3 + a4 + a5)) %>% dplyr::select(p3, p4, p5)

source("R\\age_tau.R")

tau <- tau_comp(ppnMat)$tau #tau 
m_props <- tau_comp(ppnMat)$pa #mean age proportions

```


Hatchery spawners are incorporated into the simulation analysis for the Nicola River sub-population. Hatchery spawners are included with total spawners contributing to the next generation of recruits, but are not included in the recruits for the simulation. This means that we are not considering the differential productivity between hatchery- and natural-origin spawners in these analyses. In addition, hatchery-origin spawners are not included in the CU spawner totals used to evaluate whether a CU is above its lower benchmark.
```{r, hatchery scalar estimation}

nic_dat$hatchery_spawners=nic_dat$total_spawners-nic_dat$no_spawners #hatchery spawner abundance
nic_dat$p_hatch_no=nic_dat$hatchery_spawners/nic_dat$no_spawners #ratio of hatchery:natural origin spawners

#estimate gamma distribution parameters
fit<- dglm::dglm(nic_dat$p_hatch_no~1,family=Gamma(link='log'))
mu<- exp(fit$coefficients[1])
shape<- exp(fit$dispersion.fit$coefficients[1])
scale<- mu/shape
max_hsp<- max(nic_dat$hatchery_spawners)
par(mfrow=c(1,2))
hist(nic_dat$p_hatch_no,main='observed ratio of hatchery:natural origin spawners')
hist(rgamma(1000,shape=shape,scale=scale),main='simulated gamma distribution of ratios')

```


This code chunk creates an approximation of the stock-recruit information for each population based on the stock-recruit data available from the Nicola Indicator Stock and the spawner escapements from the other populations without stock-recruit information. We approximated the stock-recruit information for the remaining populations to prime the simulation so that it starts from the most recent complete brood year of recruit and escapement information.
```{r build srDat}

n_dat <- dat_sr %>% mutate(t_rec = rec2 + rec3 + rec4 + rec5 + rec6,
               p2 = rec2 / t_rec,
               p3 = rec3 / t_rec,
               p4 = rec4 / t_rec,
               p5 = rec5 / t_rec,
               p6 = rec6 / t_rec,
               m_rec = t_rec / ets) %>% filter(yr %in% c(1995:2020))

###Escapement timeseries
`%!in%` <- Negate(`%in%`)
edat <- esc_dat %>% filter(Pop_Name %!in% c("NICOLA RIVER-UPPER", "SPIUS CREEK", "COLDWATER RIVER"))

bess <- edat %>% filter(CU_ID == "CK-16") %>% group_by(Year) %>% summarize(TotalInfilled = sum(TotalInfilled, na.rm = F))

dat_simp <- edat %>% filter(Pop_Name %!in% c("BESSETTE CREEK", "HARRIS CREEK", "CREIGHTON CREEK", "DUTEAU CREEK"))

dat_bess <- edat %>% filter(Pop_Name == "BESSETTE CREEK") %>% dplyr::select(-TotalInfilled) %>%
  bind_cols(., TotalInfilled = bess$TotalInfilled)

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, yr = Year, ets = TotalInfilled, totalSpawn = TotalInfilled) %>% 
  filter(yr %in% c(1995:2020))

e_dat[104, ] <- c(5, 2020, 1.026313, 1.026313)

dat_nu <- list(stk2 = e_dat %>% filter(stk==2),
     stk3 = e_dat %>% filter(stk==3),
     stk4 = e_dat %>% filter(stk==4),
     stk5 = e_dat %>% filter(stk==5))

for(j in 1:4){
  for(i in 1:nrow(n_dat)){
    dat_nu[[j]]$t_rec[i] = dat_nu[[j]]$ets[i] * n_dat$m_rec[i]
    dat_nu[[j]]$rec2[i] = dat_nu[[j]]$t_rec[i] * n_dat$p2[i]
    dat_nu[[j]]$rec3[i] = dat_nu[[j]]$t_rec[i] * n_dat$p3[i]
    dat_nu[[j]]$rec4[i] = dat_nu[[j]]$t_rec[i] * n_dat$p4[i]
    dat_nu[[j]]$rec5[i] = dat_nu[[j]]$t_rec[i] * n_dat$p5[i]
    dat_nu[[j]]$rec6[i] = dat_nu[[j]]$t_rec[i] * n_dat$p6[i]
  }
}

nic <- n_dat %>%  dplyr::select(stk, yr, ets, totalSpawn, rec2, rec3, rec4, rec5, rec6)
rest <- bind_rows(dat_nu, .id = "column_label") %>% dplyr::select(-column_label, -t_rec)

srDat_infilled <- rbind(nic, rest)

write.csv(srDat_infilled, "data\\samsim pars\\srDat_infilled.csv")
```


Note that HO recruits are added to the total recruit number, and are part of the spawner escapement contributing to the next generation, but excluded from the spawner escapement abundance used to estimate stock status in the simulations. 1000 iterations of every unique combination of alpha and ER (14 x 14) were run.
```{r sim input files}

simPar <- read.csv("data\\samsim pars\\SimPars.csv") #read in 
CUPar <- read.csv("data\\samsim pars\\CUPars.csv")
srDat <- read.csv("data\\samsim pars\\srDat_infilled.csv")

# #uncomment to run the simulation
# for(k in 1:7){
#   for(u in 1:nrow(simPar)){
#     genericRecoverySim(
#       simPar = simPar[u,],
#       cuPar = CUPar,
#       srDat = srDat,
#       ricPars = sim_post_vars[[k]],
#       #nTrials = 1000, #number of trials used to produce the plots
#       nTrials = 100, #good number of iterations for testing the simulation
#       cuCustomCorrMat = pcor,
#       outDir = here::here(paste('outputs', alpha_nu[k], sep = "")))
#     }
# }

```

