---
title: "4plot & ER plot code"
author: "Colin Bailey"
date: "2025-06-26"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(cowplot)
#library(samSim)
library(tidyverse)
library(readxl)
library(ggplot2)
library(lubridate)
library(scales)
library(RColorBrewer)
library(tidyr)
library(patchwork)

dat <- read.csv("SP_1.2\\Data_in\\srDat.csv")
esc_dat <- read.csv("SP_1.2\\Data_in\\sp1.2_smu_no_escape.csv")
nic_dat <- read.csv("SP_1.2\\Data_in\\nic_dat.csv")
nic_ER <- read.csv("SP_1.2\\Data_in\\nic_ER.csv")
epad_dat <- read.csv("SP_1.2\\Data_in\\Fraser_Chinook_Releases_1975-2024.csv")
age_dat <- read.csv("SP_1.2\\Data_in\\prefishery_abundance_age_BY.csv")
pni_dat <-read.csv("SP_1.2\\Data_in\\nic_PNI.csv")

```

Code chunk to create the Spring 1.2 recruitment plot
```{r recruitment plot}

n_dat <- dat %>% mutate(t_rec = rec2 + rec3 + rec4 + rec5 + rec6,
               p2 = rec2 / t_rec,
               p3 = rec3 / t_rec,
               p4 = rec4 / t_rec,
               p5 = rec5 / t_rec,
               p6 = rec6 / t_rec,
               m_rec = t_rec / ets) %>% filter(yr %in% c(1995:2020))

###Escapement timeseries
`%!in%` <- Negate(`%in%`)
edat <- esc_dat %>% filter(Pop_Name %!in% c("NICOLA RIVER-UPPER", "SPIUS CREEK", "COLDWATER RIVER"))

bess <- edat %>% filter(CU_ID == "CK-16") %>% group_by(Year) %>% summarize(TotalInfilled = sum(TotalInfilled, na.rm = F))

dat_simp <- edat %>% filter(Pop_Name %!in% c("BESSETTE CREEK", "HARRIS CREEK", "CREIGHTON CREEK", "DUTEAU CREEK"))

dat_bess <- edat %>% filter(Pop_Name == "BESSETTE CREEK") %>% dplyr::select(-TotalInfilled) %>%
  bind_cols(., TotalInfilled = bess$TotalInfilled)

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, ret_year = Year, no_spawners = TotalInfilled) %>% 
  filter(ret_year > 1994)

e_dat[116, ] <- c(5, 2020, 1.026313)

nicced <- nic_dat %>% dplyr::select(ret_year = brood_year, no_spawners) %>% mutate(stk = 1) %>% 
  dplyr::select(stk, ret_year, no_spawners)
nicced[30:32, 1] <- c(1, 1, 1)
nicced[30:32, 2] <- c(2021:2023)
nicced[30:32, 3] <- c(965, 3447, 1688)

escape <- rbind(nicced, e_dat) %>% filter(ret_year > 1994) %>% arrange(ret_year) %>% arrange(stk)
escape$ER <- rep((nic_ER %>% filter(ret_year %in% c(1995:2023)))[,3], 5)

recs <- escape %>% mutate(p_spawn = 1-ER,
                          recs = no_spawners / p_spawn) %>% group_by(ret_year) %>% 
  summarize(smu_recs = sum(recs))


recruit <- recs %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = smu_recs/1000))+
  labs(x = "Return year", y = "Recruits (1000s)")+
  scale_y_continuous(breaks = c(0,5,10,15,20, 25, 30))+
  scale_x_continuous(limits = c(1989, 2024))+
  theme_classic()


```

Code chunk to create the Spring 1.2 catch plot
```{r catch plot}

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, ret_year = Year, no_spawners = TotalInfilled) %>% 
  filter(ret_year > 1994)

e_dat[116, ] <- c(5, 2020, 1.026313)

nicced <- nic_dat %>% dplyr::select(ret_year = brood_year, no_spawners) %>% mutate(stk = 1) %>% 
  dplyr::select(stk, ret_year, no_spawners)
nicced[30:32, 1] <- c(1, 1, 1)
nicced[30:32, 2] <- c(2021:2023)
nicced[30:32, 3] <- c(965, 3447, 1688)

escape <- rbind(nicced, e_dat) %>% filter(ret_year > 1994) %>% arrange(ret_year) %>% arrange(stk)
escape$ER <- rep((nic_ER %>% filter(ret_year %in% c(1995:2023)))[,3], 5)

cat <- escape %>% mutate(p_spawn = 1-ER,
                          recs = no_spawners / p_spawn,
                          catch = ER * recs) %>% group_by(ret_year) %>% 
  summarize(smu_catch = sum(catch))

catch <- cat %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = smu_catch/1000))+
  scale_x_continuous(limits = c(1989, 2024))+
  labs(x = "Return year", y = "Catch (1000s)")+
  theme_classic()

```

Code chunk to create the Spring 1.2 spawners plot
```{r spawners plot}

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, ret_year = Year, no_spawners = TotalInfilled) %>% 
  filter(ret_year > 1994)

e_dat[116, ] <- c(5, 2020, 1.026313)

nicced <- nic_dat %>% dplyr::select(ret_year = brood_year, no_spawners) %>% mutate(stk = 1) %>% 
  dplyr::select(stk, ret_year, no_spawners)
nicced[30:32, 1] <- c(1, 1, 1)
nicced[30:32, 2] <- c(2021:2023)
nicced[30:32, 3] <- c(965, 3447, 1688)

escape <- rbind(nicced, e_dat) %>% filter(ret_year > 1994) %>% arrange(ret_year) %>% arrange(stk)
escape$ER <- rep((nic_ER %>% filter(ret_year %in% c(1995:2023)))[,3], 5)

esc <- escape %>% group_by(ret_year) %>% summarize(smu_spawn = sum(no_spawners))

spawn <- esc %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = smu_spawn/1000))+
  labs(x = "Return year", y = "Spawner abundance (1000s)")+
  scale_y_continuous(breaks = c(0,5,10, 15, 20, 25))+
  scale_x_continuous(limits = c(1989, 2024))+
  theme_classic()

cu_esc <- escape %>% mutate(cu = ifelse(stk %in% c(1:4), "Lth", "Bst"),
                            p_spawn = 1-ER,
                            recruits = no_spawners / p_spawn) %>% 
  group_by(cu, ret_year) %>%
  summarize(sum_cu = sum(no_spawners),
            sum_cu_rec = sum(recruits))

write.csv(cu_esc, "cu_esc.csv")

```

Code chunk to create the Spring 1.2 exploitation rate plot
```{r ER plot}

ER <- nic_ER %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = tot_mort_um), colour = "black")+
  geom_hline(aes(yintercept = 0.34), colour = "red")+
  scale_x_continuous(limits = c(1989, 2024))+
  labs(x = "Return year", y = "Exploitation rate")+
  theme_classic()


```

Code chunk for combining all the plots into a single 4-panel figure
```{r 4-plot}

four_plot <- plot_grid(catch, spawn, ER, recruit,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          label_size = 12,
          align = "v",
          label_x = 0.87)

ggsave(four_plot, height = 5, width = , units = "in", filename = "4plot.png")

```

Code chunk to create the smolt-to-age_3 survival index plot
```{r surv plot}

nic_dat %>% ggplot(aes(x = brood_year, y = smolt_age3_survival*100))+
  geom_line()+
  scale_x_continuous(limits = c(1993, 2020),
                     breaks = c(1995, 2000, 2005, 2010, 2015, 2020))+
  scale_y_continuous()+
  labs(x = "Brood year", y = "Smolt to age 3 recruit survival (%)")+
  theme_classic()

ggsave(height = 3.5, width = 4.5, units = "in", filename = "surv.png")

```

Code chunk to create the Nicola age proportions plot
```{r surv plot}

## Convert data-frame to long-form ##### 

age_data <- age_data %>%
  mutate(across(ends_with("percent"), ~ as.numeric(sub("%", "", .)) / 100))


# Pivot counts
counts_long <- age_data %>%
  pivot_longer(
    cols = starts_with("age_") & !ends_with("percent"),
    names_to = "age",
    names_prefix = "age_",
    values_to = "count"
  )

# Pivot percents
percents_long <- age_data %>%
  pivot_longer(
    cols = ends_with("percent"),
    names_to = "age",
    names_pattern = "age_(\\d+)_percent",
    values_to = "percent"
  )

# Join the two long-form datasets
age_data_long <- left_join(counts_long, percents_long, by = c("BY", "age"))

# Convert age to numeric
age_data_long <- age_data_long %>%
  mutate(age = as.numeric(age))

# Preview result
print(age_data_long)
### Change age to factor #### 

age_data_long <- age_data_long %>%
  mutate(age = as.factor(age)) 


#### Create Stacked Bar Plot #####

pal <- gray.colors(3, start=0.1, end=0.9) #gray scale option
# pal <- c("darkslategrey","azure4","azure3","azure1")
#pal <- c("#88CCEE", "#CC6677", "#DDCC77")


windows()

  
  age_data_long %>%
    ggplot(aes(x= BY, y = percent, fill = age)) +
    geom_bar(stat = "identity", position = "stack") +
    labs(
      x = "Brood Year",
      y = "Proportion (Prefishery Abundance)",
      fill = "Age"
    ) +
    scale_y_continuous(
      breaks = seq(0, 1, by = 0.1),
      expand = expansion(mult = c(0, 0.1))
    ) +
    scale_x_continuous(breaks = seq(1993, 2019, by = 1)) +
    scale_fill_manual(values = pal) +
    theme_classic() +
    theme(
      legend.position = "top",
      axis.text.x = element_text(size = 10, angle = 45, hjust = 1, face = "bold"),
      axis.text.y = element_text(size = 10, hjust = 1, face = "bold", vjust = 1)
    )
  
  ggsave("Nicola_age_structure_prefishery_abundanceBY.png",plot = last_plot(), width = 7, height = 5, units = "in", dpi = 300)

```

Code chunk to create the  hatchery releases plot
```{r surv plot}

# Filter for STOCK_CU_INDEX "CK-17"
epad_data <- epad_data %>%
  filter(STOCK_CU_INDEX == "CK-17")

# Replace NA numeric values with zero (if any remain)
epad_data <- epad_data %>%
  mutate(across(where(is.numeric), ~replace_na(.x, 0)))

# Define full range of years
full_years <- 1980:2024

### Filter Fry Data ##
fry_data <- epad_data %>%
  filter(RELEASE_STAGE_NAME %in% c("Fed Fry", "Nat Fry")) %>%
  group_by(RELEASE_YEAR, STOCK_CU_INDEX, RELEASE_SITE_NAME) %>%
  summarise(TotalReleased = sum(TotalRelease, na.rm = TRUE), .groups = "drop") %>%
  mutate(Stage = "Fry") %>%
  mutate(CombinedSite = case_when(
    RELEASE_SITE_NAME %in% c("Bonaparte R", "Bonaparte R Low", "Bonaparte R Up") ~ "Bonaparte R",
    RELEASE_SITE_NAME %in% c("Nicola R", "Nicola R Up") ~ "Nicola R",
    RELEASE_SITE_NAME %in% c("Spius Cr", "Spahomin Cr", "Maka Cr") ~ "Spius Cr",
    TRUE ~ RELEASE_SITE_NAME
  )) %>%
  # Fill missing year-site combinations with 0
  complete(RELEASE_YEAR = full_years, CombinedSite, Stage, fill = list(TotalReleased = 0))


### Split Smolt Data into Smolt 0+ and Smolt 1+ ###
smolt_data <- epad_data %>%
  filter(RELEASE_STAGE_NAME %in% c("Smolt 0+", "Smolt 1+")) %>%
  group_by(RELEASE_YEAR, STOCK_CU_INDEX, RELEASE_SITE_NAME, RELEASE_STAGE_NAME) %>%
  summarise(TotalReleased = sum(TotalRelease, na.rm = TRUE), .groups = "drop") %>%
  mutate(Stage = RELEASE_STAGE_NAME) %>%  # Now Stage = "Smolt 0+" or "Smolt 1+"
  mutate(CombinedSite = case_when(
    RELEASE_SITE_NAME %in% c("Bonaparte R", "Bonaparte R Low", "Bonaparte R Up") ~ "Bonaparte",
    RELEASE_SITE_NAME %in% c("Nicola R", "Nicola R Up") ~ "Nicola",
    RELEASE_SITE_NAME %in% c("Spius Cr", "Spahomin Cr", "Maka Cr") ~ "Spius Cr",
    TRUE ~ RELEASE_SITE_NAME
  )) %>%
  # Fill missing year-site combinations with 0
  complete(RELEASE_YEAR = full_years, CombinedSite, Stage, fill = list(TotalReleased = 0))

# Split by stage
fry_data_plot <- fry_data %>% filter(Stage == "Fry")
smolt0_data_plot <- smolt_data %>% filter(Stage == "Smolt 0+")
smolt1_data_plot <- smolt_data %>% filter(Stage == "Smolt 1+")

# Plot Fry
plot_fry <- ggplot(fry_data_plot, aes(x = RELEASE_YEAR, y = TotalReleased,
                                      group = interaction(CombinedSite, Stage),
                                      color = CombinedSite)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_color_viridis_d(option = "D") +
  scale_y_continuous(labels = label_comma()) +
  scale_x_continuous(breaks = seq(1980, 2024, 4)) +
  labs(y = "Fry", x = NULL, color = NULL) +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "top",
    axis.text = element_text(size = 10),
    plot.margin = margin(10, 10, 0, 10)
  )

# Plot Smolt 0+
plot_smolt0 <- ggplot(smolt0_data_plot, aes(x = RELEASE_YEAR, y = TotalReleased,
                                            group = CombinedSite, color = CombinedSite)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_color_viridis_d(option = "D") +
  scale_y_continuous(labels = label_comma()) +
  scale_x_continuous(breaks = seq(1980, 2024, 4)) +
  labs(y = "Sub-yearling Smolts", x = NULL) +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text = element_text(size = 10),
    plot.margin = margin(0, 10, 0, 10)
  )

# Plot Smolt 1+
plot_smolt1 <- ggplot(smolt1_data_plot, aes(x = RELEASE_YEAR, y = TotalReleased,
                                            group = CombinedSite, color = CombinedSite)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_color_viridis_d(option = "D") +
  scale_y_continuous(labels = label_comma()) +
  scale_x_continuous(breaks = seq(1980, 2024, 4)) +
  labs(y = "Yearling Smolts", x = "Release Year") +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text = element_text(size = 10),
    plot.margin = margin(0, 10, 10, 10)
  )

combined_plot <- plot_fry / plot_smolt0 / plot_smolt1 + plot_layout(heights = c(1, 1, 1))
windows()
print(combined_plot)

ggsave("Spring 1.2 Hatchery Releases (3 panels).png", plot = combined_plot,
       width = 7, height = 7.5, units = "in", dpi = 300)
```

Code chunk to create the PNI plot
```{r surv plot}

pni_dat %>% ggplot(aes(x = recovery_year, y = PNI))+
  geom_line()+
  scale_x_continuous(limits = c(1992, 2024),
                     breaks = seq(1992,2024,4))+
  scale_y_continuous(limits = c(0,1),
                     breaks = seq(0,1,0.1))+
  labs(x = "Recovery Year", y = "PNI Value")+
  theme_classic()

ggsave(height = 3.5, width = 4.5, units = "in", filename = "pni.png")

```