---
title: "4plot & ER plot code"
author: "Colin Bailey"
date: "2025-06-26"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(cowplot)
library(samSim)

dat <- read.csv("SP_1.2\\Data_in\\srDat.csv")
esc_dat <- read.csv("SP_1.2\\Data_in\\sp1.2_smu_no_escape.csv")
nic_dat <- read.csv("SP_1.2\\Data_in\\nic_dat.csv")
nic_ER <- read.csv("SP_1.2\\Data_in\\nic_ER.csv")

```

Code chunk to create the Spring 1.2 recruitment plot
```{r recruitment plot}

n_dat <- dat %>% mutate(t_rec = rec2 + rec3 + rec4 + rec5 + rec6,
               p2 = rec2 / t_rec,
               p3 = rec3 / t_rec,
               p4 = rec4 / t_rec,
               p5 = rec5 / t_rec,
               p6 = rec6 / t_rec,
               m_rec = t_rec / ets) %>% filter(yr %in% c(1995:2020))

###Escapement timeseries
`%!in%` <- Negate(`%in%`)
edat <- esc_dat %>% filter(Pop_Name %!in% c("NICOLA RIVER-UPPER", "SPIUS CREEK", "COLDWATER RIVER"))

bess <- edat %>% filter(CU_ID == "CK-16") %>% group_by(Year) %>% summarize(TotalInfilled = sum(TotalInfilled, na.rm = F))

dat_simp <- edat %>% filter(Pop_Name %!in% c("BESSETTE CREEK", "HARRIS CREEK", "CREIGHTON CREEK", "DUTEAU CREEK"))

dat_bess <- edat %>% filter(Pop_Name == "BESSETTE CREEK") %>% dplyr::select(-TotalInfilled) %>%
  bind_cols(., TotalInfilled = bess$TotalInfilled)

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, ret_year = Year, no_spawners = TotalInfilled) %>% 
  filter(ret_year > 1994)

e_dat[116, ] <- c(5, 2020, 1.026313)

nicced <- nic_dat %>% dplyr::select(ret_year = brood_year, no_spawners) %>% mutate(stk = 1) %>% 
  dplyr::select(stk, ret_year, no_spawners)
nicced[30:32, 1] <- c(1, 1, 1)
nicced[30:32, 2] <- c(2021:2023)
nicced[30:32, 3] <- c(965, 3447, 1688)

escape <- rbind(nicced, e_dat) %>% filter(ret_year > 1994) %>% arrange(ret_year) %>% arrange(stk)
escape$ER <- rep((nic_ER %>% filter(ret_year %in% c(1995:2023)))[,3], 5)

recs <- escape %>% mutate(p_spawn = 1-ER,
                          recs = no_spawners / p_spawn) %>% group_by(ret_year) %>% 
  summarize(smu_recs = sum(recs))


recruit <- recs %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = smu_recs/1000))+
  labs(x = "Return year", y = "Recruits (1000s)")+
  scale_y_continuous(breaks = c(0,5,10,15,20, 25, 30))+
  scale_x_continuous(limits = c(1989, 2024))+
  theme_classic()


```

Code chunk to create the Spring 1.2 catch plot
```{r catch plot}

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, ret_year = Year, no_spawners = TotalInfilled) %>% 
  filter(ret_year > 1994)

e_dat[116, ] <- c(5, 2020, 1.026313)

nicced <- nic_dat %>% dplyr::select(ret_year = brood_year, no_spawners) %>% mutate(stk = 1) %>% 
  dplyr::select(stk, ret_year, no_spawners)
nicced[30:32, 1] <- c(1, 1, 1)
nicced[30:32, 2] <- c(2021:2023)
nicced[30:32, 3] <- c(965, 3447, 1688)

escape <- rbind(nicced, e_dat) %>% filter(ret_year > 1994) %>% arrange(ret_year) %>% arrange(stk)
escape$ER <- rep((nic_ER %>% filter(ret_year %in% c(1995:2023)))[,3], 5)

cat <- escape %>% mutate(p_spawn = 1-ER,
                          recs = no_spawners / p_spawn,
                          catch = ER * recs) %>% group_by(ret_year) %>% 
  summarize(smu_catch = sum(catch))

catch <- cat %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = smu_catch/1000))+
  scale_x_continuous(limits = c(1989, 2024))+
  labs(x = "Return year", y = "Catch (1000s)")+
  theme_classic()

```

Code chunk to create the Spring 1.2 spawners plot
```{r spawners plot}

e_dat <- bind_rows(dat_simp, dat_bess) %>% mutate(stk = ifelse(Pop_Name == "NICOLA RIVER", 1,
                                                         ifelse(Pop_Name == "BONAPARTE RIVER", 2,
                                                                ifelse(Pop_Name == "DEADMAN RIVER", 3, 
                                                                       ifelse(Pop_Name == "LOUIS CREEK", 4, 5))))) %>% 
  filter(Pop_Name != "NICOLA RIVER") %>% 
  dplyr:: select(stk, ret_year = Year, no_spawners = TotalInfilled) %>% 
  filter(ret_year > 1994)

e_dat[116, ] <- c(5, 2020, 1.026313)

nicced <- nic_dat %>% dplyr::select(ret_year = brood_year, no_spawners) %>% mutate(stk = 1) %>% 
  dplyr::select(stk, ret_year, no_spawners)
nicced[30:32, 1] <- c(1, 1, 1)
nicced[30:32, 2] <- c(2021:2023)
nicced[30:32, 3] <- c(965, 3447, 1688)

escape <- rbind(nicced, e_dat) %>% filter(ret_year > 1994) %>% arrange(ret_year) %>% arrange(stk)
escape$ER <- rep((nic_ER %>% filter(ret_year %in% c(1995:2023)))[,3], 5)

esc <- escape %>% group_by(ret_year) %>% summarize(smu_spawn = sum(no_spawners))

spawn <- esc %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = smu_spawn/1000))+
  labs(x = "Return year", y = "Spawner abundance (1000s)")+
  scale_y_continuous(breaks = c(0,5,10, 15, 20, 25))+
  scale_x_continuous(limits = c(1989, 2024))+
  theme_classic()

cu_esc <- escape %>% mutate(cu = ifelse(stk %in% c(1:4), "Lth", "Bst"),
                            p_spawn = 1-ER,
                            recruits = no_spawners / p_spawn) %>% 
  group_by(cu, ret_year) %>%
  summarize(sum_cu = sum(no_spawners),
            sum_cu_rec = sum(recruits))

write.csv(cu_esc, "cu_esc.csv")

```

Code chunk to create the Spring 1.2 exploitation rate plot
```{r ER plot}

ER <- nic_ER %>% ggplot(aes(x = ret_year))+
  geom_line(aes(x = ret_year, y = tot_mort_um), colour = "black")+
  geom_hline(aes(yintercept = 0.34), colour = "red")+
  scale_x_continuous(limits = c(1989, 2024))+
  labs(x = "Return year", y = "Exploitation rate")+
  theme_classic()


```

Code chunk for combining all the plots into a single 4-panel figure
```{r 4-plot}

four_plot <- plot_grid(catch, spawn, ER, recruit,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          label_size = 12,
          align = "v",
          label_x = 0.87)

ggsave(four_plot, height = 5, width = , units = "in", filename = "4plot.png")

```

Code chunk to create the smolt-to-age_3 survival index plot
```{r surv plot}

nic_dat %>% ggplot(aes(x = brood_year, y = smolt_age3_survival*100))+
  geom_line()+
  scale_x_continuous(limits = c(1993, 2020),
                     breaks = c(1995, 2000, 2005, 2010, 2015, 2020))+
  scale_y_continuous()+
  labs(x = "Brood year", y = "Smolt to age 3 recruit survival (%)")+
  theme_classic()

ggsave(height = 3.5, width = 4.5, units = "in", filename = "surv.png")

```




