---
title: "Nicola S-R"
author: "Colin Bailey"
date: "2025-04-15"
output: html_document
---

This code chunk loads the required packages and the data. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
library(dglm)
library(samSim)

pkgbuild::has_build_tools(debug = TRUE)

rstan_options(auto_write=T)

options(mc.cores = parallel::detectCores())

nic_dat <- read.csv("SP_1.2//Data_in//nic_dat.csv")
head(nic_dat)
```


A quick data visualization of the stock-recruit information for the Nicola River Chinook stock.
```{r data vis}

nic_dat %>% ggplot(aes(x = total_spawners, y = no_recruits))+
  geom_point()+
  theme_classic()

```


This code chunk runs a Ricker stock-recruit model using Stan that incorporates a hatchery-based smolt-to-adult survival index covariate. The model also includes a temporal autocorrelation term. The smolt-to-adult survival index is logit-transformed and standardized. Note that hatchery-origin spawners are included in the total spawners generating recruits, but only natural-origin recruits are used in the model. In addition, the model estimates the first year of smolt-to-adult survival because of a disease issue at Spius Creek Hatchery that severely-reduced smolt survival that year.
```{r ricker model}

# #creating the list of data to feed to Stan
# dat <- list("N" = nrow(nic_dat),                  #number of years of data
#             "surv" = (logit(nic_dat$smolt_age3_survival) - mean(logit(nic_dat$smolt_age3_survival))) /
#               sd(logit(nic_dat$smolt_age3_survival)), #logit-transformed smolt to age 3 adult survival
#             "lrs" = pull(nic_dat %>% mutate(lrs = log(no_recruits/total_spawners)) %>% dplyr::select(lrs)),  #log natural origin  recruits per spawner (HO & NO)
#             "S" = nic_dat$total_spawners, #vector of total spawner abundance
#             "mlogit_surv" = 0) #mean logit-transformed survival
# 
# #running the Stan model
# fit <- stan(file = "SP_1.2/Scripts/Ricker.stan", data = dat, chains=6,
#                     iter=10000, cores=6, thin = 1,
#                     control=list("max_treedepth"=15,"adapt_delta"=0.8),
#                     pars=c("beta", "alpha", "gamma", "sigma", "Smax", "rho", "surv_est", "nu_Y", "nu_rec", "srep", "smsy_85", "smsy",
#                            "umsy", "alpha_prime", "srep_prime"))
# 
# #fit summary
# out <- summary(fit)
# saveRDS(fit, "SP_1.2//Results/fit.rds")
# saveRDS(out, "SP_1.2//Results/out.rds")

fit <- readRDS("SP_1.2//Results/fit.rds")
out <- readRDS("SP_1.2//Results/out.rds")

```


This code chunk visualizes the results of the Stan model, includes diagnostic plots, and estimates Sgen for the Nicola River Chinook stock.
```{r results vis}

#mean prediction functions for Ricker with SAS index covariate
ricker <- function(x){
  (-out$summary[1,1] * x + out$summary[2,1])
}

ricker_exp <- function(x){
  exp(-out$summary[1,1] * x + out$summary[2,1]) * x
}

#drawing from the posterior distribution to show error in relationships
alpha <- as.vector(extract(fit)[2])
beta <- as.vector(extract(fit)[1])
gamma <- as.data.frame(extract(fit)[3])
post <- data.frame(alpha, beta, gamma) %>% mutate(beta = beta * -1)

qpost <- post %>% filter(alpha > quantile(post$alpha, probs = c(0.025)) & alpha < quantile(post$alpha, probs = c(0.975)))

set.seed(42)
poste <- sample_n(qpost, 1000)

#showing a sample of 1000 alternative lines within the posterior
uncertainty_ricker <- apply(as.matrix(poste), 1, function(poste) {
  stat_function(fun=function(x){(poste[1] + poste[2] * x)}, colour="blue",
                alpha = 0.02, linewidth = 0.01)
  })

uncertainty_ricker_exp <- apply(as.matrix(poste), 1, function(poste) {
  stat_function(fun=function(x){exp(poste[1] + poste[2] * x) * x}, colour="blue",
                alpha = 0.02, linewidth = 0.01)
  })

#S-R plot for relationship with SAS index covariate
nic_dat %>% ggplot(aes(x = total_spawners, y = log(no_recruits/total_spawners)))+
  geom_point()+
  uncertainty_ricker+
  geom_function(fun = ricker)+
  labs(x = "Spawners(n)", y = "log(Recruits/Spawner)")+
  theme_classic()

nic_dat %>% ggplot(aes(x = total_spawners, y = no_recruits))+
  geom_point()+
  geom_function(fun = ricker_exp)+
  geom_abline(aes(slope = 1, intercept = 0), colour = "black", linetype = "dashed")+
  uncertainty_ricker_exp+
  labs(x = "Spawners(n)", y = "Recruits(n)")+
  scale_y_continuous(limits = c(0, 30000))+
  theme_classic()


#Diagnostic Plots

##Pairs Plots
pairs(fit, pars = c("beta", "alpha", "gamma", "sigma", "surv_est", "rho"))

##Predicted vs observed
nic_dat$pred <- out$summary[8:36,1]

###predicted ~ observed
nic_dat %>% ggplot(aes(x = log(no_recruits/total_spawners), y = pred))+
  geom_point()+
  geom_abline(aes(slope = 1, intercept = 0), colour = "black", linetype = "dashed")+
  labs(x = "Observed", y = "Predicted")+
  theme_classic()

###observed - predicted ~ brood year
nic_dat %>% ggplot(aes(x = brood_year, y = log(no_recruits/total_spawners) - pred))+
  geom_point()+
  geom_abline(aes(slope = 0, intercept = 0), colour = "black", linetype = "dashed")+
  labs(x = "Brood Year", y = "Observed - Predicted")+
  theme_classic()


#creating a list of dataframes of parameter vectors to feed to the sgen solver -> note that negative values of sMSY are not sensible, thus all negative values from the posterior are converted to 0
theta = data.frame(alpha = as.vector(alpha), beta = as.vector(beta), sigma = as.vector(extract(fit)[4]))
sMSY = ifelse(unlist(data.frame(as.vector(extract(fit)[12]))) > 0, unlist(data.frame(as.vector(extract(fit)[12]))), 0)

#calculating sgen for each iteration of the Stan model
sgen <- matrix(nrow = nrow(theta), ncol = 1)
for(i in 1:nrow(theta)){
  sgen[i] <- sGenSolver(unlist(theta[i,]), sMSY[i])
  }

quantile(unlist(sgen), probs = c(0.025, 0.5, 0.975))

# #alternative method for calculating Sgen
# sGenDirect <- function(loga, b){
#  sMSY <- ( 1 - gsl::lambert_W0 (exp ( 1 - loga) ) ) / b
#  a <- exp(loga)
#  -1/b*gsl::lambert_W0(-b*sMSY/a)
# }
# 
# sgen <- matrix(nrow = nrow(theta), ncol = 1)
# for(i in 1:nrow(theta)){
#   sgen[i] <- sGenDirect(unlist(theta[i,1]), unlist(theta[i,2]))
# }

#95% CI and median sgen value for Nicola River
#quantile(unlist(sgen), probs = c(0.025, 0.5, 0.975))

```

This code chunk extracts values from the posterior of the Nicola S-R model for use in the forward simulation (see SP_1.2_SIM.Rmd).
```{r extract posterior data for samsim}

#drawing from the posterior distribution to show error in relationships
alpha <- as.vector(extract(fit)[2])
beta <- as.vector(extract(fit)[1])
sigma <- as.data.frame(extract(fit)[4])
gamma <- as.data.frame(extract(fit)[3])
alpha_prime <- as.data.frame(extract(fit)[14])
post <- data.frame(alpha, beta, sigma, gamma, alpha_prime)

poste <- post

saveRDS(poste, "data\\post.rds")

```

Code chunk for going back and forth between real space and transformed space for smolt to age 3 recruit survival
```{r survival transform}

#plot logit-transformed and standardized range of smolt survival
ss <- c(-1.2, -0.8, -0.4, 0.0, 0.4, 0.8, 1.2)

inv.logit(ss * sd(logit(nic_dat$smolt_age3_survival)) + mean(logit(nic_dat$smolt_age3_survival)))

```
