---
title: "Simulation - post processing"
author: "C. Bailey"
date: "5/29/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```


```{r, read in scenario outputs}

#retrieving the basic simulation parameterization
simPar <- read.csv("data\\samsim pars\\SimPars.csv")
CUPar <- read.csv("data\\samsim pars\\CUPars.csv")

#regenerating alpha_nu to extract the simultation results from the output folders
fit <- readRDS("SP_1.2//Results/fit.rds")
alpha_nu <- seq(from = 0.01, to = 1.61, by = 0.133)

#creating an empty list to store a dataframe for each value of alpha tested
srdat_aq <- list()

#extracting the dataframes of results
for(k in 1:length(alpha_nu)){
   hcrDatalist<-list()
   srData<- list()
   for(a in seq_len(nrow(simPar))){
      hcrDatalist[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/",
                                         simPar$nameOM[a],"/", 
                                         simPar$scenario[a],"/",
                                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_",
                                               "CU_HCR_PM.RData",sep=""), sep=""))$hcrDatout
      hcrDatalist[[a]]$scenario<-simPar$scenario[a]
      hcrDatalist[[a]]$nameOM<-simPar$nameOM[a]
      hcrDatalist[[a]]$nameMP<-simPar$nameMP[a]
      
      srData[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/", 
                         simPar$nameOM[a],"/",
                         simPar$scenario[a],"/",
                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_", "CUsrDat.RData",sep=""), sep=""))$srDatout
      srData[[a]]$scenario<-simPar$scenario[a]
      srData[[a]]$nameOM<-simPar$nameOM[a]
      srData[[a]]$nameMP<-simPar$nameMP[a]
      }
   hcrdat <- do.call(rbind,hcrDatalist)
   srdat<- do.call(rbind,srData)
   hcrdat<-hcrdat[hcrdat$year>50,] #remove burn-in period
   srdat<-srdat[srdat$year>50,]
   
   #hcrdat maybe not needed - has catch statistics though
   hcrdat=hcrdat[order(hcrdat$scenario,hcrdat$iteration,hcrdat$CU,hcrdat$year),]
   srdat=srdat[order(srdat$scenario,srdat$iteration,srdat$CU,srdat$year),]
   
   srdat_aq[[k]] <- srdat
}

#converting from a list of dataframes to a single comprehensive dataframe
sim_out <- bind_rows(srdat_aq, .id = "column_label")

```

Currently, the simulation outputs are broken out at the individual population level. They need to be summarized at the CU level, and then evaluated against sgen or 1500, whichever is higher for each CU (Lower Thompson SP 1.2 will be sgen, and Bessette SP 1.2 will be 1500). The success of each trial examines the probability of the geometric mean of the last generation of the simulation (4 years in this case) exceeding 1500 or sgen depending on the CU. Summaries will also note the probability of 1 or more subpopulations becoming extirpated during simulation.

Lower Thompson sgen = 2608    ***note -> larger Sgen because previous run of the rapid status scanner did not include the Nicola stock sgen due to hatchery influence***

Lower Thompson 20% smax = 2678 ***alternative LBM to sgen***

Bessette sgen... small population with poor contrast in S-R data, so default to 1500 as the lower benchmark
***77 fish is the calculated 20% smax***

```{r sim output summarization}

#***need to recalculate lower benchmarks and use below - reference the watershed areas that Chuck sent you and use the SREP ~ WA model
#***need to use a QET at the CU level for the first plot - set to 50 spawners for now, but see lit justifications Michael A. sent
#***need to update the Nicola SR dat that goes into the SR relationship


sim_sum <- sim_out %>% mutate(CU_ID = ifelse(CU %in% c(1:4), "lth", "bst"),
                              wildSpawners = ifelse(wildSpawners < 0, 0, wildSpawners),
                              hatcherySpawners = ifelse(hatcherySpawners < 0, 0, hatcherySpawners),
                              return = ifelse(CU == 1, wildSpawners, spawners))

sim_sum_subpop <- sim_sum %>% group_by(CU, alpha, targetER, scenario, iteration, year) %>% 
   filter(year %in% c(62)) %>% 
   group_by(CU, alpha, targetER, scenario, iteration) %>%
   mutate(subpop_extinct = ifelse(return <= 50, 0, 1)) %>% 
   group_by(CU, alpha, targetER, scenario) %>%
   summarize(p_extinct = mean(subpop_extinct))

sim_sum_CU <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(59:62)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 1500, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 2678, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(CU_ID, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

```


```{r sim results vis}

Ccols <- c("Very Low (0.00-0.04)" = "mediumpurple4",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderate (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")


cu_names <- as_labeller(c(`1` = "Nicola River", `2` = "Bonaparte River", `3` = "Deadman River", `4` = "Louis Creek",
                          `5` = "Bessette Creek"))

sim_sum_subpop %>% mutate(extinct = ifelse(p_extinct <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_extinct > 0.04 & p_extinct <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_extinct > 0.24 & p_extinct <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_extinct > 0.49 & p_extinct <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_extinct > 0.74 & p_extinct <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = extinct, fill = extinct))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   labs(y = "Canadian exploitation rate")+
   scale_fill_manual(values = Ccols, 
                     name = "P(extant)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = FALSE,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ ((. - quantile(unlist(as.vector(extract(fit)[2])),probs = c(0.5))) / 0.39), 
                                          name = "Smolt-to-adult survival index",
                                          breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0, 0.25, 0.5, 0.75, 1, 1.25, 1.5))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
   guides(fill = guide_legend(ncol = 1),
          title.position = "top")+
   theme_classic()+
   facet_wrap(.~CU,
              ncol = 2,
              labeller = cu_names)
  

CU_ID_names <- as_labeller(c("bst" = "Bessette Creek", "lth" = "Lower Thompson"))

sim_sum_CU %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(CU above 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt-to-adult survival index",
                                          breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0, 0.25, 0.5, 0.75, 1, 1.25, 1.5))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
  guides(fill = guide_legend(ncol = 1), title.position = "top") +
  labs(y = "Canadian exploitation rate", x = "Productivity [log(alpha)]") + 
   facet_wrap(. ~ CU_ID,
              nrow = 2,
              labeller = CU_ID_names)+
   theme_classic()



```
