---
title: "Simulation - post processing"
author: "C. Bailey"
date: "5/29/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```


```{r, read in scenario outputs}

#retrieving the basic simulation parameterization
simPar <- read.csv("data\\samsim pars\\SimPars.csv")
CUPar <- read.csv("data\\samsim pars\\CUPars.csv")

#regenerating alpha_nu to extract the simultation results from the output folders
fit <- readRDS("SP_1.2//Results/fit.rds")
alpha_nu <- seq(from = 0.15, to = 1.70, by = 0.125)

#creating an empty list to store a dataframe for each value of alpha tested
srdat_aq <- list()

#extracting the dataframes of results
for(k in 1:length(alpha_nu)){
   hcrDatalist<-list()
   srData<- list()
   for(a in seq_len(nrow(simPar))){
      hcrDatalist[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/",
                                         simPar$nameOM[a],"/", 
                                         simPar$scenario[a],"/",
                                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_",
                                               "CU_HCR_PM.RData",sep=""), sep=""))$hcrDatout
      hcrDatalist[[a]]$scenario<-simPar$scenario[a]
      hcrDatalist[[a]]$nameOM<-simPar$nameOM[a]
      hcrDatalist[[a]]$nameMP<-simPar$nameMP[a]
      
      srData[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/", 
                         simPar$nameOM[a],"/",
                         simPar$scenario[a],"/",
                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_", "CUsrDat.RData",sep=""), sep=""))$srDatout
      srData[[a]]$scenario<-simPar$scenario[a]
      srData[[a]]$nameOM<-simPar$nameOM[a]
      srData[[a]]$nameMP<-simPar$nameMP[a]
      }
   hcrdat <- do.call(rbind,hcrDatalist)
   srdat<- do.call(rbind,srData)
   hcrdat<-hcrdat[hcrdat$year>50,] #remove burn-in period
   srdat<-srdat[srdat$year>50,]
   
   #hcrdat maybe not needed - has catch statistics though
   hcrdat=hcrdat[order(hcrdat$scenario,hcrdat$iteration,hcrdat$CU,hcrdat$year),]
   srdat=srdat[order(srdat$scenario,srdat$iteration,srdat$CU,srdat$year),]
   
   srdat_aq[[k]] <- srdat
}

#converting from a list of dataframes to a single comprehensive dataframe
sim_out <- bind_rows(srdat_aq, .id = "column_label")

```

Currently, the simulation outputs are broken out at the individual population level. They need to be summarized at the CU level, and then evaluated against sgen or 1500, whichever is higher for each CU (Lower Thompson SP 1.2 will be sgen, and Bessette SP 1.2 will be 1500). The success of each trial examines the probability of the geometric mean of the last generation of the simulation (4 years in this case) exceeding 1500 or sgen depending on the CU. Summaries will also note the probability of 1 or more subpopulations becoming extirpated during simulation.

Lower Thompson sgen = 2608    ***note -> larger Sgen because previous run of the rapid status scanner did not include the Nicola stock sgen due to hatchery influence***

Lower Thompson 20% smax = 2678 ***alternative LBM to sgen***

Bessette sgen... small population with poor contrast in S-R data, so default to 1500 as the lower benchmark
***77 fish is the calculated 20% smax***

```{r sim output summarization}

#***need to recalculate lower benchmarks and use below - reference the watershed areas that Chuck sent you and use the SREP ~ WA model
#***need to use a QET at the CU level for the first plot - set to 50 spawners for now, but see lit justifications Michael A. sent
#***need to update the Nicola SR dat that goes into the SR relationship


sim_sum <- sim_out %>% mutate(CU_ID = ifelse(CU %in% c(1:4), "lth", "bst"),
                              wildSpawners = ifelse(wildSpawners < 0, 0, wildSpawners),
                              hatcherySpawners = ifelse(hatcherySpawners < 0, 0, hatcherySpawners),
                              return = ifelse(CU == 1, wildSpawners, spawners))


sim_sum_CU <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(59:62)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 1500, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 2678, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(CU_ID, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#QET set to 50 fish for same life-history of Chinook in the Snake River Basin, so used that here
sim_sum_CU_QET <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(59:62)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 50, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 50, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 50, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(CU_ID, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#Summarizing at the SMU level to examine likelihood of exceeding CU-status-based LRP
sim_sum_SMU <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(59:62)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 1500, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 2678, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(alpha, targetER, scenario, iteration) %>%
   summarize(smu_fail = ifelse(mean(cu_fail) < 1, 0, 1)) %>% 
   group_by(alpha, targetER, scenario) %>% 
   summarize(p_fail = mean(smu_fail))

```


```{r sim results vis}

Ccols <- c("Very Low (0.00-0.04)" = "mediumpurple4",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderate (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

CU_ID_names <- as_labeller(c("bst" = "Bessette Creek", "lth" = "Lower Thompson"))

#p(CU above LBM)
sim_sum_CU %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 | 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.6, -1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2, 1.6, 2, 2.4)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0.1, 0.3, 0.5, 0.7, 0.9, 1.1, 1.3, 1.5, 1.7),
                      limits = c(0.0873, 1.714))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
   guides(fill = guide_legend(ncol = 1), title.position = "top") +
   labs(y = "Canadian exploitation rate", 
        x = "Productivity [log(alpha)]") + 
   facet_wrap(. ~ CU_ID,
              nrow = 2,
              labeller = CU_ID_names)+
   theme_classic()+
    geom_segment(aes(x = 0.0873, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

ggsave(height = 6, width = 5.5, units = "in", filename = "sim_sum_CU.pdf")
ggsave(height = 6, width = 5.5, units = "in", filename = "sim_sum_CU.png")


#p(CU above QET)
sim_sum_CU_QET %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit >\nQuasi-Extinction Threshold)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.6, -1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2, 1.6, 2, 2.4)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0.1, 0.3, 0.5, 0.7, 0.9, 1.1, 1.3, 1.5, 1.7),
                      limits = c(0.0873, 1.714))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
  guides(fill = guide_legend(ncol = 1), title.position = "top") +
  labs(y = "Canadian exploitation rate", x = "Productivity [log(alpha)]") + 
   facet_wrap(. ~ CU_ID,
              nrow = 2,
              labeller = CU_ID_names)+
   theme_classic()+
    geom_segment(aes(x = 0.0873, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

ggsave(height = 6, width = 5.5, units = "in", filename = "sim_sum_CU_QET.pdf")
ggsave(height = 6, width = 5.5, units = "in", filename = "sim_sum_CU_QET.png")

#p(SMU above LBM)
sim_sum_SMU %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Stock Management Unit\n> Limit Reference Point)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.6, -1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2, 1.6, 2, 2.4)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0.1, 0.3, 0.5, 0.7, 0.9, 1.1, 1.3, 1.5, 1.7),
                      limits = c(0.0873, 1.714))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
  guides(fill = guide_legend(ncol = 1), title.position = "top") +
  labs(y = "Canadian exploitation rate", x = "Productivity [log(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.0873, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

ggsave(height = 3.5, width = 5.5, units = "in", filename = "sim_sum_SMU.pdf")
ggsave(height = 3.5, width = 5.5, units = "in", filename = "sim_sum_SMU.png")

```


Note that here, the best probability of both CUs exceeding 20% Smax is only 60%, and that is when the SMU is experiencing extremely high productivity. The simulation space did not explore abundances large enough to reach 66% or 90% p(exceeding LBMs).Near mean productivity (mean = 0.78, nearest alpha tested = 0.808), the greatest probability of both CUs exceeding their LBMs was 53%. The aggregate abundance associated with 53% success was 9361 fish.
```{r aggregate abundance}

#Summarizing at the SMU level to examine likelihood of exceeding the LBMs for both CUs
sim_sum_agg <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(59:62)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(lbm_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 75, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 75, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 2678, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(alpha, targetER, scenario, iteration) %>%
   summarize(smu_fail = ifelse(mean(lbm_fail) < 1, 0, 1),
             geo_mean_gen = sum(geo_mean_gen)) %>% 
   group_by(alpha, targetER, scenario) %>% 
   summarize(p_fail = mean(smu_fail),
             geo_mean_gen = mean(geo_mean_gen))


#p(SMU above LBM)
sim_sum_agg %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Both Conservation Units\n> 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.6, -1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2, 1.6, 2, 2.4)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0.1, 0.3, 0.5, 0.7, 0.9, 1.1, 1.3, 1.5, 1.7),
                      limits = c(0.0873, 1.714))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
  guides(fill = guide_legend(ncol = 1), title.position = "top") +
  labs(y = "Canadian exploitation rate", x = "Productivity [log(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.0873, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.0873, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

ggsave(height = 3.5, width = 5.5, units = "in", filename = "sim_sum_agg.pdf")
ggsave(height = 3.5, width = 5.5, units = "in", filename = "sim_sum_agg.png")

```



```{r subpop plotting}

sim_sum_subpop <- sim_sum %>% group_by(CU, alpha, targetER, scenario, iteration, year) %>% 
   filter(year %in% c(62)) %>% 
   group_by(CU, alpha, targetER, scenario, iteration) %>%
   mutate(subpop_extinct = ifelse(return <= 50, 0, 1)) %>% 
   group_by(CU, alpha, targetER, scenario) %>%
   summarize(p_extinct = mean(subpop_extinct))

cu_names <- as_labeller(c(`1` = "Nicola River", `2` = "Bonaparte River", `3` = "Deadman River", `4` = "Louis Creek",
                          `5` = "Bessette Creek"))

sim_sum_subpop %>% mutate(extinct = ifelse(p_extinct <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_extinct > 0.04 & p_extinct <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_extinct > 0.24 & p_extinct <= 0.49, "Moderate (0.25-0.49)",
                                                        ifelse(p_extinct > 0.49 & p_extinct <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_extinct > 0.74 & p_extinct <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = extinct, fill = extinct))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   labs(y = "Canadian exploitation rate")+
   scale_fill_manual(values = Ccols, 
                     name = "P(extant)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = FALSE,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderate (0.25-0.49)", "Moderately High (0.50-0.74)",
                                "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ ((. - quantile(unlist(as.vector(extract(fit)[2])),probs = c(0.5))) / 0.39), 
                                          name = "Smolt-to-adult survival index",
                                          breaks = c(-2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2)),
                      name = "Productivity [log(alpha)]", expand = c(0,0),
                      breaks = c(0, 0.25, 0.5, 0.75, 1, 1.25, 1.5))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.6, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
   guides(fill = guide_legend(ncol = 1),
          title.position = "top")+
   theme_classic()+
   facet_wrap(.~CU,
              ncol = 2,
              labeller = cu_names)
```
