---
title: "SP_1.2_SIM"
author: "Colin Bailey"
date: "2025-04-24"
output: html_document
---

This code chunk loads the required packages and the data. Note that a specific version of samSim is required (see commented-out code to install the correct version), and that if a different version of samSim is installed on your computer, you may need to manually delete it from your library to get the new version to install correctly.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(viridis)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
#install.packages("remotes")    #run this line and the next once to get access to the sgen solver that DFO has developed
#remotes::install_github("Pacific-salmon-assess/samSim", ref="sbccnk-hatch", force=TRUE)

library(samSim) #package that DFO created with the sgen solver to estimate sgen given stock recruit parameters

pkgbuild::has_build_tools(debug = TRUE)

rstan_options(auto_write=T)

options(mc.cores = parallel::detectCores())

#escapement data
esc_dat <- read.csv("SP_1.2\\Data_in\\sp1.2_smu_no_escape.csv")
head(esc_dat)

#posterior data
pos_dat <- readRDS("data\\post.rds")
head(pos_dat)

#age data
age_dat <- read.csv("SP_1.2\\Data_in\\rec_age_comp.csv")
head(age_dat)

#Nicola S-R data
nic_dat <- read.csv("SP_1.2//Data_in//nic_dat.csv")
```


This code chunk prepares data for use in 'samSim' (the forward simulation tool). The key data inputs in this chunk include:
1) a correlation matrix of the sub-populations being simulated
2) watershed area-based estimates of SREP for sub-populations without S-R models (all except Nicola)
3) a posterior for each sub-population with Ricker model parameters "alpha", "beta", and "sigma" (*detailed explanation of the calculation of these parameters below this list*)
4) mean proportions and variance in age at return

*Description of the posteriors for the sub-populations*
The 'samSim' package can produce forward simulations of salmon abundance using fixed Ricker parameter values or posteriors from Ricker stock-recruit models. Here, we wanted to simulate abundances in the sub-populations of the Fraser Spring 1.2 Chinook SMU across a realistic fixed range of alpha values (productivity) while still incorporating uncertainty from models' posteriors used to:
1) Generate a CI of alpha values from the Nicola S-R data to be used for all sub-populations
2) Generate beta and sigma values for the Nicola River
3) Generate watershed area-based SREPs for the non-Nicola sub-populations from which beta values can be derived using Nicola alpha values

This code chunk creates sub-population-specific posteriors across a fixed range of alpha values with realistically-varying values of beta and sigma. 

This is accomplished first by generating a posterior including alpha, beta and sigma for each sub-population. The Nicola River posterior is generated by taking 1000 random samples (rows) from the Nicola S-R model posterior. For the remaining sub-populations, the order of the Nicola posterior rows were randomized, and the beta values removed. Then, new beta values for each sub-population were calculated using the equation:

beta = alpha prime / srep 

to derive estimates of beta for the non-Nicola posteriors. Posteriors of SREP for each non-Nicola sub-population were generated using the Parken habitat model (see "R\\srep_wa_analysis_predict.R") and predicting SREP based on watershed area. 1000 random samples were drawn from each posterior, and then used to calculate beta. Note that alpha prime is used in this instance because alpha prime was used to calculate SREPs in the data fed to the Parken habitat model, but are not used below for ____ reasons.

The second step is to take the posteriors, calculate SREP using the following equation:

srep = alpha / beta

and then replicate each sub-population posterior by the number of unique (14) alpha values evenly spaced across the 80% CI of the estimate of alpha for the Nicola stock. For each replication, the random alpha values from the Nicola posterior are replaced with one of the 14 fixed values of alpha, and then beta is recalculated based on SREP and the fixed alpha value according to the following equation:

beta = alpha / srep

which produces varying beta values relative to fixed values of alpha.

```{r sim data prep}

###Escapement correlation### - filter out pops with high hatchery influence & no NO estimates, and filter out years with NAs
`%!in%` <- Negate(`%in%`)
dat <- esc_dat %>% filter(Pop_Name %!in% c("NICOLA RIVER-UPPER", "SPIUS CREEK", "COLDWATER RIVER"))

bess <- dat %>% filter(CU_ID == "CK-16") %>% group_by(Year) %>% summarize(TotalInfilled = sum(TotalInfilled, na.rm = F))

dat_simp <- dat %>% filter(Pop_Name %!in% c("BESSETTE CREEK", "HARRIS CREEK", "CREIGHTON CREEK", "DUTEAU CREEK"))

dat_bess <- dat %>% filter(Pop_Name == "BESSETTE CREEK") %>% dplyr::select(-TotalInfilled) %>%
  bind_cols(., TotalInfilled = bess$TotalInfilled)

dat <- bind_rows(dat_simp, dat_bess)

source("R\\pop_cor.R")

pcor <- pop_cor(dat) #population correlation matrix

###Estimate srep from watershed areas for populations without beta estimates###
wa = c(4521, 3498.64, 889.64, 519.39, 276.21)
pop = c("Nicola River", "Bonaparte River", "Deadman River", "Louis Creek", "Bessette Creek")

nu_wa = data.frame(pop, wa)

source("R\\srep_wa_analysis_predict.R")

nu_srep <- srep_est(nu_wa)
names(nu_srep) <- c(unique(nu_wa$pop))
nu_srep <- nu_srep[sample(nrow(nu_srep), 30000),] #srep posterior, 1000 samples each per population

###Estimate beta posterior from nu_srep posterior###
post <- readRDS("data\\post.rds")

srep_post <- nu_srep %>% dplyr::select(-`Nicola River`) %>% pivot_longer(names_to = "pop", cols = c(1:4)) %>% arrange(pop)

#creating alpha-sigma-gamma-alpha_prime posterior for Bonaparte, Deadman, Louis and Bessette
bt <- post[sample(nrow(post), 30000),]
dm <- post[sample(nrow(post), 30000),]
ls <- post[sample(nrow(post), 30000),]
bs <- post[sample(nrow(post), 30000),]

h1 <- rbind(bt,dm)
h2 <- rbind(ls,bs)
w <- rbind(h1,h2) %>% dplyr::select(-beta)

srep_post$alpha_prime <- w$alpha_prime
srep_post$alpha <- ifelse(w$alpha > 0, w$alpha, 0)
srep_post$sigma <- w$sigma
srep_post$gamma <- w$gamma

nu_beta <- srep_post %>% mutate(srep = value,
                     beta = alpha_prime/srep) %>%
  dplyr::select(alpha, beta, sigma, gamma, pop)

nu_post <- post %>%
  mutate(pop = "Nicola River",
         alpha = ifelse(alpha > 0, alpha, 0)) %>% 
  dplyr::select(alpha, beta, sigma, gamma, pop)

sim_post <- rbind(nu_beta, nu_post) %>% 
  mutate(stk = ifelse(pop == "Nicola River", 1,
                      ifelse(pop == "Bonaparte River", 2,
                             ifelse(pop == "Deadman River", 3,
                                    ifelse(pop == "Louis Creek", 4, 5))))) %>% 
  dplyr::select(stk, alpha, beta, sigma)#full posterior to feed to the simulation

sim_post=sim_post[order(sim_post$stk),]

#manipulate the posterior into 17 posteriors, each with a fixed value for alpha and varying values of beta based on srep - this preserves the posterior variance while allowing fixed values of alpha to test across the plausible range for the icecream plots
#note that alpha values are based on the 2 SD range in SAS 
alpha_nu <- seq(from = 0.1, to = 1.75, by = 0.125)
stk_beta <- list()
beta_nu <- list()
b_ks <- c(7.142857,
             (7.142857*2),
             (7.142857*3),
             (7.142857*4),
             (7.142857*5),
             (7.142857*6),
             (7.142857*7),
             (7.142857*8),
             (7.142857*9),
             (7.142857*10),
             (7.142857*11),
             (7.142857*12),
             (7.142857*13)) * 0.01


for(s in 1:5){
  stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta < quantile(beta, probs = c(b_ks[1]))), 1000)[,3:4]
}
beta_nu[[1]] <- bind_rows(stk_beta, .id = "column_label")

for(i in 2:(length(alpha_nu) - 1)){
  for(s in 1:5){
    stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta >= quantile(beta, probs = c(b_ks[i-1])) &
                                                                      beta < quantile(beta, probs = c(b_ks[i]))), 1000)[,3:4]
  }
  
  
  sim_post[sim_post$beta >= quantile(sim_post$beta, probs = c(b_ks[i-1])) & 
                            sim_post$beta < quantile(sim_post$beta, probs = c(b_ks[i])), 3:4]
  
  beta_nu[[i]] = bind_rows(stk_beta, .id = "column_label")
}

for(s in 1:5){
  stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta >= quantile(beta, probs = c(b_ks[13]))), 1000)[,3:4]
}
beta_nu[[14]] <- bind_rows(stk_beta, .id = "column_label")

sim_post_vars <- list()

for(i in 1:length(alpha_nu)){
  sim_post_vars[[i]] <- assign(paste("sim_post_a", alpha_nu[i], sep =""), rep(99, 5000))
}

for(i in 1:length(alpha_nu)){
  sim_post_vars[[i]] <- sample_n(sim_post, 5000) %>% mutate(alpha = alpha_nu[i], 
                                                            beta = 99,
                                                            sigma = 99)
  sim_post_vars[[i]]$stk <- c(rep(1,1000), rep(2,1000), rep(3,1000), rep(4,1000), rep(5,1000))
}


for(i in 1:length(sim_post_vars)){
  sim_post_vars[[i]][,3:4] = beta_nu[[i]][2:3]
}

###Tau for age variance and mean proportions at age (3,4,5)###
ppnMat <- age_dat %>% mutate(p3 = a3/(a3 + a4 + a5),
                   p4 = a4/(a3 + a4 + a5),
                   p5 = a5/(a3 + a4 + a5)) %>% dplyr::select(p3, p4, p5)

source("R\\age_tau.R")

tau <- tau_comp(ppnMat)$tau #tau 
m_props <- tau_comp(ppnMat)$pa #mean age proportions

```


Hatchery spawners are incorporated into the simulation analysis for the Nicola River sub-population. Hatchery spawners are included with total spawners contributing to the next generation of recruits, but are not included in the recruits for the simulation. This means that we are not considering the differential productivity between hatchery- and natural-origin spawners in these analyses. In addition, hatchery-origin spawners are not included in the CU spawner totals used to evaluate whether a CU is above its lower benchmark.
```{r, hatchery scalar estimation}

nic_dat$hatchery_spawners=nic_dat$total_spawners-nic_dat$no_spawners #hatchery spawner abundance
nic_dat$p_hatch_no=nic_dat$hatchery_spawners/nic_dat$no_spawners #ratio of hatchery:natural origin spawners

#estimate gamma distribution parameters
fit<- dglm::dglm(nic_dat$p_hatch_no~1,family=Gamma(link='log'))
mu<- exp(fit$coefficients[1])
shape<- exp(fit$dispersion.fit$coefficients[1])
scale<- mu/shape
max_hsp<- max(nic_dat$hatchery_spawners)
par(mfrow=c(1,2))
hist(nic_dat$p_hatch_no,main='observed ratio of hatchery:natural origin spawners')
hist(rgamma(1000,shape=shape,scale=scale),main='simulated gamma distribution of ratios')

```

When calculating beta from srep for the posterior, use alpha prime to back-calculate to beta from the predicted SREPs from the habitat model

Note that HO recruits are added to the total recruit number, and are part of the spawner escapement contributing to the next generation, but excluded from the spawner escapement abundance used to estimate stock status in the simulations.

```{r sim input files}


###samSim struggles when too much of the posterior is sampled - must be some values of beta or sigma that it cannot handle
simPar <- read.csv("data\\samsim pars\\SimPars.csv")
CUPar <- read.csv("data\\samsim pars\\CUPars.csv")
#srDat <- read.csv("data\\samsim pars\\srDat.csv")

for(k in 1:length(alpha_nu)){
  for(u in 1:nrow(simPar)){
    genericRecoverySim(
      simPar = simPar[u,],
      cuPar = CUPar,
      #srDat = srDat,
      ricPars = sim_post_vars[[k]],
      nTrials = 2000,
      cuCustomCorrMat = pcor,
      outDir = here::here(paste('outputs', alpha_nu[k], sep = "")))
    }
}

```

