---
title: "SP_1.2_SIM"
author: "Colin Bailey"
date: "2025-04-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
#install.packages("remotes")    #run this line and the next once to get access to the sgen solver that DFO has developed
#remotes::install_github("Pacific-salmon-assess/samSim", ref="sbccnk-hatch", force=TRUE)

library(samSim) #package that DFO created with the sgen solver to estimate sgen given stock recruit parameters

pkgbuild::has_build_tools(debug = TRUE)

rstan_options(auto_write=T)

options(mc.cores = parallel::detectCores())

#escapement data
esc_dat <- read.csv("SP_1.2\\Data_in\\sp1.2_smu_no_escape.csv")
head(esc_dat)

#posterior data
pos_dat <- readRDS("data\\post.rds")
head(pos_dat)

#age data
age_dat <- read.csv("SP_1.2\\Data_in\\rec_age_comp.csv")
head(age_dat)

```


```{r sim data prep}


###Escapement correlation### - filter out pops with high hatchery influence & no NO estimates, and filter out years with NAs
`%!in%` <- Negate(`%in%`)
dat <- esc_dat %>% filter(Pop_Name %!in% c("NICOLA RIVER-UPPER", "SPIUS CREEK", "COLDWATER RIVER"))

bess <- dat %>% filter(CU_ID == "CK-16") %>% group_by(Year) %>% summarize(TotalInfilled = sum(TotalInfilled, na.rm = F))

dat_simp <- dat %>% filter(Pop_Name %!in% c("BESSETTE CREEK", "HARRIS CREEK", "CREIGHTON CREEK", "DUTEAU CREEK"))

dat_bess <- dat %>% filter(Pop_Name == "BESSETTE CREEK") %>% dplyr::select(-TotalInfilled) %>%
  bind_cols(., TotalInfilled = bess$TotalInfilled)

dat <- bind_rows(dat_simp, dat_bess)

source("R\\pop_cor.R")

pcor <- pop_cor(dat) #population correlation matrix

###Estimate srep from watershed areas for populations without beta estimates###
wa = c(3499, 890, 519, 388)
pop = c("Bonaparte River", "Deadman River", "Louis Creek", "Bessette Creek")

nu_wa = data.frame(pop, wa)

source("R\\srep_wa_analysis_predict.R")

nu_srep <- srep_est(nu_wa)
names(nu_srep) <- c(unique(nu_wa$pop))
nu_srep <- nu_srep[sample(nrow(nu_srep), 1000),] #srep posterior, 1000 samples each per population

###Estimate beta posterior from nu_srep posterior###
post <- readRDS("data\\post.rds")

srep_post <- nu_srep %>% pivot_longer(names_to = "pop", cols = c(1:4)) %>% arrange(pop)

#creating alpha-sigma-gamma-alpha_prime posterior for Bonaparte, Deadman, Louis and Bessette
bt <- post[sample(nrow(post), 1000),]
dm <- post[sample(nrow(post), 1000),]
ls <- post[sample(nrow(post), 1000),]
bs <- post[sample(nrow(post), 1000),]

h1 <- rbind(bt,dm)
h2 <- rbind(ls,bs)
w <- rbind(h1,h2) %>% dplyr::select(-beta)

srep_post$alpha_prime <- w$alpha_prime
srep_post$alpha <- ifelse(w$alpha > 0, w$alpha, 0)
srep_post$sigma <- w$sigma
srep_post$gamma <- w$gamma

nu_beta <- srep_post %>% mutate(srep = value,
                     beta = alpha_prime/srep) %>%
  dplyr::select(alpha, beta, sigma, gamma, pop)

nu_post <- post %>%
  mutate(pop = "Nicola River",
         alpha = ifelse(alpha > 0, alpha, 0)) %>% 
  dplyr::select(alpha, beta, sigma, gamma, pop)

sim_post <- rbind(nu_beta, nu_post) %>% 
  mutate(stk = ifelse(pop == "Nicola River", 1,
                      ifelse(pop == "Bonaparte River", 2,
                             ifelse(pop == "Deadman River", 3,
                                    ifelse(pop == "Louis Creek", 4, 5))))) %>% 
  dplyr::select(stk, alpha, beta, sigma)#full posterior to feed to the simulation

sim_post=sim_post[order(sim_post$stk),]

#mainpulate the posterior into 11 posteriors, each with a fixed value for alpha and varying values of beta based on srep - this preserves the posterior variance while allowing fixed values of alpha to test across the plausible range for the icecream plots
#note that alpha values are based on the 95% CI of alpha from the Nicola SR function, where more values of alpha are tested closer to the median of the posterior (where the greatest confidence in the estimate of alpha lays)

fit <- readRDS("SP_1.2//Results/fit.rds")
quants <- c(0.15, 0.25, 0.35, 0.40, 0.45, 0.50, 0.55, 0.60, 0.65, 0.75, 0.85)
alpha_nu <- unlist(as.vector(extract(fit)[2])) %>% 
  quantile(probs = quants)

sim_post_a15 <- rep(99, 1000)
sim_post_a25 <- rep(99, 1000)
sim_post_a35 <- rep(99, 1000)
sim_post_a40 <- rep(99, 1000)
sim_post_a45 <- rep(99, 1000)
sim_post_a50 <- rep(99, 1000)
sim_post_a55 <- rep(99, 1000)
sim_post_a60 <- rep(99, 1000)
sim_post_a65 <- rep(99, 1000)
sim_post_a75 <- rep(99, 1000)
sim_post_a85 <- rep(99, 1000)

sim_post_vars <- list(sim_post_a15,sim_post_a25,sim_post_a35,sim_post_a40,sim_post_a45,sim_post_a50,sim_post_a55,sim_post_a60,sim_post_a65,sim_post_a75,sim_post_a85)

for(i in 1:length(alpha_nu)){
  sim_post_vars[[i]] <- sim_post %>% mutate(srep = alpha/beta,
                                    alpha = alpha_nu[i],
                                    beta = alpha/srep) %>% dplyr::select(-srep)
}


###Tau for age variance and mean proportions at age (3,4,5)###
ppnMat <- age_dat %>% mutate(p3 = a3/(a3 + a4 + a5),
                   p4 = a4/(a3 + a4 + a5),
                   p5 = a5/(a3 + a4 + a5)) %>% dplyr::select(p3, p4, p5)

source("R\\age_tau.R")

tau <- tau_comp(ppnMat)$tau #tau 
m_props <- tau_comp(ppnMat)$pa #mean age proportions

```


When calculating beta from srep for the posterior, use alpha prime to back-calculate to beta from the predicted SREPs from the habitat model

Note that HO recruits are added to the total recruit number, and are part of the spawner escapement contributing to the next generation, but excluded from the spawner escapement abundance used to estimate stock status in the simulations.

```{r sim input files}

simPar <- read.csv("data\\samsim pars\\SimPars.csv")
CUPar <- read.csv("data\\samsim pars\\CUPars.csv")

for(k in 1:length(alpha_nu)){
  for(u in 1:nrow(simPar)){
    genericRecoverySim(
      simPar = simPar[u,],
      cuPar = CUPar,
      ricPars = sim_post_vars[[k]],
      nTrials = 100,
      cuCustomCorrMat = pcor,
      outDir = here::here(paste('outputs', quants[k], sep = "")))
    }
}






```

