---
title: "Ricker Parameter Estimation"
author: "Colin Bailey"
date: "2025-08-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
library(dglm)

pkgbuild::has_build_tools(debug = TRUE)
rstan_options(auto_write=T)
options(mc.cores = parallel::detectCores())

#read in and check data
nic_dat <- read.csv("SP_1.2//Data_in//nic_dat.csv") #data required to run stock-recruit curve to generate Nicola alpha from which the Spring and Summer 1.3 alpha values will be derived
fec_dat <- read.csv("data//fecundity.csv") #fecundity data for adjusting Nicola alpha parameter for use in Spring and Summer 1.3 simulations
head(nic_dat)
```

This code chunk runs a Ricker stock-recruit model using Stan that incorporates a hatchery-based smolt-to-age_3 survival (SS) index covariate. The model also includes an AR-1 temporal autocorrelation structure. The SS index is logit-transformed and standardized (z-scored). Note that hatchery-origin spawners are included in the total spawners generating recruits, but only natural-origin recruits are used in the model. In addition, the model estimates the first year (1992) of the SS index because of a disease issue at Spius Creek Hatchery that severely-reduced smolt survival that year. The purpose of running this model with Nicola data is to produce a Fraser stream-type chinook productivity estimate that can be adjust below for Spring/Summer 1.3 chinook.
```{r ricker model}

#un-comment the section below to re-run the Nicola stock-recruit analysis

#creating the list of data to feed to Stan
dat <- list("N" = nrow(nic_dat),                  #number of years of data
            "surv" = (logit(nic_dat$smolt_age3_survival) - mean(logit(nic_dat$smolt_age3_survival))) /
              sd(logit(nic_dat$smolt_age3_survival)), #logit-transformed smolt to age 3 adult survival
            "lrs" = pull(nic_dat %>% mutate(lrs = log(no_recruits/total_spawners)) %>% dplyr::select(lrs)),  #log natural origin  recruits per spawner (HO & NO)
            "S" = nic_dat$total_spawners, #vector of total spawner abundance
            "mlogit_surv" = 0, #mean logit-transformed survival
            "nicN" = length(pull(fec_dat %>% filter(SMU == "sp_12"))),
            "suN" = length(pull(fec_dat %>% filter(SMU == "su_13"))),
            "spN" = length(pull(fec_dat %>% filter(SMU == "sp_13"))),
            "fnic" = pull(fec_dat %>% filter(SMU == "sp_12")),
            "fsu" = pull(fec_dat %>% filter(SMU == "su_13")),
            "fsp" = pull(fec_dat %>% filter(SMU == "sp_13"))) 

#running the Stan model
fit <- stan(file = "R//Ricker_mod_alpha.stan", data = dat, chains=6,
                    iter=10000, cores=6, thin = 1,
                    control=list("max_treedepth"=15,"adapt_delta"=0.8),
                    pars=c("beta", "alpha", "gamma", "sigma", "Smax", "rho", "surv_est", "f_nic", "f_su", "f_sp", "alpha_su",
                           "alpha_sp", "umsy_su", "umsy_sp", "alpha_prime_su", "alpha_prime_sp"))

#extract alpha posterior
alpha_su <- as.vector(extract(fit)[11]) #need to set correct extraction number
alpha_sp <- as.vector(extract(fit)[12]) #need to set correct extraction number
alpha_prime_su <- as.vector(extract(fit)[15]) #need to set correct extraction number
alpha_prime_sp <- as.vector(extract(fit)[16]) #need to set correct extraction number
umsy_su <- as.vector(extract(fit)[13]) #need to set correct extraction number
umsy_sp <- as.vector(extract(fit)[14]) #need to set correct extraction number
  
```

