---
title: "Ricker Parameter Estimation"
author: "Colin Bailey"
date: "2025-08-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
library(dglm)

pkgbuild::has_build_tools(debug = TRUE)
rstan_options(auto_write=T)
options(mc.cores = parallel::detectCores())

#read in and check data
nic_dat <- read.csv("SP_1.2//Data_in//nic_dat.csv") #data required to run stock-recruit curve to generate Nicola alpha from which the Spring and Summer 1.3 alpha values will be derived
fec_dat <- read.csv("data//fecundity.csv") #fecundity data for adjusting Nicola alpha parameter for use in Spring and Summer 1.3 simulations
head(nic_dat)

set.seed(1352)
```


The fecundity data from SEP for non Lower Chilcotin fish include measurements that are averages across more than one fish, but the original individual-based measures are missing (these measures came from Big Bar monitoring). To avoid inflating or underestimating certainty, we simulate the missing fecundity measures using the variance of all SP 1.3 fecundity measures (individual and average).
```{r data manip}
sp_13_sd <- sd((fec_dat %>% filter(SMU == "sp_13"))[,5])

f_dat <- fec_dat %>% mutate(sd = sp_13_sd) %>% 
  slice(rep(1:n(), times = n_sampled)) %>% 
  mutate(f_new = ifelse(n_sampled == 1, fecundity, rnorm(n(), fecundity, sd))) %>% 
  dplyr::select(SMU, stock, year, fecundity = f_new)

f_dat %>% mutate(stock = ifelse(SMU == "sp_12", "Fraser Spring 1.2",
                                ifelse(SMU == "sp_13", "Fraser Spring 1.3", "Fraser Summer 1.3"))) %>% 
  ggplot(aes(x = fecundity, fill = stock, colour = NULL))+
  geom_histogram(alpha = 0.5)+
  scale_fill_manual(values = c("#D55E00", "#009E73", "#0072B2"),
                    labels = c("Fraser Spring 1.2", "Fraser Spring 1.3", "Fraser Summer 1.3"))+
  labs(x = "Fecundity", y = "Density")+
  facet_wrap(~SMU, nrow = 3)+
  theme_classic()

ggsave(height = 2.5, width = 3, units = "in", filename = "fec_dat.pdf")
```


This code chunk runs a Ricker stock-recruit model using Stan that incorporates a hatchery-based smolt-to-age_3 survival (SS) index covariate. The model also includes an AR-1 temporal autocorrelation structure. The SS index is logit-transformed and standardized (z-scored). Note that hatchery-origin spawners are included in the total spawners generating recruits, but only natural-origin recruits are used in the model. In addition, the model estimates the first year (1992) of the SS index because of a disease issue at Spius Creek Hatchery that severely-reduced smolt survival that year. The purpose of running this model with Nicola data is to produce a Fraser stream-type chinook productivity estimate that can be adjust below for Spring/Summer 1.3 chinook.
```{r ricker model}

#un-comment the section below to re-run the Nicola stock-recruit analysis

#creating the list of data to feed to Stan
dat <- list("N" = nrow(nic_dat),                  #number of years of data
            "surv" = (logit(nic_dat$smolt_age3_survival) - mean(logit(nic_dat$smolt_age3_survival))) /
              sd(logit(nic_dat$smolt_age3_survival)), #logit-transformed smolt to age 3 adult survival
            "lrs" = pull(nic_dat %>% mutate(lrs = log(no_recruits/total_spawners)) %>% dplyr::select(lrs)),  #log natural origin  recruits per spawner (HO & NO)
            "S" = nic_dat$total_spawners, #vector of total spawner abundance
            "mlogit_surv" = 0, #mean logit-transformed survival
            "nicN" = length(pull(f_dat %>% filter(SMU == "sp_12"))),
            "suN" = length(pull(f_dat %>% filter(SMU == "su_13"))),
            "spN" = length(pull(f_dat %>% filter(SMU == "sp_13"))),
            "fnic" = (f_dat %>% filter(SMU == "sp_12"))[,4],
            "fsu" = (f_dat %>% filter(SMU == "su_13"))[,4],
            "fsp" = (f_dat %>% filter(SMU == "sp_13"))[,4]) 

#running the Stan model
fit <- stan(file = "R//Ricker_mod_alpha.stan", data = dat, chains=6,
                    iter=10000, cores=6, thin = 1, seed = 1352,
                    control=list("max_treedepth"=15,"adapt_delta"=0.8),
                    pars=c("beta", "alpha", "gamma", "sigma", "Smax", "rho", "surv_est", "f_nic", "f_su", "f_sp", "alpha_su",
                           "alpha_sp", "umsy_su", "umsy_sp", "alpha_prime_su", "alpha_prime_sp", "umsy_nic", "nu_Y", "alpha_prime_nic"))

saveRDS(fit, "R//sp_su_1.3_fit.RDS")

fit <- readRDS("R//sp_su_1.3_fit.RDS")

#extract posteriors
f_nic <- as.vector(extract(fit)[8])
f_sp <- as.vector(extract(fit)[10])
f_su <- as.vector(extract(fit)[9])
alpha_nic <- as.vector(extract(fit)[2]) #need to set correct extraction number
alpha_sp <- as.vector(extract(fit)[12]) #need to set correct extraction number
alpha_su <- as.vector(extract(fit)[11]) #need to set correct extraction number
alpha_prime_sp <- as.vector(extract(fit)[16]) #need to set correct extraction number
alpha_prime_su <- as.vector(extract(fit)[15]) #need to set correct extraction number
umsy_nic <- as.vector(extract(fit)[17]) #need to set correct extraction number
umsy_sp <- as.vector(extract(fit)[14]) #need to set correct extraction number
umsy_su <- as.vector(extract(fit)[13]) #need to set correct extraction number

out <- summary(fit)

nuy <- out$summary[18:46,1]
lrs <- pull(nic_dat %>% mutate(lrs = log(no_recruits/total_spawners)) %>% dplyr::select(lrs))

preds <- data.frame(nuy, lrs)
preds$year <- c(1992:2020)

preds %>% ggplot(aes(x = year, y = nuy-lrs))+
  geom_point()+
  geom_hline(yintercept = 0, colour = "Red")+
  labs(x = "Brood Year", y = "Predicted - Observed")+
  theme_classic()

nic_dat %>% ggplot(aes(x = total_spawners, y = no_recruits))+
  geom_point()+
  geom_function(fun = function(x) exp(median(alpha_nic$alpha) - median(as.vector(extract(fit)[1])$beta)*x)*x)+
  labs(x = "Spawners", y = "Recruits")+
  theme_classic()

ggsave(height = 2.5, width = 3, units = "in", filename = "nic_sr_fit.pdf")
  

##############SR Function Plot####################

#mean prediction function for real space Ricker with SS index covariate
ricker_exp <- function(x){
  exp(-out$summary[1,1] * x + out$summary[2,1]) * x
}

#drawing from the posterior distribution to plot error in relationships
alpha <- as.vector(extract(fit)[2])
beta <- as.vector(extract(fit)[1])
gamma <- as.data.frame(extract(fit)[3])
post <- data.frame(alpha, beta, gamma) %>% mutate(beta = beta * -1)

#sampling from the posterior using rows that fall within the 95% CI for alpha
qpost <- post %>% filter(alpha > quantile(post$alpha, probs = c(0.025)) & alpha < quantile(post$alpha, probs = c(0.975)))

set.seed(1352)
poste <- sample_n(qpost, 1000)

#taking a sample of 1000 lines from the 95% CI of the posterior for the normal space Ricker
uncertainty_ricker_exp <- apply(as.matrix(poste), 1, function(poste) {
  stat_function(fun=function(x){exp(poste[1] + poste[2] * x) * x}, colour="blue",
                alpha = 0.1, linewidth = 0.05)
  })

preds$spawn <- nic_dat$no_spawners

#normal space Ricker plot
preds %>% ggplot(aes(x = spawn, y = exp(lrs)*spawn))+
  uncertainty_ricker_exp+
  geom_point()+
  geom_function(fun = ricker_exp)+
  geom_abline(aes(slope = 1, intercept = 0), colour = "black", linetype = "dashed")+
  labs(x = "Spawners(n)", y = "Recruits(n)")+
  scale_y_continuous(limits = c(0, 25000))+
  theme_classic()

ggsave(height = 3.5, width = 4, units = "in", filename = "nic_sr_fit.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "nic_sr_fit.png")



################Fecundity results

fnic <- f_nic$f_nic
fsu <- f_su$f_su
fsp <- f_sp$f_sp

f_new <- c(fnic, fsu, fsp)
stock <- c(rep("Fraser Spring 1.2", length(fnic)), rep("Fraser Summer 1.3", length(fsu)), rep("Fraser Spring 1.3", length(fsp)))
fec_dat <- data.frame(f_new, stock)

fec_dat %>% 
  ggplot(aes(x = f_new, fill = stock, colour = NULL))+
  geom_histogram(alpha = 0.5)+
  scale_fill_manual(values = c("#D55E00", "#009E73", "#0072B2"),
                    labels = c("Fraser Spring 1.2", "Fraser Spring 1.3", "Fraser Summer 1.3"))+
  labs(x = "Fecundity", y = "Density")+
  facet_wrap(~stock, nrow = 3)+
  theme_classic()+
  theme(legend.position = "none")

ggsave(height = 4, width = 3, units = "in", filename = "fec_dat.pdf")
ggsave(height = 4, width = 3, units = "in", filename = "fec_dat.png")

####################alpha results
anic <- alpha_nic$alpha
asu <- alpha_su$alpha
asp <- alpha_sp$alpha

a_new <- c(anic, asu, asp)
stock <- c(rep("Fraser Spring 1.2", length(anic)), rep("Fraser Summer 1.3", length(asu)), rep("Fraser Spring 1.3", length(asp)))
alpha_dat <- data.frame(a_new, stock)

alpha_dat %>% filter(stock != "Fraser Spring 1.2") %>% 
  ggplot(aes(x = a_new, fill = stock, colour = NULL))+
  geom_histogram(alpha = 0.5)+
  scale_fill_manual(values = c("#D55E00", "#009E73", "#0072B2"),
                    labels = c("Fraser Spring 1.2", "Fraser Spring 1.3", "Fraser Summer 1.3"))+
  labs(x = "Productivity (ln(a))", y = "Density")+
  facet_wrap(~stock, nrow = 3)+
  theme_classic()+
  theme(legend.position = "none")

ggsave(height = 4, width = 3, units = "in", filename = "alpha_dat.pdf")
ggsave(height = 4, width = 3, units = "in", filename = "alpha_dat.png")
```








