---
title: "SP_1.3_SIM"
author: "Colin Bailey"
date: "2025-12-11"
output: html_document
---

This code chunk loads the required packages and the data. Note that a specific version of samSim is required (see commented-out code to install the correct version), and that if a different version of samSim is installed on your computer, you may need to manually delete it from your library to get the new version to install correctly.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(viridis)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
#install.packages("remotes")    #run this line and the next once to get access to the sgen solver that DFO has developed
#remotes::install_github("Pacific-salmon-assess/samSim", ref="sbccnk-hatch", force=TRUE)
library(samSim) #package that DFO created to simulate salmon abundances

pkgbuild::has_build_tools(debug = TRUE)
rstan_options(auto_write=T)
options(mc.cores = parallel::detectCores())

#escapement data
esc_dat <- read.csv("SP_SU_1.3\\Data_in\\sp_su_1.3_escape_series.csv")
head(esc_dat)

#posterior data
pos_dat <- summary(readRDS("R\\sp_su_1.3_fit.RDS"))
head(pos_dat)

#age data
age_dat <- read.csv("SP_SU_1.3\\Data_in\\age_dat_SP1.3.csv")
head(age_dat)

```


This code chunk prepares data for use in 'samSim' (the forward simulation tool). The key data inputs in this chunk include:
1) a correlation matrix of the CUs being simulated
2) watershed area-based estimates of SREP for CUs that are converted into beta values (*see "02_Benchmarks.Rmd" for details on conversion of SREP to beta*)
3) a posterior for each sub-population with Ricker model parameters "alpha", "beta", and "sigma" (**detailed explanation of the calculation of these parameters below this list**)
4) mean proportions and variance in age at return

**Description of the posteriors for the sub-populations**
The 'samSim' package can produce forward simulations of salmon abundance using fixed Ricker parameter values or posteriors from Ricker stock-recruit models. Here, we wanted to simulate abundances in the CUs of the Fraser Spring 1.3 Chinook SMU across a realistic fixed range of alpha values (productivity) while still incorporating uncertainty from models' posteriors. The parameters provided in the population-specific posteriors included:
1) alpha - range from 0.36 to 2.13 in even steps representing a wide range of alpha values observed in the estimated log(alpha) posterior (*see "01_SR_parameters.Rmd" for details*). The same alpha posterior was assumed to be representative of all Fraser Spring 1.3 populations.
2) beta - posterior generated from the Parken Habitat Model and the log(alpha) posterior for all CUs.
3) sigma - posterior generated from the Nicola S-R analysis and assumed to be representative of all CUs.

The range of alpha values tested (n = 10) roughly matches the 95% CI of alpha values in the posterior.

Beta values were estimated from posterior predictions of SREP for each CU as described in "02_Benchmarks.Rmd". Because alpha and beta are correlated statistically, and pairings of low values of one parameter with high values of the other parameter can lead to simulation malfunction (samSim errors out and fails to complete the simulation), we paired lower values of alpha with lower quantile slices of beta, and vice versa. Thus, for each CU, the vector of 30000 possible values of beta were sliced into 10 quantiles, and the 1st quantile of beta was matched with the lowest value of alpha tested, etc. 

Sigma values were not matched in any particular fashion to values of alpha or beta as they are not correlated with those parameters. Thus, sigma was drawn at random from the Nicola S-R model posterior.

For each CU and level of alpha tested, a posterior of 1000 rows with alpha, beta and sigma were fed into the simulation.

```{r sim data prep}

###Escapement correlation### - filter for Spring 1.3 pops
`%!in%` <- Negate(`%in%`)

dat <- esc_dat %>% filter(CU_ID %in% c("CK-04", "CK-08", "CK-10", "CK-12", "CK-18")) %>% 
  dplyr::select(Pop_Name = CU_ID, Year, TotalInfilled = SpnForAbd_Wild) %>% 
  filter(Year > 2008)

dat[dat$Pop_Name == "CK-04" & dat$Year == 2024, 3] <- 89 #most up-to-date data

source("R\\pop_cor.R")

pcor <- pop_cor(dat) #population correlation matrix

###Estimate srep from watershed areas for populations without beta estimates###
nu_wa_dat <- read.csv("data\\CN1.3_watershed_areas.csv")
nu_wa = nu_wa_dat %>% dplyr::select(wa = w_area, pop = CU, smu = SMU) %>% filter(smu == "SP_1.3")

#baseline data (paired watershed areas and SREPs) are specific to stream-type chinook for maximum relevance to Fraser Spring 1.3 Chinook (which are stream-type Chinook) -> these data are for running the Parken Habitat Model (2006)
old_wa <- read.csv("data\\srep_habitat_model_data_stream-type_ May 2025.csv") %>% mutate_at(c(2:4), as.numeric)

source("R\\srep_wa_analysis_predict.R")

nu_srep <- srep_est(nu_wa, old_wa)
names(nu_srep) <- c(unique(nu_wa$pop))
nu_srep <- nu_srep[sample(nrow(nu_srep), 30000),] #srep posterior, 30000 samples each per population

###Estimate beta posterior from nu_srep posterior###
post <- readRDS("R//sp_su_1.3_fit.RDS")

srep_post <- nu_srep %>% pivot_longer(names_to = "pop", cols = c(1:5)) %>% arrange(pop) #posterior of srep values for all populations

#creating alpha-sigma-alpha_prime posterior for each CU
`CK-04` <- data.frame(as.vector(extract(post)[12])$alpha_sp, 
                      as.vector(extract(post)[4])$sigma,
                      as.vector(extract(post)[16])$alpha_prime_sp) %>% 
  mutate(CU = "CK-04")
names(`CK-04`) <- c("alpha_sp", "sigma", "alpha_prime_sp", "CU")
`CK-08` <- `CK-04`[sample(nrow(`CK-04`), 30000),] %>% mutate(CU = "CK-08")
`CK-10` <- `CK-04`[sample(nrow(`CK-04`), 30000),] %>% mutate(CU = "CK-10")
`CK-12` <- `CK-04`[sample(nrow(`CK-04`), 30000),] %>% mutate(CU = "CK-12")
`CK-18` <- `CK-04`[sample(nrow(`CK-04`), 30000),] %>% mutate(CU = "CK-18")

w <- rbind(`CK-04`, `CK-08`) %>% rbind(.,`CK-10`) %>% rbind(.,`CK-12`) %>% rbind(.,`CK-18`)

srep_post$alpha_prime_sp <- w$alpha_prime_sp
srep_post$alpha <- ifelse(w$alpha_sp > 0, w$alpha_sp, 0) 
srep_post$sigma <- w$sigma

nu_beta <- srep_post %>% mutate(srep = value, #produces equivalent-to-Nicola-posteriors for all the CUs
                     beta = alpha_prime_sp/srep) %>%
  dplyr::select(alpha, beta, sigma, pop)

sim_post <- nu_beta %>% #creates one large posterior with all CUs represented
  mutate(stk = ifelse(pop == "CK-04", 1,
                      ifelse(pop == "CK-08", 2,
                             ifelse(pop == "CK-10", 3,
                                    ifelse(pop == "CK-12", 4, 5))))) %>% 
  dplyr::select(stk, alpha, beta, sigma)#full posterior to feed to the simulation

sim_post=sim_post[order(sim_post$stk),] #orders the posterior by stk #

#manipulate the posterior into 10 posteriors, each with a fixed value for alpha and varying values of beta based on srep - this preserves the posterior variance while allowing fixed values of alpha to test across the plausible range for the icecream plots (see "04_samsim_processing.Rmd")
#note that alpha values are based on the 2 SE range in alpha_sp
alpha_nu <- seq(from = 0.36, to = 2.13, length.out = 10) #alpha values to test
stk_beta <- list() #empty list to populate with beta values sampled from 10 quantiles
beta_nu <- list() #empty list of lists to combine the outputs of stk_beta
b_ks <- seq(0.1, 1, 0.1)
###Creating a list of dataframes with beta and sigma pairs arranged by beta quantile slice##

for(s in 1:5){
  stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta < quantile(beta, probs = c(b_ks[1]))), 1000)[,3:4] #sample beta and sigma pairs from the posterior for each stock and the first beta quantile
}
beta_nu[[1]] <- bind_rows(stk_beta, .id = "column_label") #bind together for loop outputs

for(i in 2:length(alpha_nu)){ #sample beta and sigma pairs from the posterior for each stock and the middle 11 beta quantiles
  for(s in 1:5){
    stk_beta[[s]] = sample_n(sim_post %>% filter(stk == s) %>% filter(beta >= quantile(beta, probs = c(b_ks[i-1])) &
                                                                      beta < quantile(beta, probs = c(b_ks[i]))), 1000)[,3:4]
  }
  
  
  sim_post[sim_post$beta >= quantile(sim_post$beta, probs = c(b_ks[i-1])) & 
                            sim_post$beta < quantile(sim_post$beta, probs = c(b_ks[i])), 3:4]
  
  beta_nu[[i]] = bind_rows(stk_beta, .id = "column_label")
}

###Creating a list of dataframes with rows of alpha, beta, and sigma arranged by alpha value and beta quantile slice##

sim_post_vars <- list() #create empty list for final posteriors to feed to the simulation

for(i in 1:length(alpha_nu)){
  sim_post_vars[[i]] <- assign(paste("sim_post_a", alpha_nu[i], sep =""), rep(99, 5000))
}

for(i in 1:length(alpha_nu)){ #populating dataframes with stk and alpha, leaving dummy values for beta and sigma
  sim_post_vars[[i]] <- sample_n(sim_post, 5000) %>% mutate(alpha = alpha_nu[i], 
                                                            beta = 99,
                                                            sigma = 99)
  sim_post_vars[[i]]$stk <- c(rep(1,1000), rep(2,1000), rep(3,1000), rep(4,1000), rep(5,1000))
}


for(i in 1:length(sim_post_vars)){ #replacing dummy values of beta and sigma with pairs from beta_nu
  sim_post_vars[[i]][,3:4] = beta_nu[[i]][2:3]
}

###Tau for age variance and mean proportions at age (3,4,5,6)### - note, needed to add a very small number to zeros for the math to work properly (otherwise provides significant overestimate of proportion at age 6)
ppnMat <- age_dat %>% mutate(p3 = ifelse(a3/(a3 + a4 + a5 + a6) > 0, a3/(a3 + a4 + a5 + a6), 0.001),
                   p4 = ifelse(a4/(a3 + a4 + a5 + a6) > 0, a4/(a3 + a4 + a5 + a6), 0.001),
                   p5 = ifelse(a5/(a3 + a4 + a5 + a6) > 0, a5/(a3 + a4 + a5 + a6), 0.001),
                   p6 = ifelse(a6/(a3 + a4 + a5 + a6) > 0, a6/(a3 + a4 + a5 + a6), 0.001)) %>% dplyr::select(p3, p4, p5, p6)

source("R\\age_tau.R")

tau <- tau_comp(ppnMat)$tau #tau 
m_props <- tau_comp(ppnMat)$pa #mean age proportions

```


This last chunk runs the simulation.*Need to confirm base ER rates and CVs on ERs in simPars*
```{r sim input files}
#each pair of CSVs is for a different error scenario - comment out the other 2 when running simulation
# simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp_opti.csv")
# CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp_opti.csv")
# 
# simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp_pess.csv")
# CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp_pess.csv")
# 
simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp-impl.csv")
CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp-impl.csv")

#uncomment to run the simulation
t <- Sys.time()
for(k in 1:10){
  for(u in 1:nrow(simPar)){
    genericRecoverySim(
      simPar = simPar[u,],
      cuPar = CUPar,
      srDat = NULL,
      ricPars = sim_post_vars[[k]],
      nTrials = 500, #number of trials used to produce the plots
      #nTrials = 10, #good number of iterations for testing the simulation
      cuCustomCorrMat = pcor,
      outDir = here::here(paste('outputs', alpha_nu[k], sep = "")))
    }
}
Sys.time() - t

```

