---
title: "Simulation - post processing"
author: "C. Bailey"
date: "5/29/2025"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(cowplot)
library(boot)
library(ggpattern)

#posterior data from CYER ~ FMI relationship
ER_post <- readRDS("data\\fmi_cyer_posterior_predictions.rds") %>% 
   filter(fmi %in% c(0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5))
```


This code chunk retrieves the simulation results from the folders and combines them into a single dataframe.
```{r, read in scenario outputs}

#retrieving the basic simulation parameterization
simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp_opti.csv")
CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp_opti.csv")

#regenerating alpha_nu to extract the simultation results from the output folders
alpha_nu <- seq(0.36, 2.13, length.out = 10)

#creating an empty list to store a dataframe for each value of alpha tested
srdat_aq <- list()

#extracting the dataframes of results
for(k in 1:length(alpha_nu)){
   hcrDatalist<-list()
   srData<- list()
   for(a in seq_len(nrow(simPar))){
      hcrDatalist[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/",
                                         simPar$nameOM[a],"/", 
                                         simPar$scenario[a],"/",
                                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_",
                                               "CU_HCR_PM.RData",sep=""), sep=""))$hcrDatout
      hcrDatalist[[a]]$scenario<-simPar$scenario[a]
      hcrDatalist[[a]]$nameOM<-simPar$nameOM[a]
      hcrDatalist[[a]]$nameMP<-simPar$nameMP[a]
      
      srData[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/", 
                         simPar$nameOM[a],"/",
                         simPar$scenario[a],"/",
                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_", "CUsrDat.RData",sep=""), sep=""))$srDatout
      srData[[a]]$scenario<-simPar$scenario[a]
      srData[[a]]$nameOM<-simPar$nameOM[a]
      srData[[a]]$nameMP<-simPar$nameMP[a]
      }
   hcrdat <- do.call(rbind,hcrDatalist)
   srdat<- do.call(rbind,srData)
   hcrdat<-hcrdat[hcrdat$year>0,] #remove burn-in period
   srdat<-srdat[srdat$year>0,]
   
   #hcrdat maybe not needed - has catch statistics though
   hcrdat=hcrdat[order(hcrdat$scenario,hcrdat$iteration,hcrdat$CU,hcrdat$year),]
   srdat=srdat[order(srdat$scenario,srdat$iteration,srdat$CU,srdat$year),]
   
   srdat_aq[[k]] <- srdat
}

#converting from a list of dataframes to a single comprehensive dataframe
sim_out <- bind_rows(srdat_aq, .id = "column_label")

```

The raw simulation outputs (sim_out) are broken out at the individual CU level. In the code chunk below, sim_out is summarized at the CU- and SMU-level, and then evaluated against:

1) CU-level lower benchmarks (20% Smax or 1500 spawners, whichever number is higher).
2) CU-level quasi-extinction threshold (50 spawners).
3) SMU-level Limit Reference Point, where both CUs need to be above 20% Smax or 1500 spawners (whichever is more for a given CU) for the SMU to be above the LRP.

The success of each trial examines the probability of the geometric mean of the last generation of the simulation (5 years in this case) meeting the conditions laid out above.

```{r sim output summarization}

sim_sum <- sim_out %>% mutate(CU_ID = ifelse(CU == 1, "CK-04",
                                             ifelse(CU == 2, "CK-08",
                                                    ifelse(CU == 3, "CK-10",
                                                           ifelse(CU == 4, "CK-12", "CK-18"))))) %>% 
                                 dplyr::select(iteration, year, CU_ID, CU, scenario, spawners, beta, alpha, sigma) %>% 
   mutate(targetER = as.numeric(substr(scenario, 3, nchar(scenario))))


#read in RDS with lower biological benchmarks (0.2 Smax)
summ_smax0.2 <- readRDS("smax0.2.RDS")

sim_sum_CU <- sim_sum %>%
   filter(year %in% c(41:45)) %>%  #need to update when new sim is run... will be years 41:45 
   group_by(CU_ID, CU, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(spawners)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "CK-04" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-04" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen >= summ_smax0.2[[6,2]], 1,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen < summ_smax0.2[[6,2]], 0,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen >= summ_smax0.2[[8,2]], 1,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen < summ_smax0.2[[8,2]], 0,
                           ifelse(CU_ID == "CK-18" & geo_mean_gen >= summ_smax0.2[[10,2]], 1, 0)))))))))) %>% 
   group_by(CU_ID, CU, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#QET set to 50 fish for similar life-history of Chinook in the Snake River Basin, so used that here
sim_sum_CU_QET <- sim_sum %>%
   filter(year %in% c(41:45)) %>%  #need to update when new sim is run... will be years 41:45 
   group_by(CU_ID, CU, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(spawners)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "CK-04" & geo_mean_gen >= 50, 1,
                           ifelse(CU_ID == "CK-04" & geo_mean_gen < 50, 0,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen >= 50, 1,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen < 50, 0,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen >= 50, 1,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen < 50, 0,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen >= 50, 1,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen < 50, 0,
                           ifelse(CU_ID == "CK-18" & geo_mean_gen >= 50, 1, 0)))))))))) %>% 
   group_by(CU_ID, CU, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#Summarizing at the SMU level to examine likelihood of exceeding CU-status-based LRP
sim_sum_SMU <- sim_sum %>% filter(year %in% c(41:45)) %>%  #need to update when new sim is run... will be years 41:45 
   group_by(CU_ID, CU, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(spawners)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "CK-04" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-04" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen >= summ_smax0.2[[6,2]], 1,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen < summ_smax0.2[[6,2]], 0,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen >= summ_smax0.2[[8,2]], 1,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen < summ_smax0.2[[8,2]], 0,
                           ifelse(CU_ID == "CK-18" & geo_mean_gen >= summ_smax0.2[[10,2]], 1, 0)))))))))) %>% 
   group_by(alpha, targetER, scenario, iteration) %>%
   summarize(smu_fail = ifelse(mean(cu_fail) < 1, 0, 1)) %>% 
   group_by(alpha, targetER, scenario) %>% 
   summarize(p_fail = mean(smu_fail))

```


The following code chunks create icecream plots that illustrate the probability of exceeding the thresholds detailed above (1-3). Note that the secondary y-axes are coded to show the equivalent FMI for a given CYER measure.

This chunk defines a function for converting FMI to CYER which is used to calculate the secondary axes in the icecream plots.
```{r ER transform}

i_o = -1.54
s_o = 0.400
i_p = -1.28
s_p = 0.0843

FMI = seq(0, 1, by = 0.01)

opti <- function(FMI){
   CYER = inv.logit(FMI * s_o + i_o)
   print(CYER)
}

df_opti <- data.frame(FMI, opti(FMI)) %>% 
   dplyr::select(FMI, CYER = opti.FMI.)

anns_opti <- df_opti[FMI %in% seq(0, 0.5, by = 0.05), ]

pess <- function(targetER){
   CYER = inv.logit(FMI * s_p + i_p)
   print(CYER)
}

df_pess <- data.frame(FMI, pess(FMI)) %>% 
   dplyr::select(FMI, CYER = pess.FMI.)

anns_pess <- df_pess[FMI %in% seq(0, 0.5, by = 0.05), ]

```

Illustrating the CYER FMI relationship in the optimistic and pessimistic scenarios
```{r freq dist plot of FMI vs CYER}

#pessimistic scenario
med_pess <- ER_post %>% filter(model == "state space - 0.3 CV") %>% group_by(fmi) %>% summarize(med_cyer = median(cyer))

pess_plot <- ER_post %>% filter(model == "state space - 0.3 CV") %>% ggplot()+
   geom_density(aes(x = cyer, fill = as.factor(fmi)), alpha = 0.3)+
   coord_flip()+
   scale_x_continuous(limits = c(0, 0.45),
                      breaks = seq(0, 0.45, by = 0.05))+
   scale_y_continuous(expand = c(0,0))+
   # scale_fill_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   # scale_colour_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   geom_vline(data = med_pess, aes(xintercept = med_cyer, colour = as.factor(fmi)))+
   labs(x = NULL, y = "Frequency", fill = "FMI", colour = "FMI")+
   theme_classic()+
   theme(legend.position = c(0.9, 0.80),
         legend.key.size = unit(0.5, "lines"))+
   guides(fill = guide_legend(ncol = 1))

#optimistic scenario
med_opti <- ER_post %>% filter(model == "state space - 0.1 CV") %>% group_by(fmi) %>% summarize(med_cyer = median(cyer))

opti_plot <- ER_post %>% filter(model == "state space - 0.1 CV") %>% ggplot()+
   geom_density(aes(x = cyer, fill = as.factor(fmi)), alpha = 0.3)+
   coord_flip()+
   scale_x_continuous(limits = c(0, 0.45),
                      breaks = seq(0, 0.45, by = 0.05))+
   scale_y_continuous(expand = c(0,0))+
   # scale_fill_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   # scale_colour_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   geom_vline(data = med_opti, aes(xintercept = med_cyer, colour = as.factor(fmi)))+
   labs(x = NULL, y = "Frequency", fill = "FMI", colour = "FMI")+
   theme_classic()+
   theme(legend.position = c(0.9, 0.80),
         legend.key.size = unit(0.5, "lines"))+
   guides(fill = guide_legend(ncol = 1))




```



```{r sim results vis CU sum}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

#p(CU above LBM)
CU_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- sim_sum_CU %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.45, by = 0.05))+
   labs(y = "CAN CYER", 
        x = "Productivity [ln(α)]") + 
   theme_classic()
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(CU_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- CU_plot[[i]]+
   theme(legend.position='none',
         axis.text.y = if(i %in% c(2,4)){
            element_blank()
         } else{
            element_text(colour = "black")},
         axis.title.y = if(i %in% c(2,4)){
            element_blank()
         } else{
            element_text(colour = "black")},
         plot.margin = if(i %in% c(2,4)){
            margin(r = 0)
         } else{
            margin()})
}

CU <- ggdraw(plot_grid(CU_plot[[1]], CU_plot[[2]], opti_plot + theme(axis.text.y = element_blank(),
                                                                     axis.title.y = element_blank()),
                       CU_plot[[3]], CU_plot[[4]], opti_plot + theme(axis.text.y = element_blank(),
                                                                     axis.title.y = element_blank()),
                       CU_plot[[5]], opti_plot + theme(axis.text.y = element_blank(),
                                                                     axis.title.y = element_blank()), legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 3, nrow = 3, axis = c("l"), align = c("hv"),
                       labels = c("CK-04", "CK-08", "", "CK-10", "CK-12", "", "CK-18", ""),
                       label_size = 12,
                       label_x = 0.55, label_y = 0.9))

CU_plot <- cowplot::plot_grid(CU)

ggsave(CU_plot, height = 6.5, width = 6.5, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU.pdf")

```


```{r sim results vis CU QET}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

#p(CU above LBM)
QET_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   QET_plot[[i]] <- sim_sum_CU_QET %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> Quasi-Extinction Threshold)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(expand = c(0,0))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.45, by = 0.05))+
   labs(y = "CAN CYER", 
        x = "Productivity [ln(α)]") + 
   theme_classic()#+
   
   ###code for adding lines to the plots at ERs X log(a)s of interest (or placing an FRP-L)
   # geom_segment(aes(x = 0.26, y = 0.30, xend = 1.09, yend = 0.30),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)+
   #    geom_segment(aes(x = 0.26, y = 0.05, xend = 0.725, yend = 0.05),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)+
   # geom_segment(aes(x = 0.725, y = 0.05, xend = 0.725, yend = -0.025),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)+
   # geom_segment(aes(x = 1.09, y = 0.30, xend = 1.09, yend = -0.025),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)
   # annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   # annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   # annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(QET_plot[[1]])

QET_plot[[1]] <- QET_plot[[1]] + 
   theme(legend.position='none')
QET_plot[[2]] <- QET_plot[[2]] + 
   theme(legend.position='none')
QET_plot[[3]] <- QET_plot[[3]]  + 
   theme(legend.position='none')
QET_plot[[4]] <- QET_plot[[4]] + 
   theme(legend.position='none')
QET_plot[[5]] <- QET_plot[[5]] + 
   theme(legend.position='none')


QET <- ggdraw(plot_grid(QET_plot[[1]], QET_plot[[2]], QET_plot[[3]], QET_plot[[4]], QET_plot[[5]], legend1,
                       rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 2, nrow = 3, axis = c("l"), align = c("hv"),
                       labels = c("CK-04", "CK-08", "CK-10", "CK-12", "CK-18"),
                       label_size = 12,
                       label_x = 0.55, label_y = 0.9))

QET_plot <- cowplot::plot_grid(QET)

ggsave(QET_plot, height = 7.5, width = 6, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU_QET.pdf")

```


```{r sim results vis SMU sum}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

#p(SMU > LRP)
SMU_plot <- sim_sum_SMU  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Stock Management Unit\n> Limit Reference Point)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(expand = c(0,0))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.45, by = 0.05))+
   labs(y = "CAN CYER", 
        x = "Productivity [ln(α)]") + 
   theme_classic()#+

   ###code for adding lines to the plots at ERs X log(a)s of interest (or placing an FRP-L)
   # geom_segment(aes(x = 0.26, y = 0.30, xend = 1.09, yend = 0.30),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)+
   #    geom_segment(aes(x = 0.26, y = 0.05, xend = 0.725, yend = 0.05),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)+
   # geom_segment(aes(x = 0.725, y = 0.05, xend = 0.725, yend = -0.025),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)+
   # geom_segment(aes(x = 1.09, y = 0.30, xend = 1.09, yend = -0.025),
   #              colour = "blue", linewidth = 0.5, alpha = 0.1)
   # annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   # annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   # annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

ggsave(SMU_plot, height = 2.5, width = 4.75, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_SMU.pdf")

```


```{r freq dist plot of FMI vs CYER}

#pessimistic scenario
med_pess <- ER_post %>% filter(model == "state space - 0.3 CV") %>% group_by(fmi) %>% summarize(med_cyer = median(cyer))

ER_post %>% filter(model == "state space - 0.3 CV") %>% ggplot()+
   geom_density(aes(x = cyer, fill = as.factor(fmi)), alpha = 0.3)+
   coord_flip()+
   scale_x_continuous(limits = c(0, 0.5),
                      expand = c(0,0),
                      breaks = seq(0, 0.45, by = 0.05))+
   scale_y_continuous(expand = c(0,0))+
   scale_fill_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   scale_colour_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   geom_vline(data = med_pess, aes(xintercept = med_cyer, colour = as.factor(fmi)))+
   theme_classic()

#optimistic scenario
med_opti <- ER_post %>% filter(model == "state space - 0.1 CV") %>% group_by(fmi) %>% summarize(med_cyer = median(cyer))

ER_post %>% filter(model == "state space - 0.1 CV") %>% ggplot()+
   geom_density(aes(x = cyer, fill = as.factor(fmi)), alpha = 0.3)+
   coord_flip()+
   scale_x_continuous(limits = c(0, 0.5),
                      expand = c(0,0),
                      breaks = seq(0, 0.45, by = 0.05))+
   scale_y_continuous(expand = c(0,0))+
   scale_fill_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   scale_colour_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   geom_vline(data = med_opti, aes(xintercept = med_cyer, colour = as.factor(fmi)))+
   theme_classic()




```


