---
title: "Simulation - post processing"
author: "C. Bailey"
date: "5/29/2025"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(cowplot)
library(boot)
library(ggpattern)

nic_dat <- read.csv("SP_1.2//Data_in//nic_dat.csv")
fit <- readRDS("SP_1.2//Results/fit.rds")
```


This code chunk retrieves the simulation results from the folders and combines them into a single dataframe.
```{r, read in scenario outputs}

#retrieving the basic simulation parameterization
simPar <- read.csv("data\\samsim pars\\SimPars.csv")
CUPar <- read.csv("data\\samsim pars\\CUPars.csv")

#regenerating alpha_nu to extract the simultation results from the output folders
fit <- readRDS("SP_1.2//Results/fit.rds")
alpha_nu <- seq(from = 0.2, to = 1.35, by = 0.085)

#creating an empty list to store a dataframe for each value of alpha tested
srdat_aq <- list()

#extracting the dataframes of results
for(k in 1:length(alpha_nu)){
   hcrDatalist<-list()
   srData<- list()
   for(a in seq_len(nrow(simPar))){
      hcrDatalist[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/",
                                         simPar$nameOM[a],"/", 
                                         simPar$scenario[a],"/",
                                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_",
                                               "CU_HCR_PM.RData",sep=""), sep=""))$hcrDatout
      hcrDatalist[[a]]$scenario<-simPar$scenario[a]
      hcrDatalist[[a]]$nameOM<-simPar$nameOM[a]
      hcrDatalist[[a]]$nameMP<-simPar$nameMP[a]
      
      srData[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/", 
                         simPar$nameOM[a],"/",
                         simPar$scenario[a],"/",
                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_", "CUsrDat.RData",sep=""), sep=""))$srDatout
      srData[[a]]$scenario<-simPar$scenario[a]
      srData[[a]]$nameOM<-simPar$nameOM[a]
      srData[[a]]$nameMP<-simPar$nameMP[a]
      }
   hcrdat <- do.call(rbind,hcrDatalist)
   srdat<- do.call(rbind,srData)
   hcrdat<-hcrdat[hcrdat$year>26,] #remove burn-in period
   srdat<-srdat[srdat$year>26,]
   
   #hcrdat maybe not needed - has catch statistics though
   hcrdat=hcrdat[order(hcrdat$scenario,hcrdat$iteration,hcrdat$CU,hcrdat$year),]
   srdat=srdat[order(srdat$scenario,srdat$iteration,srdat$CU,srdat$year),]
   
   srdat_aq[[k]] <- srdat
}

#converting from a list of dataframes to a single comprehensive dataframe
sim_out <- bind_rows(srdat_aq, .id = "column_label")

```

The raw simulation outputs (sim_out) are broken out at the individual population level. In the code chunk below, sim_out is summarized at the CU- and SMU-level, and then evaluated against:

1) CU-level lower benchmarks (20% Smax or 1500 spawners, whichever number is higher).
2) CU-level quasi-extinction threshold (50 spawners).
3) SMU-level Limit Reference Point, where both CUs need to be above Sgen or 1500 spawners (whichever is more for a given CU) for the SMU to be above the LRP.

The success of each trial examines the probability of the geometric mean of the last generation of the simulation (4 years in this case) meeting the conditions laid out above.

Lower Thompson 20% smax = 2662

Bessette 20% Smax... small population with poor contrast in S-R data, so default to 1500 as the lower benchmark
***77 fish is the calculated 20% smax***

```{r sim output summarization}
#***need to use a QET at the CU level for the first plot - set to 50 spawners for now


sim_sum <- sim_out %>% mutate(CU_ID = ifelse(CU %in% c(1:4), "lth", "bst"),
                              wildSpawners = ifelse(wildSpawners < 0, 0, wildSpawners),
                              hatcherySpawners = ifelse(hatcherySpawners < 0, 0, hatcherySpawners),
                              return = ifelse(CU == 1, wildSpawners, spawners))


sim_sum_CU <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(spawners)) %>% 
   filter(year %in% c(35:38)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 1500, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 2662, 1, 0)))) %>% 
   group_by(CU_ID, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#QET set to 50 fish for same life-history of Chinook in the Snake River Basin, so used that here
sim_sum_CU_QET <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(35:38)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 50, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 50, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 50, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(CU_ID, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#Summarizing at the SMU level to examine likelihood of exceeding CU-status-based LRP
sim_sum_SMU <- sim_sum %>% group_by(CU_ID, alpha, targetER, scenario, iteration, year) %>% 
   summarize(cu_return = sum(return)) %>% 
   filter(year %in% c(35:38)) %>% 
   group_by(CU_ID, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(cu_return)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "bst" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "bst" & geo_mean_gen < 1500, 0,
                                  ifelse(CU_ID == "lth" & geo_mean_gen >= 2662, 1, 0)))) %>% #need to change 2996 to 20% Smax
   group_by(alpha, targetER, scenario, iteration) %>%
   summarize(smu_fail = ifelse(mean(cu_fail) < 1, 0, 1)) %>% 
   group_by(alpha, targetER, scenario) %>% 
   summarize(p_fail = mean(smu_fail))

```


The following code chunks create icecream plots that illustrate the probability of exceeding the thresholds detailed above (1-3). Note that the upper x-axes on the plots are shown as z-scored logit-transformed smolt-to-age_3 survival index. The plots shown in the FSRR have had the z-scores replaced with the equivalent "real-space" survival index percentages (see last code chunk for translation of z-scored survival to "real-space" survival).
```{r sim results vis CU sum}

Ccols <- c("Very Low (0.00-0.04)" = "mediumpurple4",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

#p(CU above LBM)
p1 <- sim_sum_CU %>% filter(CU_ID == "bst")  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2)),
                      name = "Productivity [ln(α)]", expand = c(0,0),
                      breaks = c(0.2, 0.4, 0.6, 0.8, 1, 1.2),
                      limits = c(0.1575, 1.35))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.3, by = 0.05))+
   # theme(legend.text = element_text(size = 10),
   #      legend.title = element_text(size = 13)) +
   # guides(fill = guide_legend(ncol = 1), title.position = "top") +
   labs(y = "Canadian exploitation rate", 
        x = "Productivity [ln(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.1575, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

#p(CU above LBM)
p1.5 <- sim_sum_CU %>% filter(CU_ID == "lth") %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2)),
                      name = "Productivity [ln(α)]", expand = c(0,0),
                      breaks = c(0.2, 0.4, 0.6, 0.8, 1, 1.2),
                      limits = c(0.1575, 1.35))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.3, by = 0.05))+
   # theme(legend.text = element_text(size = 10),
   #      legend.title = element_text(size = 13)) +
   # guides(fill = guide_legend(ncol = 1), title.position = "top") +
   labs(y = "Canadian exploitation rate", 
        x = "Productivity [ln(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.1575, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)


#frequency of survival rates
surv <- as.data.frame(logit(nic_dat$smolt_age3_survival) - mean(logit(nic_dat$smolt_age3_survival))) /
   sd(logit(nic_dat$smolt_age3_survival))

names(surv)[1] <- "std_surv"
surv$type <- ""

s_plot <- surv %>% ggplot(aes(x = std_surv))+
   geom_histogram(aes(x = std_surv), fill = "gray30", colour = "grey30")+
   scale_x_continuous(limits = c(-1.472903, 1.584789),
                      breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2),
                      expand = c(0,0))+
   labs(x = "Observed smolt survival index (%)", y = "Occurrences (n)")+
   theme_classic()

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(p1)
p1 <- p1 + theme(legend.position='none')
p1.5 <- p1.5 + theme(legend.position='none')
s_plot <- s_plot + theme(legend.position='none')

CU <- ggdraw(plot_grid(p1, p1.5, s_plot, ncol = 1, axis = c("l"), align = "v", rel_heights = c(1, 1, 0.3), 
                       labels = c("A", "B", "C"),
                       label_size = 12,
                       label_x = 0.9, label_y = 0.87))
CU_plot <- cowplot::plot_grid(CU,legend1,rel_widths = c(1, 0.6, 0.25))

ggsave(CU_plot, height = 7.5, width = 5.3, units = "in", filename = "sim_sum_CU.pdf")




```


```{r sim results vis CU QET}

Ccols <- c("Very Low (0.00-0.04)" = "mediumpurple4",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

#p(CU above QET)
p2 <- sim_sum_CU_QET %>% filter(CU_ID == "bst")  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit >\nQuasi-Extinction Threshold)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2)),
                      name = "Productivity [ln(α)]", expand = c(0,0),
                      breaks = c(0.2, 0.4, 0.6, 0.8, 1, 1.2),
                      limits = c(0.1575, 1.35))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.3, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
   guides(fill = guide_legend(ncol = 1), title.position = "top") +
   labs(y = "Canadian exploitation rate", 
        x = "Productivity [ln(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.1575, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

p2.5 <- sim_sum_CU_QET %>% filter(CU_ID == "lth") %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit >\nQuasi-Extinction Threshold)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2)),
                      name = "Productivity [ln(α)]", expand = c(0,0),
                      breaks = c(0.2, 0.4, 0.6, 0.8, 1, 1.2),
                      limits = c(0.1575, 1.35))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.3, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
   guides(fill = guide_legend(ncol = 1), title.position = "top") +
   labs(y = "Canadian exploitation rate", 
        x = "Productivity [ln(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.1575, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)


#frequency of survival rates
surv <- as.data.frame(logit(nic_dat$smolt_age3_survival) - mean(logit(nic_dat$smolt_age3_survival))) /
   sd(logit(nic_dat$smolt_age3_survival))

names(surv)[1] <- "std_surv"
surv$type <- ""

s_plot <- surv %>% ggplot(aes(x = std_surv))+
   geom_histogram(aes(x = std_surv), fill = "gray30", colour = "grey30")+
   scale_x_continuous(limits = c(-1.472903, 1.584789),
                      breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2),
                      expand = c(0,0))+
   labs(x = "Observed smolt survival index (%)", y = "Occurrences (n)")+
   theme_classic()

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend2 = get_legend(p2)
p2 <- p2 + theme(legend.position='none')
p2.5 <- p2.5 + theme(legend.position='none')
s_plot <- s_plot + theme(legend.position='none')

CU_QET <- ggdraw(plot_grid(p2, p2.5, s_plot, ncol = 1, axis = c("l"), align = "v", rel_heights = c(1, 1, 0.3), 
                       labels = c("A", "B", "C"),
                       label_size = 12,
                       label_x = 0.9, label_y = 0.87))
QET_plot <- cowplot::plot_grid(CU_QET,legend2,rel_widths = c(1, 0.6, 0.25))

ggsave(QET_plot, height = 7.5, width = 5.3, units = "in", filename = "sim_sum_CU_QET.pdf")

```


```{r sim results vis SMU sum}

Ccols <- c("Very Low (0.00-0.04)" = "mediumpurple4",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

#p(SMU above LBM)
p3 <- sim_sum_SMU %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols, 
                     name = "P(Stock Management Unit\n> Limit Reference Point)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(sec.axis = sec_axis(~ (. - quantile(unlist(as.vector(extract(fit)[2])), probs = c(0.5))) / 0.39, 
                                          name = "Smolt survival index (%)",
                                          breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2)),
                      name = "Productivity [ln(α)]", expand = c(0,0),
                      breaks = c(0.2, 0.4, 0.6, 0.8, 1, 1.2),
                      limits = c(0.1575, 1.35))+
   scale_y_continuous(expand = c(0,0),
                      breaks = seq(0, 0.3, by = 0.05))+
   theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
   guides(fill = guide_legend(ncol = 1), title.position = "top") +
   labs(y = "Canadian exploitation rate", 
        x = "Productivity [log(alpha)]") + 
   theme_classic()+
    geom_segment(aes(x = 0.1575, y = 0.05, xend = 0.78, yend = 0.05),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.167, xend = 0.78, yend = 0.167),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.1575, y = 0.119, xend = 0.78, yend = 0.119),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
    geom_segment(aes(x = 0.78, y = 0.167, xend = 0.78, yend = 0),
                colour = "blue", linewidth = 0.5, alpha = 0.1)+
   annotate("text", x = 0.78 + 0.03, y = 0.05, label = "Low", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.167, label = "Limit", hjust = 0, size = 4)+
   annotate("text", x = 0.78 + 0.03, y = 0.119, label = "3-yr mean", hjust = 0, size = 4)

#frequency of survival rates
surv <- as.data.frame(logit(nic_dat$smolt_age3_survival) - mean(logit(nic_dat$smolt_age3_survival))) /
   sd(logit(nic_dat$smolt_age3_survival))

names(surv)[1] <- "std_surv"
surv$type <- ""

s_plot <- surv %>% ggplot(aes(x = std_surv))+
   geom_histogram(aes(x = std_surv), fill = "gray30", colour = "grey30")+
   scale_x_continuous(limits = c(-1.472903, 1.584789),
                      breaks = c(-1.2, -0.8, -0.4, 0, 0.4, 0.8, 1.2),
                      expand = c(0,0))+
   labs(x = "Observed smolt survival index (%)", y = "Occurrences (n)")+
   theme_classic()

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend3 = get_legend(p3)
p3 <- p3 + theme(legend.position='none')
s_plot <- s_plot + theme(legend.position='none')

SMU_plot <- ggdraw(plot_grid(p3, s_plot, ncol = 1, axis = c("l"), align = "v", rel_heights = c(1, 0.3), 
                       labels = c("A", "B"),
                       label_size = 12,
                       label_x = 0.9, label_y = 0.87))
plot_SMU <- cowplot::plot_grid(SMU_plot,legend3,rel_widths = c(1, 0.6, 0.25))

ggsave(plot_SMU, height = 4.5, width = 5.3, units = "in", filename = "sim_sum_SMU.pdf")
```


Code chunk for going back and forth between real space and transformed space for smolt-to-age_3 recruit survival.
```{r survival transform}

#logit-transformed and standardized range of smolt survival
ss <- c(-1.2, -0.8, -0.4, 0.0, 0.4, 0.8, 1.2)

ss <- c(-2.1935084, -1.7301351, -1.2708537, -0.7700096,  0.9455846,  1.0967433,  1.1587859,  1.3693443)

#translating back to "real space"
inv.logit(ss * sd(logit(nic_dat$smolt_age3_survival)) + mean(logit(nic_dat$smolt_age3_survival)))

```

