---
title: "Simulation - post processing"
author: "C. Bailey"
date: "5/29/2025"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(cowplot)
library(boot)
library(ggpattern)
library(lamW)

#posterior data from CYER ~ FMI relationship
ER_post <- readRDS("data\\fmi_cyer_posterior_predictions.rds") %>% ##################NEED TO PUSH AND PULL TO GET NEW POSTERIORS
   filter(fmi %in% c(0, 0.1, 0.2, 0.3, 0.4))

#read in posterior estimate for Ricker alpha for Spring 1.3
fit <- readRDS("R//sp_su_1.3_fit.RDS")
alpha_sp <- as.vector(extract(fit)[12])$alpha

set.seed(1352)
```


This code chunk retrieves the simulation results from the folders and combines them into a single dataframe.
```{r, read in scenario outputs}

#retrieving the basic simulation parameterization
#each pair of CSVs is for a different error scenario - comment out the other 2 when running simulation
# simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp_opti.csv")
# CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp_opti.csv")
# 
simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp_pess.csv")
CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp_pess.csv")
# 
# simPar <- read.csv("SP_SU_1.3\\samsim pars\\SimPars_sp-impl.csv")
# CUPar <- read.csv("SP_SU_1.3\\samsim pars\\CUPars_sp-impl.csv")

#regenerating alpha_nu to extract the simultation results from the output folders
alpha_nu <- seq(0.35, 2.10, length.out = 10)

#creating an empty list to store a dataframe for each value of alpha tested
srdat_aq <- list()

#extracting the dataframes of results
for(k in 1:length(alpha_nu)){
   hcrDatalist<-list()
   srData<- list()
   for(a in seq_len(nrow(simPar))){
      hcrDatalist[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/",
                                         simPar$nameOM[a],"/", 
                                         simPar$scenario[a],"/",
                                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_",
                                               "CU_HCR_PM.RData",sep=""), sep=""))$hcrDatout
      hcrDatalist[[a]]$scenario<-simPar$scenario[a]
      hcrDatalist[[a]]$nameOM<-simPar$nameOM[a]
      hcrDatalist[[a]]$nameMP<-simPar$nameMP[a]
      
      srData[[a]] <- readRDS(paste("./outputs",alpha_nu[k],"/SamSimOutputs/simData/", 
                         simPar$nameOM[a],"/",
                         simPar$scenario[a],"/",
                         paste(simPar$nameOM[a],"_", simPar$nameMP[a], "_", "CUsrDat.RData",sep=""), sep=""))$srDatout
      srData[[a]]$scenario<-simPar$scenario[a]
      srData[[a]]$nameOM<-simPar$nameOM[a]
      srData[[a]]$nameMP<-simPar$nameMP[a]
      }
   hcrdat <- do.call(rbind,hcrDatalist)
   srdat<- do.call(rbind,srData)
   hcrdat<-hcrdat[hcrdat$year>0,] #remove burn-in period
   srdat<-srdat[srdat$year>0,]
   
   #hcrdat maybe not needed - has catch statistics though
   hcrdat=hcrdat[order(hcrdat$scenario,hcrdat$iteration,hcrdat$CU,hcrdat$year),]
   srdat=srdat[order(srdat$scenario,srdat$iteration,srdat$CU,srdat$year),]
   
   srdat_aq[[k]] <- srdat
}

#converting from a list of dataframes to a single comprehensive dataframe
sim_out <- bind_rows(srdat_aq, .id = "column_label")

```

The raw simulation outputs (sim_out) are broken out at the individual CU level. In the code chunk below, sim_out is summarized at the CU- and SMU-level, and then evaluated against:

1) CU-level lower benchmarks (20% Smax or 1500 spawners, whichever number is higher).
2) CU-level quasi-extinction threshold (50 spawners).
3) SMU-level Limit Reference Point, where both CUs need to be above 20% Smax or 1500 spawners (whichever is more for a given CU) for the SMU to be above the LRP.

The success of each trial examines the probability of the geometric mean of the last generation of the simulation (5 years in this case) meeting the conditions laid out above.

```{r sim output summarization}

sim_sum <- sim_out %>% mutate(CU_ID = ifelse(CU == 1, "CK-04",
                                             ifelse(CU == 2, "CK-08",
                                                    ifelse(CU == 3, "CK-10",
                                                           ifelse(CU == 4, "CK-12", "CK-18"))))) %>% 
                                 dplyr::select(iteration, year, CU_ID, CU, scenario, spawners, beta, alpha, sigma) %>% 
   mutate(targetER = as.numeric(substr(scenario, 3, nchar(scenario))))


sim_sum_ER <- sim_out %>% mutate(CU_ID = ifelse(CU == 1, "CK-04",
                                             ifelse(CU == 2, "CK-08",
                                                    ifelse(CU == 3, "CK-10",
                                                           ifelse(CU == 4, "CK-12", "CK-18"))))) %>% 
                                 dplyr::select(iteration, year, CU, scenario, ER) %>% 
   mutate(targetER = as.numeric(substr(scenario, 3, nchar(scenario))))


#read in RDS with lower biological benchmarks (0.2 Smax)
summ_smax0.2 <- readRDS("smax0.2.RDS")

#threshold set to 1500 or 20% Smax, whichever value is higher (consistent with Rapid Status Approach)
sim_sum_CU <- sim_sum %>%
   filter(year %in% c(91:95)) %>%  
   group_by(CU_ID, CU, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(spawners)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "CK-04" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-04" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen >= summ_smax0.2[[6,2]], 1,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen < summ_smax0.2[[6,2]], 0,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen >= summ_smax0.2[[8,2]], 1,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen < summ_smax0.2[[8,2]], 0,
                           ifelse(CU_ID == "CK-18" & geo_mean_gen >= 1500, 1, 0)))))))))) %>% 
   group_by(CU_ID, CU, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#LBB set to 20% Smax for all CUs - contrasts with above by showing outcomes relative to watershed area-based capacity
sim_sum_CU_LBB <- sim_sum %>%
   filter(year %in% c(91:95)) %>%  
   group_by(CU_ID, CU, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(spawners)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "CK-04" & geo_mean_gen >= summ_smax0.2[[1,2]], 1,
                           ifelse(CU_ID == "CK-04" & geo_mean_gen < summ_smax0.2[[1,2]], 0,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen >= summ_smax0.2[[4,2]], 1,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen < summ_smax0.2[[4,2]], 0,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen >= summ_smax0.2[[6,2]], 1,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen < summ_smax0.2[[6,2]], 0,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen >= summ_smax0.2[[8,2]], 1,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen < summ_smax0.2[[8,2]], 0,
                           ifelse(CU_ID == "CK-18" & geo_mean_gen >= summ_smax0.2[[10,2]], 1, 0)))))))))) %>% 
   group_by(CU_ID, CU, alpha, targetER, scenario) %>%
   summarize(p_fail = mean(cu_fail))

#Summarizing at the SMU level to examine likelihood of exceeding CU-status-based LRP
sim_sum_SMU <- sim_sum %>% filter(year %in% c(91:95)) %>% 
   group_by(CU_ID, CU, alpha, targetER, scenario, iteration) %>%
   summarize(geo_mean_gen = exp(mean(log(spawners)))) %>% 
   mutate(cu_fail = ifelse(CU_ID == "CK-04" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-04" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen >= 1500, 1,
                           ifelse(CU_ID == "CK-08" & geo_mean_gen < 1500, 0,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen >= summ_smax0.2[[6,2]], 1,
                           ifelse(CU_ID == "CK-10" & geo_mean_gen < summ_smax0.2[[6,2]], 0,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen >= summ_smax0.2[[8,2]], 1,
                           ifelse(CU_ID == "CK-12" & geo_mean_gen < summ_smax0.2[[8,2]], 0,
                           ifelse(CU_ID == "CK-18" & geo_mean_gen >= summ_smax0.2[[10,2]], 1, 0)))))))))) %>% 
   group_by(alpha, targetER, scenario, iteration) %>%
   summarize(smu_fail = ifelse(mean(cu_fail) < 1, 0, 1)) %>% 
   group_by(alpha, targetER, scenario) %>% 
   summarize(p_fail = mean(smu_fail))

```


The following code chunks create icecream plots that illustrate the probability of exceeding the thresholds detailed above (1-3). Note that the secondary y-axes are coded to show the equivalent FMI for a given CYER measure.

This chunk defines a function for converting FMI to CYER which is used to calculate the secondary axes in the icecream plots.
```{r ER transform}

i_o = -1.54
s_o = 0.400
i_p = -1.28
s_p = 0.0843

FMI = seq(0, 1, by = 0.1)

opti <- function(FMI){
   CYER = inv.logit(FMI * s_o + i_o)
   print(CYER)
}

df_opti <- data.frame(FMI, opti(FMI)) %>% 
   dplyr::select(FMI, CYER = opti.FMI.)

anns_opti <- df_opti[FMI %in% seq(0, 0.4, by = 0.1), ]

pess <- function(targetER){
   CYER = inv.logit(FMI * s_p + i_p)
   print(CYER)
}

df_pess <- data.frame(FMI, pess(FMI)) %>% 
   dplyr::select(FMI, CYER = pess.FMI.)

anns_pess <- df_pess[FMI %in% seq(0, 0.4, by = 0.1), ]

```

Illustrating the CYER FMI relationship in the optimistic and pessimistic scenarios
```{r freq dist plot of FMI vs CYER}

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#pessimistic scenario
med_pess <- ER_post %>% filter(model == "state space - 0.3 CV") %>% group_by(fmi) %>% summarize(med_cyer = median(cyer)) %>% 
   mutate(fmi = fct_reorder(as.factor(fmi), fmi, .fun = median, .desc = T))

pess_plot <- ER_post %>% filter(model == "state space - 0.3 CV") %>%
   mutate(fmi = fct_reorder(as.factor(fmi), fmi, .fun = median, .desc = T)) %>% 
   ggplot()+
   geom_density(aes(x = cyer, fill = fmi), alpha = 0.3)+
   coord_flip()+
   scale_x_continuous(limits = c(0, 0.45),
                      breaks = all_breaks,
                      labels = my_labels)+
   scale_y_continuous(expand = c(0,0),
                      sec.axis = sec_axis(~ ., name = expression(paste(italic("U")[MSY]))))+
   # scale_fill_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   # scale_colour_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   geom_vline(data = med_pess, aes(xintercept = med_cyer, colour = fmi))+
   labs(x = "CAN CYER", y = "Frequency", fill = "FMI", colour = "FMI")+
   theme_classic()+
   theme(legend.position = c(1,1),
         legend.justification = c(1,1),
         legend.key.size = unit(0.5, "lines"))+
   guides(fill = guide_legend(ncol = 1))

#optimistic scenario
med_opti <- ER_post %>% filter(model == "state space - 0.1 CV") %>% group_by(fmi) %>% summarize(med_cyer = median(cyer)) %>% 
   mutate(fmi = fct_reorder(as.factor(fmi), fmi, .fun = median, .desc = T))

opti_plot <- ER_post %>% filter(model == "state space - 0.1 CV") %>% 
   mutate(fmi = fct_reorder(as.factor(fmi), fmi, .fun = median, .desc = T)) %>% 
   ggplot()+
   geom_density(aes(x = cyer, fill = fmi), alpha = 0.3)+
   coord_flip()+
   scale_x_continuous(limits = c(0, 0.45),
                      breaks = all_breaks,
                      labels = my_labels)+
   scale_y_continuous(expand = c(0,0),
                      sec.axis = sec_axis(~ ., name = expression(paste(italic("U")[MSY]))))+
   # scale_fill_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   # scale_colour_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
   geom_vline(data = med_opti, aes(xintercept = med_cyer, colour = fmi))+
   labs(x = "CAN CYER", y = "Frequency", fill = "FMI", colour = "FMI")+
   theme_classic()+
   theme(legend.position = c(1,1),
         legend.justification = c(1,1),
         legend.key.size = unit(0.5, "lines"))+
   guides(fill = guide_legend(ncol = 1))




```

Plotting realized ER by iteration and target ER
```{r plot ER}

ER <- unique(sim_sum_ER$targetER)
targetER <- as.factor(unique(sim_sum_ER$targetER))
df_ER <- data.frame(ER, targetER)

#note that ER needs to be filtered for values > 0 because extinction events cause ER to drop to zero
sim_sum_ER %>% filter(iteration %in% seq(1, 500, by = 5) & CU == 4 & year > 60 & ER > 0) %>% ggplot(aes(x = year, y = ER))+
   geom_line(aes(x = year, y = ER, group = as.factor(iteration)), alpha = 0.1, linewidth = 0.2)+
   geom_hline(data = df_ER, aes(yintercept = ER+0.04), colour = "red", linewidth = 0.1)+ #note the added 0.04 accounts for American ER in the simulation that is additional to the target canadian ER
   facet_wrap(.~ as.factor(targetER))+
   labs(x = "Year", y = "ER")+
   theme_classic()

# ggsave(height = 5, width = 5, units = "in", filename = "ER_opti_sp.pdf")
# ggsave(height = 5, width = 5, units = "in", filename = "ER_pess_sp.pdf")
# ggsave(height = 5, width = 5, units = "in", filename = "ER-impl_sp.pdf")

```

Optimistic CU Results
```{r sim results vis CU sum OPTI}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(CU above LBM)
CU_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- sim_sum_CU %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]"))) + 
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(CU_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- CU_plot[[i]]+
   if(i == 1 | i == 4){
     theme(legend.position='none',
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   } else {
     theme(legend.position='none',
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   }
}

opti_plotA <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))

opti_plotB <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


CU <- ggdraw(plot_grid(opti_plotA, CU_plot[[1]], 
                                   CU_plot[[2]], CU_plot[[3]], 
                       opti_plotB, CU_plot[[4]], CU_plot[[5]], legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 4, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("", "Lower\nFraser", "Fraser\nCanyon", "Middle\nFraser","","Upper\nFraser", "North\nThompson", ""),
                       label_size = 8,
                       label_x = 0.95, label_y = 0.85, hjust = 1))

CU_plot <- cowplot::plot_grid(CU)

ggsave(CU_plot, height = 5, width = 9, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU.pdf")

```

Optimistic CU LBB Results
```{r sim results vis CU LBB OPTI}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(CU above LBM)
LBB_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   LBB_plot[[i]] <- sim_sum_CU_LBB %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]"))) + 
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(LBB_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   LBB_plot[[i]] <- LBB_plot[[i]]+
   if(i == 1 | i == 4){
     theme(legend.position='none',
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   } else {
     theme(legend.position='none',
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   }
}

opti_plotA <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))

opti_plotB <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


LBB <- ggdraw(plot_grid(opti_plotA, LBB_plot[[1]], 
                                   LBB_plot[[2]], LBB_plot[[3]], 
                       opti_plotB, LBB_plot[[4]], LBB_plot[[5]], legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 4, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("", "Lower\nFraser", "Fraser\nCanyon", "Middle\nFraser","","Upper\nFraser", "North\nThompson", ""),
                       label_size = 8,
                       label_x = 0.95, label_y = 0.85, hjust = 1))

LBB_plot <- cowplot::plot_grid(LBB)

ggsave(LBB_plot, height = 5, width = 9, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU_LBB.pdf")

```

Optimistic SMU Results
```{r sim results vis SMU sum OPTI}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(SMU > LRP)
SMU_plot <- sim_sum_SMU  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Stock Management Unit\n> Limit Reference Point)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]")))+
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8),
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(SMU_plot)

opti_plotB <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


SMU <- ggdraw(plot_grid(opti_plotB, SMU_plot + theme(legend.position = "none"), legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 3, nrow = 1, axis = c("l"), align = c("hv"),
                       labels = c("", "Fraser\nSP 1.3"),
                       label_size = 8,
                       label_colour = "white",
                       label_x = 0.95, label_y = 0.85, hjust = 1))

SMU_plot <- cowplot::plot_grid(SMU)

ggsave(SMU_plot, height = 2.522159, width = 6.75, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_SMU.pdf")

```

Realistic CU Results
```{r sim results vis CU sum PESS}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(CU above LBM)
CU_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- sim_sum_CU %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]"))) + 
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(CU_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- CU_plot[[i]]+
   if(i == 1 | i == 4){
     theme(legend.position='none',
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   } else {
     theme(legend.position='none',
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   }
}

pess_plotA <- pess_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))

pess_plotB <- pess_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


CU <- ggdraw(plot_grid(pess_plotA, CU_plot[[1]], 
                                   CU_plot[[2]], CU_plot[[3]], 
                       pess_plotB, CU_plot[[4]], CU_plot[[5]], legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 4, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("", "Lower\nFraser", "Fraser\nCanyon", "Middle\nFraser","","Upper\nFraser", "North\nThompson", ""),
                       label_size = 8,
                       label_x = 0.95, label_y = 0.85, hjust = 1))

CU_plot <- cowplot::plot_grid(CU)

ggsave(CU_plot, height = 5, width = 9, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU_pess.pdf")

```

Realistic CU LBB Results
```{r sim results vis CU LBB PESS}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(CU above LBM)
LBB_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   LBB_plot[[i]] <- sim_sum_CU_LBB %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]"))) + 
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(LBB_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   LBB_plot[[i]] <- LBB_plot[[i]]+
   if(i == 1 | i == 4){
     theme(legend.position='none',
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   } else {
     theme(legend.position='none',
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   }
}

pess_plotA <- pess_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))

pess_plotB <- pess_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


LBB <- ggdraw(plot_grid(pess_plotA, LBB_plot[[1]], 
                                   LBB_plot[[2]], LBB_plot[[3]], 
                       pess_plotB, LBB_plot[[4]], LBB_plot[[5]], legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 4, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("", "Lower\nFraser", "Fraser\nCanyon", "Middle\nFraser","","Upper\nFraser", "North\nThompson", ""),
                       label_size = 8,
                       label_x = 0.95, label_y = 0.85, hjust = 1))

LBB_plot <- cowplot::plot_grid(LBB)

ggsave(LBB_plot, height = 5, width = 9, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU_LBB_pess.pdf")

```

Realistic SMU Results
```{r sim results vis SMU sum PESS}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(SMU > LRP)
SMU_plot <- sim_sum_SMU  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Stock Management Unit\n> Limit Reference Point)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]")))+
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8),
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(SMU_plot)

pess_plotB <- pess_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


SMU <- ggdraw(plot_grid(pess_plotB, SMU_plot + theme(legend.position = "none"), legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 3, nrow = 1, axis = c("l"), align = c("hv"),
                       labels = c("", "Fraser\nSP 1.3"),
                       label_size = 8,
                       label_colour = "white",
                       label_x = 0.95, label_y = 0.85, hjust = 1))

SMU_plot <- cowplot::plot_grid(SMU)

ggsave(SMU_plot, height = 2.15, width = 6.75, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_SMU_pess.pdf")

```

No Implmentation Error Results
```{r sim results vis CU sum -IMP}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(CU above LBM)
CU_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- sim_sum_CU %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 1500 or 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]"))) + 
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(CU_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   CU_plot[[i]] <- CU_plot[[i]]+
   if(i == 1 | i == 4){
     theme(legend.position='none',
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   } else {
     theme(legend.position='none',
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   }
}

opti_plotA <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))

opti_plotB <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


CU <- ggdraw(plot_grid(opti_plotA, CU_plot[[1]], 
                                   CU_plot[[2]], CU_plot[[3]], 
                       opti_plotB, CU_plot[[4]], CU_plot[[5]], legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 4, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("", "Lower\nFraser", "Fraser\nCanyon", "Middle\nFraser","","Upper\nFraser", "North\nThompson", ""),
                       label_size = 8,
                       label_x = 0.95, label_y = 0.85, hjust = 1))

CU_plot <- cowplot::plot_grid(CU)

ggsave(CU_plot, height = 5, width = 9, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU.pdf")

```

No Implmentation Error Results
```{r sim results vis CU LBB -IMP}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(CU above LBM)
LBB_plot <- list()
for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   LBB_plot[[i]] <- sim_sum_CU_LBB %>% filter(CU == i)  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)"))))),
                               CU = ifelse(CU_ID == 1, "CK-04",
                                           ifelse(CU_ID == 2, "CK-08",
                                                  ifelse(CU_ID == 3, "CK-10",
                                                         ifelse(CU_ID == 4, "CK-12", "CK-18"))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Conservation Unit\n> 20% Smax)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")))+
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]"))) + 
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))
}

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(LBB_plot[[1]])

for(i in 1:length(unique(sim_sum_CU$CU_ID))){
   LBB_plot[[i]] <- LBB_plot[[i]]+
   if(i == 1 | i == 4){
     theme(legend.position='none',
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   } else {
     theme(legend.position='none',
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))
   }
}

opti_plotA <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))

opti_plotB <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


LBB <- ggdraw(plot_grid(opti_plotA, LBB_plot[[1]], 
                                   LBB_plot[[2]], LBB_plot[[3]], 
                       opti_plotB, LBB_plot[[4]], LBB_plot[[5]], legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 4, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("", "Lower\nFraser", "Fraser\nCanyon", "Middle\nFraser","","Upper\nFraser", "North\nThompson", ""),
                       label_size = 8,
                       label_x = 0.95, label_y = 0.85, hjust = 1))

LBB_plot <- cowplot::plot_grid(LBB)

ggsave(LBB_plot, height = 5, width = 9, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_CU_LBB.pdf")

```

No Implmentation Error Results
```{r sim results vis SMU sum -IMP}

Ccols <- c("Very Low (0.00-0.04)" = "#330033",
           "Low (0.05-0.24)" = "#d01c8b", 
           "Moderately Low (0.25-0.49)" = "#f1b6da", 
           "Moderately High (0.50-0.74)" = "#f7f7f7",
           "High (0.75-0.94)" = "#b8e186",
           "Very High (0.95-1.00)" = "#4dac26")

all_breaks = seq(0, 0.45, by = 0.05)
my_labels = rep("", length(all_breaks))
my_labels[seq(1, length(my_labels), 2)] <- all_breaks[seq(1, length(my_labels), 2)]

#p(SMU > LRP)
SMU_plot <- sim_sum_SMU  %>% mutate(fail = ifelse(p_fail <= 0.04, "Very Low (0.00-0.04)",
                                          ifelse(p_fail > 0.04 & p_fail <= 0.24, "Low (0.05-0.24)",
                                                 ifelse(p_fail > 0.24 & p_fail <= 0.49, "Moderately Low (0.25-0.49)",
                                                        ifelse(p_fail > 0.49 & p_fail <= 0.74, "Moderately High (0.50-0.74)",
                                                               ifelse(p_fail > 0.74 & p_fail <= 0.94, "High (0.75-0.94)",
                                                                      "Very High (0.95-1.00)")))))) %>% 
   ggplot(aes(x = alpha, y = targetER, z = fail, fill = fail))+
   geom_tile(show.legend = c(fill = TRUE))+
   scale_fill_manual(values = Ccols, 
                     name = "P(Stock Management Unit\n> Limit Reference Point)",
                     breaks = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)")),
                     drop = F,
                     limits = rev(c("Very Low (0.00-0.04)", "Low (0.05-0.24)", "Moderately Low (0.25-0.49)",
                                    "Moderately High (0.50-0.74)", "High (0.75-0.94)", "Very High (0.95-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = c(0.35, 0.9, 1.5, 2.1),
                      sec.axis = sec_axis(~ (1-lambertW0(exp(1-.))),
                                          name = expression(paste(italic("U")[MSY])),
                                          breaks = c(0.17, 0.41, 0.60, 0.74)))+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks,
                      labels = my_labels)+
   geom_vline(xintercept = median(alpha_sp), colour = "grey20", linetype = "dashed", linewidth = 1)+
   labs(y = "CAN CYER", 
        x = expression(paste("Productivity [ln(",italic(α),")]")))+
   theme_classic() +
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8),
         axis.text.y = element_text(colour = "black"),
         axis.title.y = element_blank(),
         plot.margin = unit(c(0, 0, 0, 0), "cm"))

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(SMU_plot)

opti_plotB <- opti_plot + theme(legend.text = element_text(size = 8),
                                legend.title = element_text(size = 8),
                                plot.margin = unit(c(0, 0, 0, 0), "cm"))


SMU <- ggdraw(plot_grid(opti_plotB, SMU_plot + theme(legend.position = "none"), legend1,
                       #rel_widths = c(1, 1, 1, 1, 1, .2),
                       ncol = 3, nrow = 1, axis = c("l"), align = c("hv"),
                       labels = c("", "Fraser\nSP 1.3"),
                       label_size = 8,
                       label_colour = "white",
                       label_x = 0.95, label_y = 0.85, hjust = 1))

SMU_plot <- cowplot::plot_grid(SMU)

ggsave(SMU_plot, height = 2.15, width = 6.75, units = "in", filename = "SP_SU_1.3\\Figures\\SP\\sim_sum_SMU.pdf")

```



