---
title: "4plot & ER plot code"
author: "Colin Bailey, Isabella Borea"
date: "2025-06-26"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(cowplot)
#library(samSim)
library(tidyverse)
library(readxl)
library(ggplot2)
library(lubridate)
library(scales)
library(RColorBrewer)
library(tidyr)
library(patchwork)
library(here)

esc_dat <- read.csv(
  here("SP_SU_1.3", "Data_in", "sp_su_1.3_escape_series.csv")
)

ER_dat <- read.csv(
  here("SP_SU_1.3", "Data_in", "sp_1.3_ER_dat.csv")
)

epad_dat <- read.csv(
  here("SP_SU_1.3", "Data_in", "Fraser_Chinook_Releases_1975-2024.csv")
)

```

Code chunk to create the Spring 1.3 recruitment plot
```{r recruitment plot}

recs <- ER_dat %>%
  select(year, recruits_CYER, recruits_FMI) %>%
  pivot_longer(
    cols = c(recruits_CYER, recruits_FMI),
    names_to = "source",
    values_to = "recruits"
  ) %>%
  mutate(
    source = recode(
      source,
      recruits_CYER = "CYER",
      recruits_FMI  = "FMI"
    ))
  

# recs <- escape %>% mutate(p_spawn = 1-ER,
#                           recs = no_spawners / p_spawn) %>% group_by(ret_year) %>% 
#   summarize(smu_recs = sum(recs))


recruit <- recs %>% 
ggplot(aes(x = year, y = recruits / 1000, colour = source)) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Return year",
    y = "Recruit abundance (1000s)",
    colour = NULL
  ) +
  scale_colour_manual(
    values = c("CYER" = "black", "FMI" = "grey70")
  ) +
  scale_y_continuous(
    breaks = seq(
      0,
      max(recs$recruits, na.rm = TRUE) / 1000 + 5,
      by = 5
    )
  ) +
  scale_x_continuous(limits = c(2019, 2024)) +
  theme_classic()
print(recruit)

```

Code chunk to create the Spring 1.3 catch plot
```{r catch plot}


cat <- ER_dat %>%
  select(year, catch_CYER, catch_FMI) %>%
  pivot_longer(
    cols = c(catch_CYER, catch_FMI),
    names_to = "source",
    values_to = "catch"
  ) %>%
  mutate(
    source = recode(
      source,
      catch_CYER = "CYER",
      catch_FMI  = "FMI"
    ))
  

# recs <- escape %>% mutate(p_spawn = 1-ER,
#                           recs = no_spawners / p_spawn) %>% group_by(ret_year) %>% 
#   summarize(smu_recs = sum(recs))


catch <- cat %>% 
ggplot(aes(x = year, y = catch / 1000, colour = source)) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Return year",
    y = "Catch (1000s)",
    colour = NULL
  ) +
  scale_colour_manual(
    values = c("CYER" = "black", "FMI" = "grey70")
  ) +
  scale_y_continuous(
    breaks = seq(
      0,
      max(recs$recruits, na.rm = TRUE) / 1000,
      by = 1
    )
  ) +
  scale_x_continuous(limits = c(2019, 2024)) +
  theme_classic()
print(catch)

```

Code chunk to create the Spring 1.3 spawners plot
```{r spawners plot}

spring13_stocks <- c("Lower Fraser River_SP_1.3",
                     "Middle Fraser-Fraser Canyon_SP_1.3",
                     "Middle Fraser River_SP_1.3",
                     "Upper Fraser River_SP_1.3",
                     "North Thompson_SP_1.3"
                     ) 

smu_dat <- esc_dat %>% 
  filter(Year > 2009, 
         Stock %in% spring13_stocks)%>%
  group_by(Stock, Year) %>%
  summarize(no_spawners = sum(SpnForTrend_Wild, na.rm = TRUE), .groups = "drop" )

smu_total <- smu_dat %>%
  group_by(Year) %>%
  summarize(total_no_spawners = sum(no_spawners, na.rm = TRUE)) 
  


spawn <- smu_total %>% ggplot(aes(x = Year, y = total_no_spawners/1000))+
  geom_line(color= "black", linewidth = 1.2)+
  labs(x = "Return year", y = "Spawner abundance (1000s)")+
  scale_y_continuous(breaks = seq(0, max(smu_dat$no_spawners / 1000) + 5, by = 5))+
  scale_x_continuous(limits = c(2010, 2025))+
  theme_classic()
print(spawn)

write.csv(smu_total, "smu_esc_sp_1.3.csv")

```

Code chunk to create the Spring 1.3 exploitation rate plot
```{r ER plot}

ER <- ER_dat %>%
  select(year, FMI, CYER) %>%
  pivot_longer(
    cols = c(FMI, CYER),
    names_to = "source",
    values_to = "ER"
  ) %>%
  mutate(
    source = recode(
      source,
      CYER = "CYER",
      FMI  = "FMI"
    ))

ER <- ER %>% 
ggplot(aes(x = year, y = ER, colour = source)) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Return year",
    y = "Exploitation Rate",
    colour = NULL
  ) +
  scale_colour_manual(
    values = c("CYER" = "black", "FMI" = "grey70")
  ) +
  scale_y_continuous(
    breaks = seq(
      0,
      max(ER$ER, na.rm = TRUE) + 0.3,
      by = 0.05
    )
  ) +
  scale_x_continuous(limits = c(2019, 2024)) +
geom_hline(yintercept = 0.40, colour = "red",  linewidth = 0.8) +
geom_text(
  data = data.frame(x = 2024, y = 0.40),
  aes(x = x, y = y, label = "U[MSY]"),
  colour = "red",
  hjust = 1.1,
  vjust = -0.4,
  size = 3.5,
  parse = TRUE
) +
geom_hline(yintercept = 0.10, colour = "red", linewidth = 0.8) +
geom_text(
  data = data.frame(x = 2024, y = 0.10), # Insert finalized lower fishery reference point  
  aes(x = x, y = y, label = "FRP-L"),
  colour = "red",
  hjust = 1.1,
  vjust = -0.3,
  size = 3.5,
  parse = TRUE
) +
theme_classic()
print(ER)


```

Code chunk for combining all the plots into a single 4-panel figure
```{r 4-plot}

four_plot <- plot_grid(catch, spawn, ER, recruit,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          label_size = 12,
          align = "v",
          label_x = 0.87)
print(four_plot)

ggsave(four_plot, height = 5, width = 6 , units = "in", filename = "4plotspring.png")

```

Code chunk to create the smolt-to-age_3 survival index plot
```{r surv plot}

nic_dat %>% ggplot(aes(x = brood_year, y = smolt_age3_survival*100))+
  geom_line()+
  scale_x_continuous(limits = c(1993, 2020),
                     breaks = c(1995, 2000, 2005, 2010, 2015, 2020))+
  scale_y_continuous()+
  labs(x = "Brood year", y = "Smolt to age 3 recruit survival (%)")+
  theme_classic()

ggsave(height = 3.5, width = 4.5, units = "in", filename = "surv.png")

```

Code chunk to create the Nicola age proportions plot
```{r surv plot}

## Convert data-frame to long-form ##### 

age_data <- age_data %>%
  mutate(across(ends_with("percent"), ~ as.numeric(sub("%", "", .)) / 100))


# Pivot counts
counts_long <- age_data %>%
  pivot_longer(
    cols = starts_with("age_") & !ends_with("percent"),
    names_to = "age",
    names_prefix = "age_",
    values_to = "count"
  )

# Pivot percents
percents_long <- age_data %>%
  pivot_longer(
    cols = ends_with("percent"),
    names_to = "age",
    names_pattern = "age_(\\d+)_percent",
    values_to = "percent"
  )

# Join the two long-form datasets
age_data_long <- left_join(counts_long, percents_long, by = c("BY", "age"))

# Convert age to numeric
age_data_long <- age_data_long %>%
  mutate(age = as.numeric(age))

# Preview result
print(age_data_long)
### Change age to factor #### 

age_data_long <- age_data_long %>%
  mutate(age = as.factor(age)) 


#### Create Stacked Bar Plot #####

pal <- gray.colors(3, start=0.1, end=0.9) #gray scale option
# pal <- c("darkslategrey","azure4","azure3","azure1")
#pal <- c("#88CCEE", "#CC6677", "#DDCC77")


windows()

  
  age_data_long %>%
    ggplot(aes(x= BY, y = percent, fill = age)) +
    geom_bar(stat = "identity", position = "stack") +
    labs(
      x = "Brood Year",
      y = "Proportion (Prefishery Abundance)",
      fill = "Age"
    ) +
    scale_y_continuous(
      breaks = seq(0, 1, by = 0.1),
      expand = expansion(mult = c(0, 0.1))
    ) +
    scale_x_continuous(breaks = seq(1993, 2019, by = 1)) +
    scale_fill_manual(values = pal) +
    theme_classic() +
    theme(
      legend.position = "top",
      axis.text.x = element_text(size = 10, angle = 45, hjust = 1, face = "bold"),
      axis.text.y = element_text(size = 10, hjust = 1, face = "bold", vjust = 1)
    )
  
  ggsave("Nicola_age_structure_prefishery_abundanceBY.png",plot = last_plot(), width = 7, height = 5, units = "in", dpi = 300)

```


Code chunk to create the hatchery releases by CU plot
```{r surv plot}

Spring_1.3 <- c("CK-04", "CK-08", "CK-10", "CK-12", "CK-18")   # 5 CUs
Summer_1.3 <- c("CK-05", "CK-06", "CK-09", "CK-11", "CK-14", "CK-19")  # 6 CUs

########################################################
# 3. CLEAN + SUMMARIZE DATA
########################################################

full_years <- 1980:2024

clean_data <- epad_dat %>%
  mutate(
    Stage = case_when(
      RELEASE_STAGE_NAME %in% c("Fed Fry", "Nat Fry")      ~ "Fry",
      RELEASE_STAGE_NAME == "Smolt 0+"                     ~ "Sub-yearling Smolts",
      RELEASE_STAGE_NAME == "Smolt 1+"                     ~ "Yearling Smolts",
      TRUE ~ NA
    )
  ) %>%
  filter(!is.na(Stage)) %>%
  group_by(RELEASE_YEAR, STOCK_CU_INDEX, Stage) %>%
  summarise(TotalReleased = sum(TotalRelease, na.rm = TRUE), .groups = "drop") %>%
  complete(
    RELEASE_YEAR = full_years,
    STOCK_CU_INDEX,
    Stage,
    fill = list(TotalReleased = 0)
  )

########################################################
# 4. COLOUR-BLIND-SAFE PALETTES
########################################################

palette_spring <- c("#000000", "#E69F00", "#56B4E9",
                    "#009E73", "#F0E442")   # 5 CU colours

palette_summer <- c("#88CCEE", "#CC6677", "#DDCC77",
                    "#117733", "#332288", "#AA4499")  # 6 CU colours

########################################################
# 5. FUNCTION TO BUILD 3-PANEL LINE PLOTS
########################################################

make_group_lineplots <- function(data, cu_group, group_label, palette) {
  
  d <- data %>% filter(STOCK_CU_INDEX %in% cu_group)
  
  # Ensure palette is correctly named
  palette <- palette[1:length(cu_group)]
  names(palette) <- cu_group
  
  legend_title <- paste("CU –", group_label)
  
  # Single function to avoid repeating code
  make_stage_plot <- function(stage_name, y_label) {
    d %>%
      filter(Stage == stage_name) %>%
      ggplot(aes(x = RELEASE_YEAR, y = TotalReleased,
                 color = STOCK_CU_INDEX)) +
      geom_line(size = 1) +
      geom_point(size = 2) +
      scale_color_manual(values = palette, name = legend_title) +
      scale_y_continuous(labels = label_comma()) +
      theme_bw(base_size = 12) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      labs(x = "Release Year", y = y_label)
  }
  
  list(
    fry   = make_stage_plot("Fry", "Fry Released"),
    sub   = make_stage_plot("Sub-yearling Smolts", "Sub-yearlings Released"),
    year  = make_stage_plot("Yearling Smolts", "Yearlings Released")
  )
}

########################################################
# 6. CREATE SPRING & SUMMER PANELS
########################################################

Spring_plot <- make_group_lineplots(clean_data, Spring_1.3, "Spring 1.3", palette_spring)
Summer_plot <- make_group_lineplots(clean_data, Summer_1.3, "Summer 1.3", palette_summer)

########################################################
# 7. BUILD 1×3 PANELS
########################################################

Spring_panel <- Spring_plot$fry / Spring_plot$sub / Spring_plot$year
Spring_panel <- Spring_panel + plot_layout(guides = "collect") &
  theme(legend.position = "right")

Summer_panel <- Summer_plot$fry / Summer_plot$sub / Summer_plot$year
Summer_panel <- Summer_panel + plot_layout(guides = "collect") &
  theme(legend.position = "right")

########################################################
# 8. DISPLAY AND SAVE
########################################################

windows(); print(Spring_panel)
windows(); print(Summer_panel)

ggsave("Spring_1.3_3Panel_LinePlotVertical.png",
       Spring_panel, width = 6, height = 10, units = "in", dpi = 300)

ggsave("Summer_1.3_3Panel_LinePlotVertical.png",
       Summer_panel, width = 6, height = 12, units = "in", dpi = 300)

```