---
title: "4plot & ER plot code"
author: "Colin Bailey, Isabella Borea"
date: "2025-06-26"
output: html_document
---

This code chunk loads the required packages and the data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(cowplot)
#library(samSim)
library(tidyverse)
library(readxl)
library(ggplot2)
library(lubridate)
library(scales)
library(RColorBrewer)
library(tidyr)
library(patchwork)
library(here)

esc_dat <- read.csv(
  here("SP_SU_1.3", "Data_in", "sp_su_1.3_escape_series.csv")
)

ER_dat <- read.csv(
  here("SP_SU_1.3", "Data_in", "su_1.3_ER_dat.csv")
)

epad_dat <- read.csv(
  here("SP_SU_1.3", "Data_in", "Fraser_Chinook_Releases_1975-2024.csv")
)

wsp_cu_dat <-read.csv(
  here("SP_SU_1.3", "Data_in", "Retro_Synoptic_Details_FraserSandbox.csv")
)
wsp_cu_lookup <- read.csv(
  here("SP_SU_1.3", "Data_in", "MOD_MAIN_CU_LOOKUP_FOR_SOS_IP_082025.csv")
)

wsp_cu_years <- read.csv(
  here("SP_SU_1.3", "Data_in", "CU_Data_FraserSandbox_1.3_startyrs.csv")
)

survival_dat <-read.csv(
  here("SP_SU_1.3", "Data_in", "CKO_survival_dat_dec_2025.csv")
)

pHOS_dat <-read.csv(
  here("SP_SU_1.3", "Data_in", "CKO_pHOS_feb_2025.csv")
)
```

Code chunk to create the Summer 1.3 recruitment plot
```{r recruitment plot}

recs <- ER_dat %>%
  # select(year, recruits_CYER) %>%
  select(year, recruits_CYER, recruits_FMI) %>%
  pivot_longer(
    # cols = c(recruits_CYER),
    cols = c(recruits_CYER, recruits_FMI),
    names_to = "source",
    values_to = "recruits"
  ) %>%
  mutate(
    source = recode(
      source,
      recruits_CYER = "CYER",
      recruits_FMI  = "FMI"
    ))
  

# recs <- escape %>% mutate(p_spawn = 1-ER,
#                           recs = no_spawners / p_spawn) %>% group_by(ret_year) %>% 
#   summarize(smu_recs = sum(recs))


recruit <- recs %>% 
ggplot(aes(x = year, y = recruits / 1000, colour = source)) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Return year",
    y = "Recruit abundance (1000s)",
    colour = NULL
  ) +
  scale_colour_manual(
    # values= c("CYER" = "black")
    values = c("CYER" = "black", "FMI" = "grey70") # for res doc version will show both ERs
  ) +
  scale_y_continuous(
    breaks = seq(
      0,
      max(recs$recruits, na.rm = TRUE) / 1000 + 5,
      by = 5
    )
  ) +
  scale_x_continuous(limits = c(2019, 2024)) +
  theme_classic()
print(recruit)


```

Code chunk to create the Spring 1.2 catch plot
```{r catch plot}

cat <- ER_dat %>%
  # select(year, catch_CYER) %>%
  select(year, catch_CYER, catch_FMI) %>%
  pivot_longer(
    # cols = c(catch_CYER),
    cols = c(catch_CYER, catch_FMI),
    names_to = "source",
    values_to = "catch"
  ) %>%
  mutate(
    source = recode(
      source,
      catch_CYER = "CYER",
      catch_FMI  = "FMI"
    ))
  

# recs <- escape %>% mutate(p_spawn = 1-ER,
#                           recs = no_spawners / p_spawn) %>% group_by(ret_year) %>% 
#   summarize(smu_recs = sum(recs))


catch <- cat %>% 
ggplot(aes(x = year, y = catch / 1000, colour = source)) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Return year",
    y = "Catch (1000s)",
    colour = NULL
  ) +
  scale_colour_manual(
    # values = c("CYER" = "black")
    values = c("CYER" = "black", "FMI" = "grey70")
  ) +
  scale_y_continuous(
    breaks = seq(
      0,
      max(recs$recruits, na.rm = TRUE) / 1000,
      by = 1
    )
  ) +
  scale_x_continuous(limits = c(2019, 2024)) +
  theme_classic()
print(catch)

# cat <- escape %>% mutate(p_spawn = 1-ER,
#                           recs = no_spawners / p_spawn,
#                           catch = ER * recs) %>% group_by(ret_year) %>% 
#   summarize(smu_catch = sum(catch))


```

Code chunk to create the Summer 1.3 spawners plot
```{r spawners plot}

summer13_stocks <- c("Lower Fraser River_SU_1.3",
                     "Lower Fraser River-Upper Pitt_SU_1.3",
                     "Middle Fraser River_SU_1.3",
                     "Middle Fraser River-Portage_FA_1.3",
                     "North Thompson_SU_1.3",
                     "South Thompson_SU_1.3") 

smu_dat <- esc_dat %>% 
  filter(Year > 2005, 
         Stock %in% summer13_stocks,
         !(Stock == "Lower Fraser River_SU_1.3" & CU_ID == "CK-06"))%>% #CK-06 removed from smu-level escapement roll up because of data deficient status under WSP
  group_by(Stock, Year) %>%
  summarize(no_spawners = sum(SpnForTrend_Wild, na.rm = TRUE), .groups = "drop" )

smu_total <- smu_dat %>%
  group_by(Year) %>%
  summarize(total_no_spawners = sum(no_spawners, na.rm = TRUE))
  


spawn <- smu_total %>% ggplot(aes(x = Year, y = total_no_spawners/1000))+
  geom_line(color= "black", linewidth = 1.2)+
  labs(x = "Return year", y = "Spawner abundance (1000s)")+
  scale_y_continuous(breaks = seq(0, max(smu_dat$no_spawners / 1000) + 5, by = 5))+
  scale_x_continuous(limits = c(2004, 2024),
                     breaks = seq(2004,2024, by = 4) )+
  theme_classic()
print(spawn)

write.csv(smu_total, "smu_esc_su_1.3.csv")

# cu_esc <- escape %>% mutate(cu = ifelse(stk %in% c(1:4), "Lth", "Bst"),
#                             p_spawn = 1-ER,
#                             recruits = no_spawners / p_spawn) %>% 
#   group_by(cu, ret_year) %>%
#   summarize(sum_cu = sum(no_spawners),
#             sum_cu_rec = sum(recruits))
# 
# write.csv(cu_esc, "cu_esc.csv")

```

Code chunk to create the Summer 1.3 exploitation rate plot
```{r ER plot}


ER <- ER_dat %>%
  # select(year, CYER) %>%
  select(year, FMI, CYER) %>%
  pivot_longer(
    # cols = c(CYER),
    cols = c(FMI, CYER),
    names_to = "source",
    values_to = "ER"
  ) %>%
  mutate(
    source = recode(
      source,
      CYER = "CYER",
      FMI  = "FMI"
    ))

ER <- ER %>% 
ggplot(aes(x = year, y = ER, colour = source)) +
  geom_line(linewidth = 1.2) +
  labs(
    x = "Return year",
    y = "Exploitation Rate",
    colour = NULL
  ) +
  scale_colour_manual(
    # values = c("CYER"= "black")
    values = c("CYER" = "black", "FMI" = "grey70")
  ) +
  scale_y_continuous(
    breaks = seq(
      0,
      max(ER$ER, na.rm = TRUE) + 0.3,
      by = 0.05
    )
  ) +
  scale_x_continuous(limits = c(2019, 2024)) +
geom_hline(yintercept = 0.40, colour = "red",  linewidth = 0.8) +
# geom_text(
#   data = data.frame(x = 2024, y = 0.40),
#   aes(x = x, y = y, label = "U[MSY]"),
#   colour = "red",
#   hjust = 1.1,
#   vjust = 1.0,
#   size = 3.5,
#   parse = TRUE
# ) +
# geom_hline(yintercept = 0.10, colour = "red", linewidth = 0.8, linetype = "dashed") +
# geom_text(
#   data = data.frame(x = 2024, y = 0.10), # Insert finalized lower fishery reference point 
#   aes(x = x, y = y, label = "FRP-L"),
#   colour = "red",
#   hjust = 1.1,
#   vjust = 1.0,
#   size = 3.5,
#   parse = TRUE
# ) +
theme_classic()
print(ER)

# 
# ER <- ER %>% ggplot(aes(x = year))+
#   geom_rect(aes(xmin = 2019, xmax = 2024, ymin = 0.02, ymax = 0.50), fill = "lightgrey", alpha = 0.01)+
#   geom_line(aes(x = year, y = tot_mort_um), colour = "black")+
#   geom_hline(aes(yintercept = 0.34), colour = "red")+
#   scale_x_continuous(limits = c(1989, 2024))+
#   labs(x = "Return year", y = "Exploitation rate")+
#   theme_classic()


```

Code chunk for combining all the plots into a single 4-panel figure
```{r 4-plot}

four_plot <- plot_grid(catch, spawn, ER, recruit,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          label_size = 12,
          align = "v",
          label_x = 0.87)
print(four_plot)

ggsave(four_plot, height = 5, width = 10 , units = "in", filename = "4plotFSAR_SU1.3.png")

```

Code chunk to create the smolt-to-age_3 survival index plot
```{r surv plot}

nic_dat %>% ggplot(aes(x = brood_year, y = smolt_age3_survival*100))+
  geom_line()+
  scale_x_continuous(limits = c(1993, 2020),
                     breaks = c(1995, 2000, 2005, 2010, 2015, 2020))+
  scale_y_continuous()+
  labs(x = "Brood year", y = "Smolt to age 3 recruit survival (%)")+
  theme_classic()

ggsave(height = 3.5, width = 4.5, units = "in", filename = "surv.png")

```

Code chunk to create the WSP Spawner Abundance by CU Plot
```{r surv plot}
# Read data
retro.summary.tbl <- wsp_cu_dat
cu.info <- wsp_cu_lookup
data.raw <- wsp_cu_years %>%
  mutate(CU_ID = gsub("_","-",CU_ID)) %>%
  filter(!is.na(CU_Name)) %>%
  left_join(cu.info %>% select(CU_Name,Group), by="CU_Name")

# ===============================
# 1) Select CU group
# ===============================
cu_group_pattern <- "(SU_1.3|FA_1.3)"
cu_group_label   <- "SU_FA_1.3"

cu.panels <- cu.info %>%
  filter(str_detect(CU_Name, cu_group_pattern)) %>%
  pull(CU_ID_Alt2_CULookup) %>%
  unique() %>%
  sort()

if(length(cu.panels) == 0) stop("No CUs found matching group!")

# Panel letters
panel_labels <- paste0(LETTERS[1:length(cu.panels)], ")")
cu_panel_map <- tibble(CU_ID_Alt2_CULookup = cu.panels,
                       panel_label = panel_labels)

# ===============================
# 2) Prepare data
# ===============================
plot_data <- data.raw %>%
  filter(CU_ID %in% cu.info$CU_ID[cu.info$CU_ID_Alt2_CULookup %in% cu.panels]) %>%
  select(CU_ID, Year, SpnForAbd_Wild) %>%
  left_join(cu.info %>% select(CU_ID, CU_ID_Alt2_CULookup), by="CU_ID") %>%
  left_join(cu_panel_map, by="CU_ID_Alt2_CULookup") %>%
  rename(Natural_Spawners = SpnForAbd_Wild)

# ===============================
# 3) Geometric mean function
# ===============================
calc_gmean <- function(x, n){
  n <- n[1]
  if(length(x) < n) return(rep(NA, length(x)))
  exp(stats::filter(log(x), rep(1/n, n), sides = 1))
}

# Add geometric mean
avggen_lookup <- cu.info %>%
  select(CU_ID_Alt2_CULookup, Avg_Gen)

plot_data <- plot_data %>%
  left_join(avggen_lookup, by = "CU_ID_Alt2_CULookup") %>%
  group_by(CU_ID_Alt2_CULookup) %>%
  mutate(Geomean = calc_gmean(Natural_Spawners, Avg_Gen[1])) %>%
  ungroup()

# Create full panel labels
plot_data <- plot_data %>%
  mutate(panel_label_full = paste0(panel_label, " ", CU_ID_Alt2_CULookup))

# ===============================
# 4) Generate individual plots
# ===============================
plot_list <- lapply(unique(plot_data$panel_label_full), function(panel_name){
  df <- plot_data %>% filter(panel_label_full == panel_name)
  
  ggplot(df, aes(x = Year)) +
    geom_point(aes(y = Natural_Spawners), color = "darkblue", size = 2) +
    geom_line(aes(y = Natural_Spawners), color = "darkblue") +
    geom_line(aes(y = Geomean), color = "red", size = 1.2) +
    scale_y_continuous(labels = scales::comma) +
    labs(x = "Year", y = "Natural Spawner Abundance") +
    ggtitle(panel_name) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", color = "darkblue", hjust = 0),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 12),
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(color = "gray90")
    )
})

# ===============================
# 5) Arrange plots in a grid
# ===============================
n_panels <- length(plot_list)
ncol_grid <- ceiling(sqrt(n_panels))
nrow_grid <- ceiling(n_panels / ncol_grid)
final_plot <- wrap_plots(plot_list, ncol = ncol_grid)

print(final_plot)
# ===============================
# 6) Dynamic PNG size
# ===============================
panel_width  <- 3.8  # width per panel in inches
panel_height <- 3.0  # height per panel in inches

png_width  <- ncol_grid * panel_width
png_height <- nrow_grid * panel_height

# ===============================
# 7) Save to PNG
# ===============================
ggsave(filename = paste0( cu_group_label, "_Natural_Spawner_Abundance_.png"),
       plot = final_plot,
       width = png_width,
       height = png_height,
       units = "in",
       dpi = 300)

```


Code chunk to create the hatchery releases by CU plot
```{r surv plot}

Spring_1.3 <- c("CK-04", "CK-08", "CK-10", "CK-12", "CK-18")   # 5 CUs
Summer_1.3 <- c("CK-05", "CK-06", "CK-09", "CK-11", "CK-14", "CK-19")  # 6 CUs

########################################################
# 3. CLEAN + SUMMARIZE DATA
########################################################

full_years <- 1980:2024

clean_data <- epad_data %>%
  mutate(
    Stage = case_when(
      RELEASE_STAGE_NAME %in% c("Fed Fry", "Nat Fry")      ~ "Fry",
      RELEASE_STAGE_NAME == "Smolt 0+"                     ~ "Sub-yearling Smolts",
      RELEASE_STAGE_NAME == "Smolt 1+"                     ~ "Yearling Smolts",
      TRUE ~ NA
    )
  ) %>%
  filter(!is.na(Stage)) %>%
  group_by(RELEASE_YEAR, STOCK_CU_INDEX, Stage) %>%
  summarise(TotalReleased = sum(TotalRelease, na.rm = TRUE), .groups = "drop") %>%
  complete(
    RELEASE_YEAR = full_years,
    STOCK_CU_INDEX,
    Stage,
    fill = list(TotalReleased = 0)
  )

########################################################
# 4. COLOUR-BLIND-SAFE PALETTES
########################################################

palette_spring <- c("#000000", "#E69F00", "#56B4E9",
                    "#009E73", "#F0E442")   # 5 CU colours

palette_summer <- c("#88CCEE", "#CC6677", "#DDCC77",
                    "#117733", "#332288", "#AA4499")  # 6 CU colours

########################################################
# 5. FUNCTION TO BUILD 3-PANEL LINE PLOTS
########################################################

make_group_lineplots <- function(data, cu_group, group_label, palette) {
  
  d <- data %>% filter(STOCK_CU_INDEX %in% cu_group)
  
  # Ensure palette is correctly named
  palette <- palette[1:length(cu_group)]
  names(palette) <- cu_group
  
  legend_title <- paste("CU –", group_label)
  
  # Single function to avoid repeating code
  make_stage_plot <- function(stage_name, y_label) {
    d %>%
      filter(Stage == stage_name) %>%
      ggplot(aes(x = RELEASE_YEAR, y = TotalReleased,
                 color = STOCK_CU_INDEX)) +
      geom_line(size = 1) +
      geom_point(size = 2) +
      scale_color_manual(values = palette, name = legend_title) +
      scale_y_continuous(labels = label_comma()) +
      theme_bw(base_size = 12) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      labs(x = "Release Year", y = y_label)
  }
  
  list(
    fry   = make_stage_plot("Fry", "Fry Released"),
    sub   = make_stage_plot("Sub-yearling Smolts", "Sub-yearlings Released"),
    year  = make_stage_plot("Yearling Smolts", "Yearlings Released")
  )
}

########################################################
# 6. CREATE SPRING & SUMMER PANELS
########################################################

Spring_plot <- make_group_lineplots(clean_data, Spring_1.3, "Spring 1.3", palette_spring)
Summer_plot <- make_group_lineplots(clean_data, Summer_1.3, "Summer 1.3", palette_summer)

########################################################
# 7. BUILD 1×3 PANELS
########################################################

Spring_panel <- Spring_plot$fry / Spring_plot$sub / Spring_plot$year
Spring_panel <- Spring_panel + plot_layout(guides = "collect") &
  theme(legend.position = "right")

Summer_panel <- Summer_plot$fry / Summer_plot$sub / Summer_plot$year
Summer_panel <- Summer_panel + plot_layout(guides = "collect") &
  theme(legend.position = "right")

########################################################
# 8. DISPLAY AND SAVE
########################################################

windows(); print(Spring_panel)
windows(); print(Summer_panel)

ggsave("Spring_1.3_3Panel_LinePlotVertical.png",
       Spring_panel, width = 6, height = 10, units = "in", dpi = 300)

ggsave("Summer_1.3_3Panel_LinePlotVertical.png",
       Summer_panel, width = 6, height = 12, units = "in", dpi = 300)

```
Code Chunk for Chilko Survival Plot 

```{r surv plot}


CKO_survival <- survival_dat %>%
  filter(stock == "CKO", BY >= 2014, BY <= 2020)


CKO_survival %>% ggplot(aes(x = BY, y = survival*100))+
  geom_line(linewidth = 1.0)+
  # geom_point()+
  scale_x_continuous(limits = c(2014, 2020),
                     breaks = c(2014, 2015,2016,2017,2018,2019,2020))+
  scale_y_continuous()+
  labs(x = "Brood year", y = "Smolt to age 3 survival (%)")+
  theme_classic()
print(CKO_survival)

ggsave(height = 3.5, width = 4.5, units = "in", filename = "CKO_surv.png")

```
Code Chunk for Chilko pHOS Plot 

```{r surv plot}


pHOS_dat %>% ggplot(aes(x = return_year, y = afc_rate))+
  geom_line(linewidth = 1.0)+
  geom_point()+
  scale_x_continuous(limits = c(2019, 2024),
                     breaks = c(2019,2020, 2021,2022,2023,2024))+
  labs(x = "Return Year", y = "pHOS")+
  theme_classic()
print(pHOS_dat)

ggsave(height = 3.5, width = 4.5, units = "in", filename = "CKO_pHOS.png")

```
