---
title: "Icecream plot code"
author: "Colin Bailey"
date: "2026-01-02"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(cowplot)
library(boot)
library(ggpattern)
library(patchwork)

e_dat <- read.csv("SP_SU_1.3\\Data_in\\FlatFile_For_SalmonScanner_BySite.csv")
sep_dat <- read.csv("SP_SU_1.3\\Data_in\\Fraser_Chinook_Releases_1975-2024.csv")

```


```{r data manip}
#Chilko Return Rates - This is based on Brood year and includes all return ages 
#Fed Fry 2014-2018
# Min = .03 Mean = .11 Max .29 SD = .12
#Smolt 2014-2019
# Min = .21 Mean = .57 Max 1.22 SD = .43

spawn <- seq(0, 10000, by = 50)
smolt <- seq(0, 200000, by = 10000) # 10k min as that is the min release we typically do #100k max as that is easy for mental math
fry <- seq(0, 200000, by = 10000)

#can expand this code chunk to include calculations for fry survival
phos_df <- expand.grid(x=spawn, y=smolt, z=fry) %>% 
  dplyr::select(spawn = x, smolt = y, fry=z) %>% 
  mutate(l_h_spawn_smolt = smolt * 0.0021, 
         u_h_spawn_smolt = smolt * 0.0122,
         l_phos_smolt = l_h_spawn_smolt / spawn,
         u_phos_smolt = u_h_spawn_smolt / spawn,
         l_h_spawn_fry = fry * 0.0003, 
         u_h_spawn_fry = fry * 0.0029,
         l_phos_fry = l_h_spawn_fry / spawn,
         u_phos_fry = u_h_spawn_fry / spawn)
```

Currently set up the section below to make 2 plots for a given lifestage (example is smolts) - one for the lowest potential PHOS, and a second for the highest potential PHOS.THis may make more sense than creating broad probability categories that span the range of survival rates if the rates spawn an order of magnitude. Alternatively, it may make more sense to just report the maximum potential PHOS because we all know that survival can go to zero for a variety of reasons. 
```{r icecream plot}

#can update these categories to meaningful text and PHOS ranges for SEP
Ccols <- c("Wild (0.00-0.02)" = "#4dac26",
           "Integrated-wild (0.02-0.19)" = "#b8e186", 
           "Integrated-transition (0.19-0.47)" = "#f7f7f7", 
           "Integrated-hatchery (0.47-1.00)" = "#d01c8b")

#x-axis ticks
all_breaks_x = seq(0, 200, length.out = 21)
my_labels_x = rep("", length(all_breaks_x))
my_labels_x[seq(1, length(my_labels_x), 4)] <- all_breaks_x[seq(1, length(my_labels_x), 4)]

#y-axis ticks
all_breaks_y = seq(0, 10, by = 0.5)
my_labels_y = rep("", length(all_breaks_y))
my_labels_y[seq(1, length(my_labels_y), 2)] <- all_breaks_y[seq(1, length(my_labels_y), 2)]

#lower pHOS for smolt releases
p_l_phos_smolt <- phos_df %>%  mutate(l_phos_smolt = ifelse(l_phos_smolt <= 0.02, "Wild (0.00-0.02)",
                                          ifelse(l_phos_smolt > 0.02 & l_phos_smolt <= 0.19, "Integrated-wild (0.02-0.19)",
                                                 ifelse(l_phos_smolt > 0.19 & l_phos_smolt <= 0.47, "Integrated-transition (0.19-0.47)",
                                                        "Integrated-hatchery (0.47-1.00)")))) %>% 
   ggplot(aes(x = smolt/1000, y = spawn/1000, z = l_phos_smolt, fill = l_phos_smolt))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols,
                     name = "pHOS Designation",
                     breaks = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)")),
                     drop = F,
                     limits = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks_y,
                      labels = my_labels_y)+
   labs(y = "Total Spawner Abundance (1000s)", 
        x = "Smolt Release Abundance (1000s)") + 
   theme_classic()+
   theme(legend.text = element_text(size = 8),
         legend.title = element_text(size = 8))

#upper pHOS for smolt releases
p_u_phos_smolt <- phos_df %>%  mutate(u_phos_smolt = ifelse(u_phos_smolt <= 0.02, "Wild (0.00-0.02)",
                                          ifelse(u_phos_smolt > 0.02 & u_phos_smolt <= 0.19, "Integrated-wild (0.02-0.19)",
                                                 ifelse(u_phos_smolt > 0.19 & u_phos_smolt <= 0.47, 
                                                        "Integrated-transition (0.19-0.47)",
                                                        "Integrated-hatchery (0.47-1.00)")))) %>% 
   ggplot(aes(x = smolt/1000, y = spawn/1000, z = u_phos_smolt, fill = u_phos_smolt))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols,
                     name = "pHOS Designation",
                     breaks = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)")),
                     drop = F,
                     limits = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks_y,
                      labels = my_labels_y)+
   labs(y = "Total Spawner Abundance (1000s)", 
        x = "Smolt Release Abundance (1000s)") + 
   theme_classic()+
   theme(legend.position = "none")


#lower pHOS for fry releases
p_l_phos_fry <- phos_df %>%  mutate(l_phos_fry = ifelse(l_phos_fry <= 0.02, "Wild (0.00-0.02)",
                                          ifelse(l_phos_fry > 0.02 & l_phos_fry <= 0.19, "Integrated-wild (0.02-0.19)",
                                                 ifelse(l_phos_fry > 0.19 & l_phos_fry <= 0.47, "Integrated-transition (0.19-0.47)",
                                                        "Integrated-hatchery (0.47-1.00)")))) %>% 
   ggplot(aes(x = fry/1000, y = spawn/1000, z = l_phos_fry, fill = l_phos_fry))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols,
                     name = "pHOS Designation",
                     breaks = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)")),
                     drop = F,
                     limits = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks_y,
                      labels = my_labels_y)+
   labs(y = "Total Spawner Abundance (1000s)", 
        x = "Fry Release Abundance (1000s)") + 
   theme_classic()+
   theme(legend.position = "none")

#upper pHOS for fry releases
p_u_phos_fry <- phos_df %>%  mutate(u_phos_fry = ifelse(u_phos_fry <= 0.02, "Wild (0.00-0.02)",
                                          ifelse(u_phos_fry > 0.02 & u_phos_fry <= 0.19, "Integrated-wild (0.02-0.19)",
                                                 ifelse(u_phos_fry > 0.19 & u_phos_fry <= 0.47, "Integrated-transition (0.19-0.47)",
                                                        "Integrated-hatchery (0.47-1.00)")))) %>% 
   ggplot(aes(x = fry/1000, y = spawn/1000, z = u_phos_fry, fill = u_phos_fry))+
   geom_raster(show.legend = c(fill = TRUE), interpolate = F)+
   scale_fill_manual(values = Ccols,
                     name = "pHOS Designation",
                     breaks = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)")),
                     drop = F,
                     limits = rev(c("Wild (0.00-0.02)", "Integrated-wild (0.02-0.19)", "Integrated-transition (0.19-0.47)",
                                    "Integrated-hatchery (0.47-1.00)"))) +
   scale_x_continuous(expand = c(0,0),
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0),
                      breaks = all_breaks_y,
                      labels = my_labels_y)+
   labs(y = "Total Spawner Abundance (1000s)", 
        x = "Fry Release Abundance (1000s)") + 
   theme_classic()+
   theme(legend.position = "none")

get_legend <- function(plot, legend = NULL) {
  
  gt <- ggplotGrob(plot)
  
  pattern <- "guide-box"
  if (!is.null(legend)) {
    pattern <- paste0(pattern, "-", legend)
  }
  
  indices <- grep(pattern, gt$layout$name)

  not_empty <- !vapply(
    gt$grobs[indices], 
    inherits, what = "zeroGrob", 
    FUN.VALUE = logical(1)
  )
  indices <- indices[not_empty]
  
  if (length(indices) > 0) {
    return(gt$grobs[[indices[1]]])
  }
  return(NULL)
}

legend1 = get_legend(p_l_phos_smolt +  
                     theme(legend.text = element_text(size = 8),
                           legend.title = element_text(size = 8)))


pHOS <- ggdraw(plot_grid(p_l_phos_smolt + theme(axis.title.x = element_text(colour = "white"),
                                            axis.text.x = element_text(colour = "white"),
                                            axis.title.y = element_text(colour = "white"),
                                           axis.text.y = element_text(colour = "white"),
                                            plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                            legend.position = "none"), 
                       p_l_phos_fry+ theme(axis.title.x = element_text(colour = "white"),
                                           axis.text.x = element_text(colour = "white"),
                                           axis.title.y = element_text(colour = "white"),
                                           axis.text.y = element_text(colour = "white"),
                                           plot.margin = unit(c(0, 0, 0, 0), "cm")),
                       p_u_phos_smolt + theme(axis.title.x = element_text(colour = "white"),
                                              axis.text.x = element_text(colour = "white"),
                                              axis.title.y = element_text(colour = "white"),
                                              axis.text.y = element_text(colour = "white"),
                                              plot.margin = unit(c(0, 0, 0, 0), "cm")),
                       p_u_phos_fry + theme(axis.title.x = element_text(colour = "white"),
                                            axis.text.x = element_text(colour = "white"),
                                            axis.title.y = element_text(colour = "white"),
                                            axis.text.y = element_text(colour = "white"),
                                            plot.margin = unit(c(0, 0, 0, 0), "cm")),
                       ncol = 2, nrow = 2, axis = c("l"), align = c("hv"),
                       labels = c("b", "c", "e", "f"),
                       label_size = 8,
                       label_x = 0.95, label_y = 1.00, hjust = 1))

```




```{r context plots}

edat <- e_dat %>% filter(Year %in% c(2014:2024)) %>% dplyr::select(year = Year, esc = TotalInfilled, CU = CU_ID, Pop_Name) %>% 
   filter(CU %in% c("CK-05", "CK-06", "CK-09", "CK-11", "CK-14", "CK-19", "CK-04", "CK-08", "CK-10", "CK-12", "CK-18")) %>% 
   mutate(SMU = ifelse(CU %in% c("CK-05", "CK-06", "CK-09", "CK-11", "CK-14", "CK-19"), "SU_1.3", "SP_1.3"))

SP_1.3_plot <- edat %>% filter(SMU == "SP_1.3") %>% drop_na() %>% 
   ggplot()+
   geom_density(aes(x = esc/1000), fill = "grey")+
   scale_x_continuous(limits = c(0, 10),
                      expand = c(0,0),
                      n.breaks = 21,
                      breaks = all_breaks_y,
                      labels = my_labels_y)+
   scale_y_continuous(expand = c(0,0))+
   labs(x = "Spawner abundance\n(1000s)", y = "Frequency")+
   theme_classic()+
   coord_flip()
   

SU_1.3_plot <- edat %>% filter(SMU == "SU_1.3") %>% drop_na() %>% 
   ggplot()+
   geom_density(aes(x = esc/1000), fill = "grey")+
   scale_x_continuous(limits = c(0, 10),
                      expand = c(0,0),
                      n.breaks = 21,
                      breaks = all_breaks_y,
                      labels = my_labels_y)+
   scale_y_continuous(expand = c(0,0))+
   labs(x = "Spawner abundance\n(1000s)", y = "Frequency")+
   theme_classic()+
   coord_flip()

SP_plots <- ggdraw(plot_grid(SP_1.3_plot + theme(axis.title.x = element_text(colour = "white"),
                                                 axis.text.x = element_text(colour = "white"),
                                                 plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                 legend.position = "none"), 
                             SP_1.3_plot + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                 legend.position = "none"), 
                        ncol = 1, nrow = 2, axis = c("l"), align = c("hv"),
                        label_size = 8,
                        labels = c("a", "d"),
                        label_x = 0.95, label_y = 1.00, hjust = 1))

SU_plots <- ggdraw(plot_grid(SU_1.3_plot + theme(axis.title.x = element_text(colour = "white"),
                                                 axis.text.x = element_text(colour = "white"),
                                                 plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                 legend.position = "none"), 
                             SU_1.3_plot + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                 legend.position = "none"), 
                        ncol = 1, nrow = 2, axis = c("l"), align = c("hv"),
                        label_size = 8,
                        labels = c("a", "d"),
                        label_x = 0.95, label_y = 1.00, hjust = 1))

h_dat <- sep_dat %>% filter(BROOD_YEAR %in% c(2014:2024)) %>% dplyr::select(year = BROOD_YEAR, rel_code = RELEASE_STAGE_NAME,
                                                                   CU = REL_CU_INDEX, Pop_Name = STOCK_NAME, t_rel = TotalRelease) %>%
   filter(CU %in% c("CK-05", "CK-06", "CK-09", "CK-11", "CK-14", "CK-19", "CK-04", "CK-08", "CK-10", "CK-12", "CK-18")) %>% 
   mutate(SMU = ifelse(CU %in% c("CK-05", "CK-06", "CK-09", "CK-11", "CK-14", "CK-19"), "SU_1.3", "SP_1.3")) %>% 
   mutate(rel_stage = ifelse(str_detect(rel_code, "Fed"), "fry", 
                             ifelse(str_detect(rel_code, "Unfed"), "fry",
                                    ifelse(str_detect(rel_code, "Smolt 1+"), "smolt", NA)))) %>% drop_na()

SP_1.3_smolt <- h_dat %>% filter(SMU == "SP_1.3" & rel_stage == "smolt") %>%
   ggplot()+
   geom_density(aes(x = t_rel/1000), fill = "grey")+
   scale_x_continuous(limits = c(0, 200),
                      #expand = c(0,0),
                      n.breaks = 21,
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0))+
   labs(x = "Smolt Release Abundance\n(1000s)", y = "Frequency")+
   theme_classic()

SP_1.3_fry <- h_dat %>% filter(SMU == "SP_1.3" & rel_stage == "fry") %>%
   ggplot()+
   geom_density(aes(x = t_rel/1000), fill = "grey")+
   scale_x_continuous(limits = c(0, 200),
                      #expand = c(0,0),
                      n.breaks = 21,
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0))+
   labs(x = "Fry Release Abundance\n(1000s)", y = "Frequency")+
   theme_classic()

SU_1.3_smolt <- h_dat %>% filter(SMU == "SU_1.3" & rel_stage == "smolt") %>%
   ggplot()+
   geom_density(aes(x = t_rel/1000), fill = "grey")+
   scale_x_continuous(limits = c(0, 200),
                      #expand = c(0,0),
                      n.breaks = 21,
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0))+
   labs(x = "Smolt Release Abundance\n(1000s)", y = "Frequency")+
   theme_classic()

SU_1.3_fry <- h_dat %>% filter(SMU == "SU_1.3" & rel_stage == "fry") %>%
   ggplot()+
   geom_density(aes(x = t_rel/1000), fill = "grey")+
   scale_x_continuous(limits = c(0, 200),
                      #expand = c(0,0),
                      n.breaks = 21,
                      breaks = all_breaks_x,
                      labels = my_labels_x)+
   scale_y_continuous(expand = c(0,0))+
   labs(x = "Fry Release Abundance\n(1000s)", y = "Frequency")+
   theme_classic()

SP_enh_plots <- ggdraw(plot_grid(SP_1.3_smolt + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                      legend.position = "none"), 
                                 SP_1.3_fry + theme(axis.title.y = element_text(colour = "white"),
                                                    axis.text.y = element_text(colour = "white"),
                                                    plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                    legend.position = "none"), 
                        ncol = 2, nrow = 1, axis = c("l"), align = c("hv"),
                        label_size = 8,
                        labels = c("h", "i"),
                        label_x = 0.95, label_y = 1.00, hjust = 1))

SU_enh_plots <- ggdraw(plot_grid(SU_1.3_smolt + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                      legend.position = "none"), 
                                 SU_1.3_fry + theme(axis.title.y = element_text(colour = "white"),
                                                    axis.text.y = element_text(colour = "white"),
                                                    plot.margin = unit(c(0, 0, 0, 0), "cm"),
                                                    legend.position = "none"), 
                        ncol = 2, nrow = 1, axis = c("l"), align = c("hv"),
                        label_size = 8,
                        labels = c("h", "i"),
                        label_x = 0.95, label_y = 1.00, hjust = 1))

pHOS_tool_SPa <- cowplot::plot_grid(SP_plots,pHOS,
                              ncol = 2, nrow = 1,
                              axis = c("l"), align = c("hv"),
                              rel_widths = c(0.5,1))

pHOS_tool_SPb <- cowplot::plot_grid(legend1,SP_enh_plots,
                              ncol = 2, nrow = 1,
                              axis = c("l"), align = c("hv"),
                              rel_widths = c(0.5,1))

pHOS_tool_SP <- cowplot::plot_grid(pHOS_tool_SPa, pHOS_tool_SPb,
                                   ncol = 1, nrow = 2,
                                   axis = c("l"), align = c("hv"),
                                   rel_heights = c(1,0.5))

#ggsave(pHOS_tool_SP, height = 6.5, width = 6.5, units = "in", filename = "SP_SU_1.3\\Figures\\pHOS_tool_SP.pdf")

pHOS_tool_SUa <- cowplot::plot_grid(SU_plots,pHOS,
                              ncol = 2, nrow = 1,
                              axis = c("l"), align = c("hv"),
                              rel_widths = c(0.5,1))

pHOS_tool_SUb <- cowplot::plot_grid(legend1,SU_enh_plots,
                              ncol = 2, nrow = 1,
                              axis = c("l"), align = c("hv"),
                              rel_widths = c(0.5,1))

pHOS_tool_SU <- cowplot::plot_grid(pHOS_tool_SUa, pHOS_tool_SUb,
                                   ncol = 1, nrow = 2,
                                   axis = c("l"), align = c("hv"),
                                   rel_heights = c(1,0.5))

#ggsave(pHOS_tool_SU, height = 6.5, width = 6.5, units = "in", filename = "SP_SU_1.3\\Figures\\pHOS_tool_SU.pdf")
```


