---
title: "Alpha Adjustment Validation"
author: "Colin Bailey"
date: "2026-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(rstan)
library(rstanarm)
library(shinystan)
library(bayesplot)
library(pkgbuild)
library(boot)
library(loo)
library(MASS)
library(dglm)
library(lamW)

pkgbuild::has_build_tools(debug = TRUE)
rstan_options(auto_write=T)
options(mc.cores = parallel::detectCores())

#read in and check data
lshu_dat <- read.csv("SU_0.3//Data_in//lshu_dat.csv") #data required to run stock-recruit curve to generate Nicola alpha from which the Spring and Summer 1.3 alpha values will be derived
#read in and check data
har_dat <- read.csv("SU_0.3//Data_in//har_dat.csv") #data required to run stock-recruit curve to generate Nicola alpha from which the Spring and Summer 1.3 alpha values will be derived
lshu_fec_means <- read.csv("SU_0.3//Data_in//Lower_Shuswap_Fecundity_means.csv") #fecundity data for adjusting Nicola alpha parameter for use in Spring and Summer 1.3 simulations
har_fec_means <- read.csv("SU_0.3//Data_in//Harrison_Fecundity_means.csv") #fecundity data for adjusting Nicola alpha parameter for use in Spring and Summer 1.3 simulations
har_fec_ind <- read.csv("SU_0.3//Data_in//Harrison_fecundity_2018-19_individual_data.csv") #fecundity data for adjusting Nicola alpha parameter for use in Spring and Summer 1.3 simulations
har_fec_sep <- read.csv("SU_0.3//Data_in//HarrisonFecundity_SEP.csv") #fecundity data reported by SEP in the process of spawning fish collected for brood - can compare with the reconstructed fecundity timeseries to determine bias in collection methods (i.e., are hatcheries selecting larger than average females for broodstock..?)

head(lshu_dat)
head(har_dat)

set.seed(1352)
```


Cleaning up the stock-recruit timeseries for S-R models below.
```{r data manip}
lshu_srdat <- lshu_dat %>% dplyr::select(b_year = Brood.Year, spawn = spawners, rec = recruits, surv = Survival)

har_srdat <- har_dat %>% dplyr::select(b_year = Brood.Year, spawn = Total.Age.3.5.Spawners, rec = Recruits,
                                       surv = Smolt.age2Surv)

```


Fecundity data for Harrison River came from 2018 and 2019 individual-level sampling of female chinook (Weir et al. 2022) and from estimates of mean fecundity by year based on a relationship between fish length and fecundity, again from Weir et al. 2022. Here, we estimate the variance in the individual-level data from the 2018-2019 dataset, and applying it to the annuals means to generate individual-level data for use in the fecundity-based adjustments in the stock-recruit models below. Lower Shuswap individual fecundities were also calculated from annual means collected by SEP using the variance calculated from Harrison (assumption is that given the same suite of returns at age and similar life-history, applying the variance from one to the other is fine).
```{r data manip}

#comparison of Weir et al. annual fecundity means to SEP broodstock collection fecundity means
har_SEP_means <- har_fec_sep %>% group_by(SPAWNING_YEAR) %>% summarize(k = sum(TOTAL_FEMALE_SPAWNED),
                                                      f = mean(AVERAGE_FECUNDITY)) %>% 
  dplyr::select(b_year = SPAWNING_YEAR, f_sep = f)

fec_comp <- left_join(har_SEP_means, har_fec_means) %>% drop_na() %>% mutate(s_fsep = (f_sep - mean(f_sep)) / sd(f_sep),
                                                                             s_f = (f - mean(f_sep)) / sd(f_sep))

#model using centered means to estimate conversion from SEP fecundity data to representative fecundity values
s_model <- lm(s_f ~ s_fsep, data = fec_comp)
co_fs <- summary(s_model)$coefficients

#SD of individual measures
sdf <- har_fec_ind %>% summarise(sd_f = sd(f))

#Harrison individual-level fecundity data simulated - go with number of individuals sampled in 2018 and 2019
har_f_dat <- har_fec_means %>% mutate(sd = sdf$sd_f) %>% 
  slice(rep(1:n(), times = nrow(har_fec_ind))) %>% 
  mutate(f_new = rnorm(n(), f, sd),
         CU = "FA_0.3") %>% 
  dplyr::select(b_year, f_new, CU)

#Lower Shuswap individual-level fecundity data simulated - go with number of individuals sampled for fecundity each year, start at 2020 because prior there was "high-grading" for larger females
lshu_f_dat <- lshu_fec_means %>% drop_na() %>% mutate(sd = sdf$sd_f) %>% 
  dplyr::select(b_year, f = f, k, sd) %>% 
  slice(rep(1:n(), times = k)) %>% 
  mutate(f_new = rnorm(n(), f, sd),
         CU = "SU_0.3") %>% 
  dplyr::select(b_year, f_new, CU) %>% filter(b_year > 2019)


```


This code chunk runs a Ricker stock-recruit model using Stan that incorporates a hatchery-based smolt-to-age_3 survival (SS) index covariate. The model also includes an AR-1 temporal autocorrelation structure. The SS index is logit-transformed and standardized (z-scored). Note that hatchery-origin spawners are included in the total spawners generating recruits, but only natural-origin recruits are used in the model. In addition, the model estimates the first year (1992) of the SS index because of a disease issue at Spius Creek Hatchery that severely-reduced smolt survival that year. The purpose of running this model with Nicola data is to produce a Fraser stream-type chinook productivity estimate that can be adjust below for Spring/Summer 1.3 chinook.
```{r Harrison ricker model}

#creating the list of data to feed to Stan
dat <- list("N" = nrow(har_srdat),                  #number of years of data
            "surv" = (logit(har_srdat$surv) - mean(logit(har_srdat$surv))) /
              sd(logit(har_srdat$surv)), #logit-transformed smolt to age 3 adult survival
            "lrs" = pull(har_srdat %>% mutate(lrs = log(rec/spawn)) %>% dplyr::select(lrs)),  #log natural origin  recruits per spawner (HO & NO)
            "S" = har_srdat$spawn, #vector of total spawner abundance
            "mlogit_surv" = 0, #mean logit-transformed survival
            "faN" = length(har_f_dat$f_new),
            "suN" = length(lshu_f_dat$f_new),
            "ffa" = har_f_dat$f_new,
            "fsu" = lshu_f_dat$f_new) 

#running the Stan model
fit_val1 <- stan(file = "R//Ricker_mod_alpha_validation.stan", data = dat, chains=6,
                    iter=10000, cores=6, thin = 1, seed = 1352,
                    control=list("max_treedepth"=15,"adapt_delta"=0.8),
                    pars=c("beta", "alpha", "gamma", "sigma", "Smax", "rho", "f_fa", "f_su", "alpha_su",
                           "umsy_su", "umsy_fa", "nu_Y", "p_f_su_fa"))

saveRDS(fit_val1, "R//val1_0.3_fit.RDS")

fit_val1 <- readRDS("R//val1_0.3_fit.RDS")

#extract posteriors
f_fa_v1 <- as.vector(extract(fit_val1)[7])
f_su_v1 <- as.vector(extract(fit_val1)[8])
alpha_fa_v1 <- as.vector(extract(fit_val1)[2]) 
alpha_su_v1 <- as.vector(extract(fit_val1)[9]) 
umsy_fa_v1 <- as.vector(extract(fit_val1)[11])
umsy_su_v1 <- as.vector(extract(fit_val1)[10])

out_val1 <- summary(fit_val1)

nuy <- out_val1$summary[12:41,1]#need to reset range of values extracted 
lrs <- pull(har_srdat %>% mutate(lrs = log(rec/spawn)) %>% dplyr::select(lrs))

preds <- data.frame(nuy, lrs)
preds$year <- c(1984:2013)#reset year range based on Harrison dataset

#predicted-observed plot for Harrison S-R model
preds %>% ggplot(aes(x = year, y = nuy-lrs))+
  geom_point()+
  geom_hline(yintercept = 0, colour = "Red")+
  labs(x = "Brood Year", y = "Predicted - Observed")+
  theme_classic()


##############SR Function Plot####################
preds$spawn = har_srdat$spawn

#mean prediction function for real space Ricker with SS index covariate
ricker_exp <- function(x){
  exp(-out_val1$summary[1,1] * x + out_val1$summary[2,1]) * x
}

#drawing from the posterior distribution to plot error in relationships
alpha <- as.vector(extract(fit_val1)[2])
beta <- as.vector(extract(fit_val1)[1])
gamma <- as.data.frame(extract(fit_val1)[3])
post <- data.frame(alpha, beta, gamma) %>% mutate(beta = beta * -1)

#sampling from the posterior using rows that fall within the 95% CI for alpha
qpost <- post %>% filter(alpha > quantile(post$alpha, probs = c(0.025)) & alpha < quantile(post$alpha, probs = c(0.975)))

set.seed(1352)
poste <- sample_n(qpost, 1000)

#taking a sample of 1000 lines from the 95% CI of the posterior for the normal space Ricker
uncertainty_ricker_exp <- apply(as.matrix(poste), 1, function(poste) {
  stat_function(fun=function(x){exp(poste[1] + poste[2] * x) * x}, colour="blue",
                alpha = 0.1, linewidth = 0.05)
  })

options(scipen = 999)
#normal space Ricker plot
preds %>% ggplot(aes(x = spawn, y = exp(lrs)*spawn))+
  geom_point(size = 1)+
  geom_function(fun = ricker_exp)+
  geom_abline(aes(slope = 1, intercept = 0), colour = "black", linetype = "dashed")+
  uncertainty_ricker_exp+
  labs(x = "Spawners(n)", y = "Recruits(n)")+
  scale_y_continuous(limits = c(0, 600000))+
  theme_classic()

ggsave(height = 3.5, width = 4, units = "in", filename = "har_sr_fit.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "har_sr_fit.png")
  
```


```{r Lower Shuswap ricker model}

#creating the list of data to feed to Stan
dat <- list("N" = nrow(lshu_srdat),                  #number of years of data
            "surv" = (logit(lshu_srdat$surv) - mean(logit(lshu_srdat$surv))) /
              sd(logit(lshu_srdat$surv)), #logit-transformed smolt to age 3 adult survival
            "lrs" = pull(lshu_srdat %>% mutate(lrs = log(rec/spawn)) %>% dplyr::select(lrs)),  #log natural origin  recruits per spawner (HO & NO)
            "S" = lshu_srdat$spawn, #vector of total spawner abundance
            "mlogit_surv" = 0, #mean logit-transformed survival
            "faN" = length(har_f_dat$f_new),
            "suN" = length(lshu_f_dat$f_new),
            "ffa" = har_f_dat$f_new,
            "fsu" = lshu_f_dat$f_new) 

#running the Stan model
fit_val2 <- stan(file = "R//Ricker_mod_alpha_validation2.stan", data = dat, chains=6,
                    iter=10000, cores=6, thin = 1, seed = 1352,
                    control=list("max_treedepth"=15,"adapt_delta"=0.8),
                    pars=c("beta", "alpha", "gamma", "sigma", "Smax", "rho", "f_fa", "f_su", "alpha_fa",
                           "umsy_su", "umsy_fa", "nu_Y", "p_f_fa_su"))

saveRDS(fit_val2, "R//val2_0.3_fit.RDS")

fit_val2 <- readRDS("R//val2_0.3_fit.RDS")

#extract posteriors - need to reset extraction numbers
f_fa_v2 <- as.vector(extract(fit_val2)[7])
f_su_v2 <- as.vector(extract(fit_val2)[8])
alpha_fa_v2 <- as.vector(extract(fit_val2)[9]) 
alpha_su_v2 <- as.vector(extract(fit_val2)[2]) 
umsy_fa_v2 <- as.vector(extract(fit_val2)[11])
umsy_su_v2 <- as.vector(extract(fit_val2)[10])

out_val2 <- summary(fit_val2)

nuy <- out_val2$summary[12:31,1]#need to reset range of values extracted 
lrs <- pull(lshu_srdat %>% mutate(lrs = log(rec/spawn)) %>% dplyr::select(lrs))

preds <- data.frame(nuy, lrs)
preds$year <- c(1997:2016)#reset year range based on Harrison dataset

#predicted-observed plot for Harrison S-R model
preds %>% ggplot(aes(x = year, y = nuy-lrs))+
  geom_point()+
  geom_hline(yintercept = 0, colour = "Red")+
  labs(x = "Brood Year", y = "Predicted - Observed")+
  theme_classic()

##############SR Function Plot####################
preds$spawn = lshu_srdat$spawn

#mean prediction function for real space Ricker with SS index covariate
ricker_exp <- function(x){
  exp(-out_val2$summary[1,1] * x + out_val2$summary[2,1]) * x
}

#drawing from the posterior distribution to plot error in relationships
alpha <- as.vector(extract(fit_val2)[2])
beta <- as.vector(extract(fit_val2)[1])
gamma <- as.data.frame(extract(fit_val2)[3])
post <- data.frame(alpha, beta, gamma) %>% mutate(beta = beta * -1)

#sampling from the posterior using rows that fall within the 95% CI for alpha
qpost <- post %>% filter(alpha > quantile(post$alpha, probs = c(0.025)) & alpha < quantile(post$alpha, probs = c(0.975)))

set.seed(1352)
poste <- sample_n(qpost, 1000)

#taking a sample of 1000 lines from the 95% CI of the posterior for the normal space Ricker
uncertainty_ricker_exp <- apply(as.matrix(poste), 1, function(poste) {
  stat_function(fun=function(x){exp(poste[1] + poste[2] * x) * x}, colour="blue",
                alpha = 0.1, linewidth = 0.05)
  })

#normal space Ricker plot
preds %>% ggplot(aes(x = spawn, y = exp(lrs)*spawn))+
  geom_point()+
  geom_function(fun = ricker_exp)+
  geom_abline(aes(slope = 1, intercept = 0), colour = "black", linetype = "dashed")+
  uncertainty_ricker_exp+
  labs(x = "Spawners(n)", y = "Recruits(n)")+
  scale_y_continuous(limits = c(0, 175000))+
  theme_classic()

ggsave(height = 3.5, width = 4, units = "in", filename = "lshu_sr_fit.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "lshu_sr_fit.png")
```

V1 fits a stock-recruit model to the Harrison data and then attempts to estimate Lower Shuswap productivity based on proportional differences in fecundity. V2 does the inverse, and fits a stock-recruit model to the Lower Shuswap data and then attempts to estimate Harrison productivity based on proportional differences in fecundity. Below, we plot the input fecundity data as histograms for each indicator stock, then compare the S-R vs fecundity based alphas for each stock, and then finally the UMSYs.
```{r parameter comparisons}
#fecundity comparison
f_fa <- f_fa_v2$f_fa
f_su <- f_su_v2$f_su

f_new <- c(f_fa, f_su)
CU <- c(rep("Harrison River", length(f_fa)), rep("Lower Shuswap River", length(f_su)))
fec_dat <- data.frame(f_new, CU)

fec_dat %>% ggplot(aes(x = f_new, fill = CU))+
  geom_histogram(aes(x = f_new), alpha = 0.5)+
  scale_fill_manual(values = c("#D55E00", "#0072B2"))+
  labs(x = "Fecundity (n eggs)", y = "Count (n)")+
  facet_wrap(~CU, nrow = 2)+
  theme_classic()+
  theme(legend.position = "none")

ggsave(height = 3.5, width = 4, units = "in", filename = "fcomp.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "fcomp.png")

#summer 0.3 alpha estimate comparisons
a_su <- c(alpha_su_v2$alpha, alpha_su_v1$alpha_su)
method <- c(rep("Stock-recruit", 30000), rep("Fecundity", 30000))
pro_su <- data.frame(a_su, method)
pro_su$med_a <- c(rep(median(alpha_su_v2$alpha), 30000), rep(median(alpha_su_v1$alpha_su), 30000))
pro_su$u95_a <- c(rep(quantile(alpha_su_v2$alpha, probs = 0.975), 30000), rep(quantile(alpha_su_v1$alpha_su, probs = 0.975), 30000))
pro_su$l95_a <- c(rep(quantile(alpha_su_v2$alpha, probs = 0.025), 30000), rep(quantile(alpha_su_v1$alpha_su, probs = 0.025), 30000))

pro_su %>% ggplot(aes(x = a_su))+
  geom_histogram(aes(x = a_su), fill = "#0072B2", alpha = 0.3)+
  geom_vline(aes(xintercept = med_a), colour = "#0072B2", linewidth = 1.5)+
  geom_vline(aes(xintercept = u95_a), colour = "#0072B2", linewidth = 1, linetype = "dashed")+
  geom_vline(aes(xintercept = l95_a), colour = "#0072B2", linewidth = 1, linetype = "dashed")+
  labs(x = "Productivity (ln(a))", y = "Count (n)")+
  facet_wrap(~ method, nrow = 2)+
  theme_classic()

ggsave(height = 3.5, width = 4, units = "in", filename = "acompmeth_su.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "acompmeth_su.png")

#fall 0.3 alpha estimate comparisons
a_fa <- c(alpha_fa_v1$alpha, alpha_fa_v2$alpha_fa)
method <- c(rep("Stock-recruit", 30000), rep("Fecundity", 30000))
pro_fa <- data.frame(a_fa, method)
pro_fa$med_a <- c(rep(median(alpha_fa_v1$alpha), 30000), rep(median(alpha_fa_v2$alpha_fa), 30000))
pro_fa$u95_a <- c(rep(quantile(alpha_fa_v1$alpha, probs = 0.975), 30000), rep(quantile(alpha_fa_v2$alpha_fa, probs = 0.975), 30000))
pro_fa$l95_a <- c(rep(quantile(alpha_fa_v1$alpha, probs = 0.025), 30000), rep(quantile(alpha_fa_v2$alpha_fa, probs = 0.025), 30000))

pro_fa %>% ggplot(aes(x = a_fa))+
  geom_histogram(aes(x = a_fa), fill = "#D55E00", alpha = 0.3)+
  geom_vline(aes(xintercept = med_a), colour = "#D55E00", linewidth = 1.5)+
  geom_vline(aes(xintercept = u95_a), colour = "#D55E00", linewidth = 1, linetype = "dashed")+
  geom_vline(aes(xintercept = l95_a), colour = "#D55E00", linewidth = 1, linetype = "dashed")+
  labs(x = "Productivity (ln(a))", y = "Count (n)")+
  facet_wrap(~ method, nrow = 2)+
  theme_classic()

ggsave(height = 3.5, width = 4, units = "in", filename = "acompmeth_fa.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "acompmeth_fa.png")

#Comparison of the alpha estimates 
ggplot()+
  geom_histogram(data = pro_fa, aes(x = a_fa), fill = "#D55E00", alpha = 0.3)+
  geom_histogram(data = pro_su, aes(x = a_su), fill = "#0072B2", alpha = 0.3)+
  facet_wrap(.~ method, nrow = 2)+
  scale_x_continuous(limits = c(0,3))+
  labs(x = "Productivity (ln(a))", y = "Count (n)")+
  theme_classic()

ggsave(height = 3.5, width = 4, units = "in", filename = "acompmeth_allpops.pdf")
ggsave(height = 3.5, width = 4, units = "in", filename = "acompmeth_allpops.png")

#summer 0.3 Umsy estimate comparisons
u_su <- c(umsy_su_v2$umsy_su, umsy_su_v1$umsy_su)
method <- c(rep("Ricker", 30000), rep("Fecundity", 30000))
u_su <- data.frame(u_su, method)
u_su$med_u <- c(rep(median(umsy_su_v2$umsy_su), 30000), rep(median(umsy_su_v1$umsy_su), 30000))
u_su$u95_u <- c(rep(quantile(umsy_su_v2$umsy_su, probs = 0.975), 30000), rep(quantile(umsy_su_v1$umsy_su, probs = 0.975), 30000))
u_su$l95_u <- c(rep(quantile(umsy_su_v2$umsy_su, probs = 0.025), 30000), rep(quantile(umsy_su_v1$umsy_su, probs = 0.025), 30000))

u_su %>% ggplot(aes(x = u_su))+
  geom_histogram(aes(x = u_su), fill = "#0072B2", alpha = 0.3)+
  geom_vline(aes(xintercept = med_u), colour = "#0072B2", linewidth = 1.5)+
  geom_vline(aes(xintercept = u95_u), colour = "#0072B2", linewidth = 1, linetype = "dashed")+
  geom_vline(aes(xintercept = l95_u), colour = "#0072B2", linewidth = 1, linetype = "dashed")+
  labs(x = "UMSY", y = "Count (n)")+
  facet_wrap(~ method, nrow = 2)+
  theme_classic()

#fall 0.3 Umsy estimate comparisons
u_fa <- c(umsy_fa_v1$umsy_fa, umsy_fa_v2$umsy_fa)
method <- c(rep("Ricker", 30000), rep("Fecundity", 30000))
u_fa <- data.frame(u_fa, method)
u_fa$med_u <- c(rep(median(umsy_fa_v1$umsy_fa), 30000), rep(median(umsy_fa_v2$umsy_fa), 30000))
u_fa$u95_u <- c(rep(quantile(umsy_fa_v1$umsy_fa, probs = 0.975), 30000), rep(quantile(umsy_fa_v2$umsy_fa, probs = 0.975), 30000))
u_fa$l95_u <- c(rep(quantile(umsy_fa_v1$umsy_fa, probs = 0.025), 30000), rep(quantile(umsy_fa_v2$umsy_fa, probs = 0.025), 30000))

u_fa %>% ggplot(aes(x = u_fa))+
  geom_histogram(aes(x = u_fa), fill = "#D55E00", alpha = 0.3)+
  geom_vline(aes(xintercept = med_u), colour = "#D55E00", linewidth = 1.5)+
  geom_vline(aes(xintercept = u95_u), colour = "#D55E00", linewidth = 1, linetype = "dashed")+
  geom_vline(aes(xintercept = l95_u), colour = "#D55E00", linewidth = 1, linetype = "dashed")+
  labs(x = "UMSY", y = "Count (n)")+
  facet_wrap(~ method, nrow = 2)+
  theme_classic()



```

